---
title: "POC Data Re-Upload"
date: "2025-06-27, 2025-09-04"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---



:::{.callout-note title="Purpose"}
Let's bring the sample to the field - again!

(... and again, and again, and again...)
:::


In all brevity, I collect steps here to get a new POC to the database.


# preparation

## backup

1. Make sure to manually trigger backups.
  - `ssh` to the server
  - execute scripts in `~/backups`
  - bring files home with `scp`

2. Mirrors: try everything on `testing` and then `staging`, first.
  - The `testing` mirror (data sync with `033_populate_testing_db.R`) is open for play and can taken even rough rides, and for that user permissions differ on there. No guarantee that the data is correct.
  - On `staging`, everything is exactly identical to the production server (even permissions and user roles), because it gets synced with the dump/restore commands below.
  - use the `suffix` to control database connections below.
  
  
Syncing the `*_staging` database mirrors:

  - has to be done for `loceval` and `mnmgwdb` 
  - if necessary, re-instantiate the mirror prior to data upload via `postgres`/`dropdb`+`createdb` intervention on the host system (and then run `110_*` and `210_*`, if necessary)
  - Finally, use the `pg_dump | psql` commands as follows:

  
```{sh sync-staging}
#| eval: false
pg_dump -U <backup_user> -h <host> -p <port> -d <database> -N tiger -N public -c > /tmp/<database>_db_dump.txt \
        && psql -U <database_user> -h <host> -p <port> -d <database>_staging -W < /tmp/<database>_db_dump.txt \
        && rm /tmp/<database>_db_dump.txt
```

## libraries and variables

```{r libraries}
# libraries
source("MNMLibraryCollection.R")
load_poc_common_libraries()
load_database_interaction_libraries()

# the database connection object
source("MNMDatabaseConnection.R")

# more specific database tools
source("MNMDatabaseToolbox.R")


# library("mapview") # debugging only
# mapviewOptions(platform = "mapdeck")

```


## info stream from POC

First, there is the `.RData` file.

```{r load-sample-rdata}
tic <- function(toc) round(Sys.time() - toc, 1)
toc <- Sys.time()
load_poc_rdata(reload = FALSE, to_env = parent.frame())
message(glue::glue("Good morning!
  Loading the POC data took {tic(toc)} seconds today."
))

```

Some code snippets, possibly modified on the way, were provided by Floris.

```{r source-code-snippets}
# TODO: check for changes on every update, e.g. with `meld`:
#       meld 020_fieldwork_organization/code_snippets.R 900_database_organization/050_snippet_selection.R

# Load some custom GRTS functions
# project_root <- find_root(is_git_root)
# source(file.path(project_root, "R/grts.R"))
# TODO: rebase once PR#5 gets merged
snippets_path <- "/data/git/n2khab-mne-monitoring_support"

toc <- Sys.time()
load_poc_code_snippets(snippets_path)
message(glue::glue(
  "... loading/executing the code snippets took {tic(toc)}s."
))
```


Finally, check that everything was loaded correctly.

```{r poc-checks}
verify_poc_objects()
```


## database connection


```{r load-config}

config_filepath <- file.path("./inbopostgis_server.conf")
mirror <- "-staging"

# loceval
# loceval_mirror <- glue::glue("loceval{mirror}")
# 
# loceval <- connect_mnm_database(
#   config_filepath,
#   database_mirror = loceval_mirror
# ) 


# ... and mnmgwdb
mnmgwdb_mirror <- glue::glue("mnmgwdb{mirror}")

mnmgwdb <- connect_mnm_database(
  config_filepath,
  database_mirror = mnmgwdb_mirror
) 


update_cascade_lookup <- parametrize_cascaded_update(mnmgwdb)
```


## dump all data, for safety

```{r step1-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")
# if (isFALSE(grepl("-staging", loceval_mirror))) {
#   loceval$dump_all(
#     here::here("dumps", glue::glue("safedump_{loceval$database}_{now}.sql")),
#     exclude_schema = c("tiger", "public")
#   )
# }

if (isFALSE(grepl("-staging", mnmgwdb_mirror))) {
  mnmgwdb$dump_all(
    here::here("dumps", glue::glue("safedump_{mnmgwdb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```


# Gather and Upload - mnmgwdb

## database versioning

```{r version}

if (FALSE) {
  # manually set a new version
  version_tag <- "≤v0.9.0_poc0.13.0"
  version_notes <- ""
  date_applied <- as.integer(format(Sys.time(), "%Y%m%d"))

  version_id <- mnmgwdb$tag_new_version(
    version_tag,
    version_notes,
    date_applied = NA
  )
} else {
  # per default, the latest version is taken
  version_id <- mnmgwdb$load_latest_version_id()
}

if (FALSE) {
  # ... ad hoc / testing: delete version again
  table_label <- "Versions"
  glue::glue("
  DELETE FROM {mnmgwdb$get_namestring(table_label)}
  WHERE version_tag = '{version_tag}'
    AND data_iteration = {data_iteration}
  ;
  ")
}


# TODO: I still have to make up my mind whether to archive everything.
#       For now, I will preliminarily keep it with an "archive_id" column.
```


# Test Case 1: Protocols

## diff

```{r db-diff-protocols}
#| eval: false

## relevant structural columns
# columns which uniquely identify a table entry
characteristic_columns <- c("protocol_code", "protocol_version")
# the index column
index_column <- "protocol_id" # mnmgwdb$get_primary_key("Protocols")


# # columns which indicate a change from default state; used to decide whether to archive or remove
# data_columns <- list() # format: "column_label" = "unchanged state"

# # FOR TESTING
# INSERT INTO "metadata"."Protocols" (protocol_code, protocol_version, title, language, theme, manager)
# VALUES ('fmp-000-de', '2025.00', 'a test protocol to archive', 'de', 'testing', 'Falk Mielke')
# ;

## get updated raw data
protocols_raw <- read_csv(
  here::here(mnmgwdb$folder, "data_Protocols.csv"),
  show_col_types = FALSE
)

protocols_raw <- protocols_raw %>%
  arrange(protocol_version, protocol_code)

protocols_raw %>% print(n = Inf)

protocols_distribution <- categorize_data_update(
  mnmdb = mnmgwdb,
  table_label = "Protocols",
  data_future = protocols_raw,
  input_precedence_columns = precedence_columns[["Protocols"]],
  characteristic_columns = characteristic_columns
)

print_category_count(protocols_distribution, "Protocols")
```

## update

```{r update-existing}
#| eval: false

update_existing_data(
  mnmdb = mnmgwdb,
  table_label = "Protocols",
  changed_data = protocols_distribution$changed,
  input_precedence_columns = precedence_columns[["Protocols"]],
  index_columns = c(index_column),
  reference_columns = characteristic_columns
)
```

## upload

```{r upload-data}
#| eval: false

upload_additional_data(
  mnmdb = mnmgwdb,
  table_label = "Protocols",
  new_data = protocols_distribution$to_upload,
  index_columns = c(index_column),
  tabula_rasa = FALSE,
  characteristic_columns = characteristic_columns,
  skip_sequence_reset = FALSE,
  verbose = TRUE
)
```

## rows to archive

```{r archive-data}
#| eval: false

archive_ancient_data(
  mnmdb = mnmgwdb,
  table_label = "Protocols",
  data_to_archive = protocols_distribution$to_archive,
  version_id = version_id,
  reference_columns = c(index_column)
)

# ... and un-archive = reactivate
reactivate_archived_data(
  mnmdb = mnmgwdb,
  table_label = "Protocols",
  data_to_archive = protocols_distribution$reactivate,
  reference_columns = c(index_column)
)


# NOTE: un-archived rows are not subject to UPDATE
#       if in doubt, run this again.
```


# Prune Unused Rows

I would tend to delete unused calendar entries.
However, these should be regarded by the distribution procedure itself.

Even more important, the `precedence_columns` keep input fields from being considered.


# Let's Do This

## prerequisite_lookups

```{r gather-lookups}
grouped_activity_lookup <- mnmgwdb$query_lookup(
  "GroupedActivities",
  characteristic_columns = c("activity_group", "activity")
)

n2khabstrata_lookup <- mnmgwdb$query_lookup(
  "N2kHabStrata",
  characteristic_columns = c("stratum")
)

```


```{r}

activity_groupid_lookup <- mnmgwdb$query_columns(
    "GroupedActivities",
    c("activity_group", "activity_group_id")
  ) %>%
  distinct()

gw_field_activities <- mnmgwdb$query_table("GroupedActivities") %>%
  filter(is_gw_activity, is_field_activity) %>%
  distinct(activity_group)

```

## Sample Units

```{r}

sample_units <-
  fag_stratum_grts_calendar %>%
  common_current_calenderfilters() %>%
  distinct(
    scheme_moco_ps,
    stratum,
    grts_address
  ) %>%
  unnest(scheme_moco_ps) %>%
  # adding location attributes
  inner_join(
    scheme_moco_ps_stratum_targetpanel_spsamples %>%
      distinct( # <- deduplicating 7220
        scheme,
        module_combo_code,
        panel_set,
        stratum,
        grts_join_method,
        grts_address,
        grts_address_final,
        targetpanel
      ),
    join_by(scheme, module_combo_code, panel_set, stratum, grts_address),
    relationship = "many-to-one",
    unmatched = c("error", "drop")
  ) %>%
  common_current_samplefilters() %>%
  # also join the spatial poststratum, since we need this in setting
  # GRTS-address based priorities
  inner_join(
    scheme_moco_ps_stratum_sppost_spsamples %>%
      unnest(sp_poststr_samples) %>%
      select(-sample_status),
    join_by(scheme, module_combo_code, panel_set, stratum, grts_address),
    relationship = "many-to-one",
    unmatched = c("error", "drop")
  ) %>%
  select(-module_combo_code) %>%
  nest_scheme_ps_targetpanel() %>%
  # add MHQ assessment metadata
  inner_join(
    stratum_grts_n2khab_phabcorrected_no_replacements %>%
      select(stratum, grts_address, assessed_in_field, assessment_date),
    join_by(stratum, grts_address),
    relationship = "many-to-one",
    unmatched = c("error", "drop")
  ) %>%
  distinct() %>%
  # convert_stratum_to_type() %>%
  rename_grts_address_final_to_grts_address() %>%
  rename(
    assessment = assessed_in_field,
    assessment_date = assessment_date # triv.
  ) %>%
  relocate(grts_address) %>%
  relocate(grts_join_method, .after = grts_address) %>%
  mutate(
    previous_notes = NA # FUTURE TODO
  ) %>%
  mutate(
    across(c(
        grts_join_method,
        scheme_ps_targetpanels,
        sp_poststratum,
        stratum
      ),
      as.character
    )
  )
```

## sample_locations

```{r}

sample_locations <- sample_units %>%
  summarize(
    scheme_ps_targetpanels = str_flatten(
      sort(unique(scheme_ps_targetpanels)),
      collapse = " | "
    ) %>% as.character(),
    schemes = str_flatten(
      sort(unique(scheme)),
      collapse = ", "
    ) %>% as.character(),
    strata = str_flatten(
      sort(unique(stratum)),
      collapse = ", "
    ) %>% as.character(),
    .by = c(
      grts_address,
    )
  )


```

## Locations

```{r}

locations <- bind_rows(
    mnmgwdb$query_columns("Locations", c("grts_address")),
    sample_locations %>% select(grts_address),
  ) %>%
  mutate(grts_address = as.integer(grts_address)) %>%
  distinct() %>%
  # count(grts_address) %>%
  # arrange(desc(n))
  add_point_coords_grts(
    grts_var = "grts_address",
    spatrast = grts_mh,
    spatrast_index = grts_mh_index
  )

sf::st_geometry(locations) <- "wkb_geometry"


table_label <- "Locations"
data_future <- locations %>% sf::st_drop_geometry()# %>% select(-wkb_geometry)
index_column <- mnmgwdb$get_primary_key(table_label)
characteristic_columns <- c("grts_address")

distribution <- categorize_data_update(
  mnmdb = mnmgwdb,
  table_label = table_label,
  data_future = data_future,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = characteristic_columns,
  exclude_columns = c("wkb_geometry")
)
print_category_count(distribution, table_label)

locations_lookup <- just_do_it(
  mnmdb = mnmgwdb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = characteristic_columns,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = TRUE)
)


```


## Sample Locations

```{r}

if ("location_id" %in% names(sample_locations)) {
  # should not be the case in a continuous script;
  # this is extra safety for debugging and de-serial execution
  sample_locations <- sample_locations %>%
    select(-location_id)#, -location_id.x, -location_id.y)
}
sample_locations <- sample_locations %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address),
    relationship = "many-to-one"
  ) %>% distinct 

table_label <- "SampleLocations"
data_future <- sample_locations
characteristic_columns <- c("grts_address", "location_id", "strata")
index_column <- mnmgwdb$get_primary_key(table_label)

distribution <- categorize_data_update(
  mnmdb = mnmgwdb,
  table_label = table_label,
  data_future = data_future,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = characteristic_columns,
)
print_category_count(distribution, table_label)

distribution$to_upload <- distribution$to_upload %>% 
  mutate(
    # log_user = "maintenance",
    # log_update = as.POSIXct(Sys.time()),
    is_replacement = FALSE
  ) 


samplelocations_lookup <- just_do_it(
  mnmdb = mnmgwdb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = characteristic_columns,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)


```


## FieldActivityCalendar

TODO continue here

- not "shorter" any more
- should I not add "replacements" above?

```{r}

fieldwork_calendar <-
  fieldwork_2025_prioritization_by_stratum %>%
  common_current_calenderfilters() %>% 
  rename(strata = stratum) %>% 
  rename_grts_address_final_to_grts_address() %>%
  relocate(grts_address) %>%
  inner_join(
    samplelocations_lookup,
    by = join_by(grts_address, strata),
    relationship = "many-to-one"
  ) %>%
  relocate(samplelocation_id) %>%
  rename(
    activity_rank = rank,
    activity_group = field_activity_group
  ) %>%
  semi_join(gw_field_activities, by = join_by(activity_group)) %>%
  left_join(
    activity_groupid_lookup,
    by = join_by(activity_group),
    relationship = "many-to-one"
  ) %>%
  select(-activity_group) %>%
  mutate(
    across(c(
        date_interval,
        domain_part
      ),
      as.character
    )
  ) %>%
  rename(stratum_scheme_ps_targetpanels = scheme_ps_targetpanels) %>% 
  mutate(
    log_user = "maintenance",
    log_update = as.POSIXct(Sys.time()),
    excluded = FALSE,
    no_visit_planned = FALSE,
    done_planning = FALSE
  ) 


# TODO this is obsolete and fake
sspstapas <- update_cascade_lookup(
  table_label = "SSPSTaPas",
  new_data = fieldwork_calendar %>%
    distinct(stratum_scheme_ps_targetpanels) %>%
    arrange(stratum_scheme_ps_targetpanels),
  index_columns = c("sspstapa_id"),
  tabula_rasa = TRUE,
  verbose = TRUE
)

replace_sspstapa_by_lookup <- function(df) {
  df_new <- df %>%
    left_join(
      sspstapas,
      by = join_by(stratum_scheme_ps_targetpanels),
      relationship = "many-to-one"
    ) %>%
    relocate(
      sspstapa_id,
      .after = stratum_scheme_ps_targetpanels
    ) %>%
    select(-stratum_scheme_ps_targetpanels)

  return(df_new)
}

fieldcalendar_characols <- c(
    "samplelocation_id",
    "sspstapa_id",
    "grts_address",
    "activity_group_id",
    "date_start"
  )


```


```{r}

table_label <- "FieldworkCalendar"
data_future <- fieldwork_calendar
characteristic_columns <- fieldcalendar_characols
index_column <- mnmgwdb$get_primary_key(table_label)

distribution <- categorize_data_update(
  mnmdb = mnmgwdb,
  table_label = table_label,
  data_future = data_future,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = characteristic_columns,
)
print_category_count(distribution, table_label)

```

## TODO


- LocationCells
- LocationInfos

First Round: as is

Second Round:
- adjust `common_current_calenderfilters()` -> 2026 data

Third Round
- then re-download RData
- -> add new `wait_*` column
