---
title: "EXPLORATION: link new start dates for POC update"
date: "2025-10-22"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---

# Strategy

## Problem
The purpose of this script is to revert the issues caused by premature POC update and *the `start_date` issue*.

::: {.callout-note}
The `start_date` issue refers to an issue caused by the use of the `start_date` column as a characteristic column to identify uniqueness of a table entry in `FieldActivityCalendar`/`FieldworkCalendar`, `Visits`, and "Special Activity" tables.
The issue occurred upon update from POC version `0.13.1` to `0.14.0`.

Because start data could change upon calendar adjustments, related entries were not linked, and previously planned activities disappeared in the archives (due to filtering `archive_version_id` column).

:::

## Prior Partial Mitigations
In the aftermath of the confusion around "Achterhaven Zeebrugge", two paths of manual interference were explored:

1. (loceval) mostly via R script → `file:./surgery/20251020_achterhaven_zeebrugge_locevalterr.org`
2. (mnmgwdb) mostly SQL based → `file:./surgery/20251021_achterhaven_zeebrugge_gwinst.org`

Besides, all "planned" and "executed" activities were recovered from archives to avoid (visual) loss of these efforts.

```{sql}
#| eval: false
UPDATE "outbound"."FieldworkCalendar" 
SET archive_version_id = NULL
WHERE done_planning;
-- UPDATE 194

UPDATE "inbound"."Visits" 
SET archive_version_id = NULL
WHERE visit_done;
-- UPDATE 118

UPDATE "outbound"."SampleLocations"
SET archive_version_id = NULL
WHERE grts_address IN (
  1195701, 122549, 1588917, 19914421, 212661, 253621, 29769397, 3202741, 3554997, 3858101, 409269, 4447925, 44961461, 450229, 48053941, 48578229, 49692341, 50282165, 5193397, 5234357, 540341, 5455541, 5979829, 6360757, 6504117, 6635189, 6811317, 7409333, 908981
);
-- UPDATE 22


```

## Status Quo

All previously planned/executed activities have 

- (i) no `archive_version_id` 
- (ii) potential double planning with the new calendar


Ideally, they should be 

- connected with the successor activity 
- start date and other fields updated 
- then, successor activity can be archived or directly removed

*Issue 1:* adjusting start date will crash `unique` conflicts; hence, data must be downloaded and manually adjusted.

```{sql}
SELECT *
FROM "outbound"."FieldActivityCalendar" AS FAC
WHERE done_planning;
```


*Issue 2:*
Due to the intermediate manipulations, I cannot separate novel from old plans any more.
Solution would be to load the old and new calendar in R, select those which disappear, record their lookup columns, and link them manually to a newly planned event.


## Dump New Plan

This goes back to the latest `RData` file to retrieve the actual new plan, prior to fiddling.

```{r libraries}
#| eval: false

library("dplyr")
library("tidyr")
library("stringr")
library("purrr")
library("lubridate")
library("googledrive")
library("readr")
library("rprojroot")
library("sf")
library("terra")
library("n2khab")

data_basepath <- "./data"
# rdata_file <- "objects_panflpan5_v0.13.1_20250908.RData"
rdata_file <- "objects_panflpan5_v0.14.0_20251016.RData"


poc_rdata_path <- file.path(data_basepath, rdata_file)

to_env <- parent.frame()
load(poc_rdata_path, envir = to_env)


snippets_path <- rprojroot::find_root(rprojroot::is_git_root)
source(file.path(snippets_path, "020_fieldwork_organization/R/grts.R"))
source(file.path(snippets_path, "020_fieldwork_organization/R/misc.R"))

invisible(capture.output(source("050_snippet_selection.R")))
source("051_snippet_transformation_code.R")

```


Two options here: 

- the "full" list of activities (`fag_stratum_grts_calendar`)
- the reduced, applied subset (`fieldwork_2025_prioritization_by_stratum`)

I think the first one caused trouble because there were manually shifted activities
which date back to 2024; 
but because I use group-wise counting below they count as the first applicable date.
The "2025"(+) calendar is more focused, yet also lacks connection to some later procedures (thus missing the link, below).

```{r fwcal}
#| eval: false

fieldwork_calendar <-
  fag_stratum_grts_calendar %>%
  # fieldwork_2025_prioritization_by_stratum %>%
  common_current_calenderfilters() %>% # should be filtered already!
  filter(date_start >= as.Date("2025-07-01")) %>% 
  rename_grts_address_final_to_grts_address() %>%
  relocate(grts_address) %>%
  rename(type = stratum) %>%
  rename(
    activity_rank = rank,
    activity_group = field_activity_group
  ) %>%
  select(grts_address, type, activity_group, date_start) %>%
  mutate(
    across(c(
        type,
        activity_group
      ),
      as.character
    )
  )

fieldwork_calendar %>% head(5)

saveRDS(fieldwork_calendar, "dumps/fieldwork_calendar_poc0140.rds")

```


# Link Activities

I will take the planned activities and connect them to the new calendar,
then manually compare, select, and update where necessary.


```{r db-connect}

source("MNMLibraryCollection.R")
load_database_interaction_libraries()
source("MNMDatabaseConnection.R")
source("MNMDatabaseToolbox.R")


database <- "loceval"
config_filepath <- file.path("./inbopostgis_server.conf")
mirror <- ""

# connect loceval
locevaldb_mirror <- glue::glue("{database}{mirror}")

locevaldb <- connect_mnm_database(
  config_filepath,
  database_mirror = locevaldb_mirror,
  user = "monkey",
  password = NA
) 
# keyring::keyring_delete(keyring = "mnmdb_temp")

message(glue::glue("connected: psql {locevaldb$shellstring}"))


grouped_activity_lookup <- locevaldb$query_columns(
    "GroupedActivities",
    c("activity_group", "activity_group_id")
  ) %>%
  distinct()

grouped_activity_lookup %>% count(activity_group) %>% filter(n > 1)
```


All activities trace back to the FieldActivityCalendar.

```{r query-calendar}
status_quo <- locevaldb$query_columns(
    "FieldActivityCalendar",
    c("grts_address",
      "type",
      "activity_group_id",
      "date_start",
      "done_planning",
      "archive_version_id",
      "fieldactivitycalendar_id"
    )
  )  %>%
  left_join(
    locevaldb$query_columns(
      "Visits",
      c("fieldactivitycalendar_id", "visit_done")
    ),
    by = join_by(fieldactivitycalendar_id)
  )  %>% 
  arrange(date_start) %>% 
  mutate(date_id = row_number(), .by = c("grts_address", "type", "activity_group_id"))


calender_new <- readRDS("dumps/fieldwork_calendar_poc0140.rds") %>%
  left_join(grouped_activity_lookup, by = join_by(activity_group)) %>%
  select(-activity_group) %>%
  semi_join(
    status_quo,
    by = join_by(grts_address, type, activity_group_id)
  ) %>%
  mutate(date_id = row_number(), .by = c("grts_address", "type", "activity_group_id"))


versions <- locevaldb$query_table("Versions")
```

Simplification: there seem to be only unique start dates, no double action on a location.


If entries are unchanged, they are fine. 
Thus, I filter those out.
Then I select the complement, the changed activities.

```{r filter-unchanged}
status_quo %>%
  semi_join(
    calender_new,
    by = join_by(grts_address, type, activity_group_id, date_start)
  ) %>% arrange(archive_version_id) %>% 
  knitr::kable()

status_changed <- status_quo %>%
  anti_join(
    calender_new,
    by = join_by(grts_address, type, activity_group_id, date_start)
  ) %>% arrange(grts_address, type, activity_group_id, date_start) 

glimpse(status_changed) %>% knitr::kable()
```


472 changed activities.
Bring them together in a table.

```{r join-changes}

status_changed %>%
  left_join(
    calender_new,
    by = join_by(grts_address, type, activity_group_id),
    suffix = c("","_new")
  ) %>%
  filter(
    date_id == date_id_new,
    ((archive_version_id == 2)
     | (is.na(archive_version_id) & (done_planning | visit_done))
     )
  ) %>% 
  mutate(across(c(date_start, date_start_new), as.character)) %>% 
  write.csv2("dumps/fieldwork_calendar_poc0140_loceval.csv")

```


```
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 253621 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 299701 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 450229 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 518902 AND type = '7140_meso' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1375541 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1576233 AND type = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1584945 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND type = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 16 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 27 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 30 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1896241 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1899829 AND type = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3202741 AND type = '1310_pol' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3673653 AND type = '6510_hu' AND activity_group_id = 11 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 253621 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 299701 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 450229 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-07-01' WHERE grts_address = 518902 AND type = '7140_meso' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1375541 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1576233 AND type = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1584945 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1676465 AND type = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 16 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 27 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 30 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1896241 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1899829 AND type = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 3202741 AND type = '1310_pol' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2025-07-01' WHERE grts_address = 3673653 AND type = '6510_hu' AND activity_group_id = 11 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 253621 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 299701 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 450229 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 518902 AND type = '7140_meso' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1375541 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1576233 AND type = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1584945 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND type = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 16 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 27 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 30 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1896241 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1899829 AND type = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3202741 AND type = '1310_pol' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3673653 AND type = '6510_hu' AND activity_group_id = 11 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 253621 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 299701 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 450229 AND type = '1330_hpr' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-07-01' WHERE grts_address = 518902 AND type = '7140_meso' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1375541 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1576233 AND type = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1584945 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1676465 AND type = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 16 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 27 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-07-01' WHERE grts_address = 1768757 AND type = '2190_a_0_1' AND activity_group_id = 30 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1896241 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1899829 AND type = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 3202741 AND type = '1310_pol' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-07-01' WHERE grts_address = 3673653 AND type = '6510_hu' AND activity_group_id = 11 AND date_start = '2025-10-01';


UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 480306 AND type = '6410_mo' AND activity_group_id = 4 AND date_start = '2030-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1542626 AND type = '6510_hus' AND activity_group_id = 4 AND date_start = '2027-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1922225 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2027-01-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1996593 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2027-04-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 2137206 AND type = '7230' AND activity_group_id = 4 AND date_start = '2027-04-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3858101 AND type = '1310_pol' AND activity_group_id = 4 AND date_start = '2027-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 17923334 AND type = '91E0_vc' AND activity_group_id = 4 AND date_start = '2030-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 21167406 AND type = '6410_ve' AND activity_group_id = 4 AND date_start = '2027-01-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2030-10-01' WHERE grts_address = 480306 AND type = '6410_mo' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2027-10-01' WHERE grts_address = 1542626 AND type = '6510_hus' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2027-01-01' WHERE grts_address = 1922225 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2027-04-01' WHERE grts_address = 1996593 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2027-04-01' WHERE grts_address = 2137206 AND type = '7230' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2027-10-01' WHERE grts_address = 3858101 AND type = '1310_pol' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2030-07-01' WHERE grts_address = 17923334 AND type = '91E0_vc' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldActivityCalendar"  SET date_start = '2027-01-01' WHERE grts_address = 21167406 AND type = '6410_ve' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 480306 AND type = '6410_mo' AND activity_group_id = 4 AND date_start = '2030-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1542626 AND type = '6510_hus' AND activity_group_id = 4 AND date_start = '2027-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1922225 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2027-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1996593 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2027-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 2137206 AND type = '7230' AND activity_group_id = 4 AND date_start = '2027-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3858101 AND type = '1310_pol' AND activity_group_id = 4 AND date_start = '2027-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 17923334 AND type = '91E0_vc' AND activity_group_id = 4 AND date_start = '2030-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 21167406 AND type = '6410_ve' AND activity_group_id = 4 AND date_start = '2027-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2030-10-01' WHERE grts_address = 480306 AND type = '6410_mo' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-10-01' WHERE grts_address = 1542626 AND type = '6510_hus' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-01-01' WHERE grts_address = 1922225 AND type = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-04-01' WHERE grts_address = 1996593 AND type = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-04-01' WHERE grts_address = 2137206 AND type = '7230' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-10-01' WHERE grts_address = 3858101 AND type = '1310_pol' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2030-07-01' WHERE grts_address = 17923334 AND type = '91E0_vc' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-01-01' WHERE grts_address = 21167406 AND type = '6410_ve' AND activity_group_id = 4 AND date_start = '2025-07-01';

```


# MNMGWDB

```{r mnmgwdb-connect}
database <- "mnmgwdb"
config_filepath <- file.path("./inbopostgis_server.conf")
mirror <- ""

# connect loceval
mnmgwdb_mirror <- glue::glue("{database}{mirror}")

mnmgwdb <- connect_mnm_database(
  config_filepath,
  database_mirror = mnmgwdb_mirror,
  user = "monkey",
  password = NA
) 
# keyring::keyring_delete(keyring = "mnmdb_temp")

message(glue::glue("connected: psql {mnmgwdb$shellstring}"))


grouped_activity_lookup <- mnmgwdb$query_columns(
    "GroupedActivities",
    c("activity_group", "activity_group_id")
  ) %>%
  distinct()

grouped_activity_lookup %>% count(activity_group) %>% filter(n > 1)
```

```{r query-gw-calendar}
status_quo <- mnmgwdb$query_columns(
    "FieldworkCalendar",
    c("grts_address",
      "stratum",
      "activity_group_id",
      "date_start",
      "done_planning",
      "archive_version_id",
      "fieldworkcalendar_id"
    )
  )  %>%
  left_join(
    mnmgwdb$query_columns(
      "Visits",
      c("fieldworkcalendar_id", "visit_done")
    ),
    by = join_by(fieldworkcalendar_id)
  )  %>% 
  arrange(date_start) %>% 
  mutate(date_id = row_number(), .by = c("grts_address", "stratum", "activity_group_id"))


calender_new <- readRDS("dumps/fieldwork_calendar_poc0140.rds") %>%
  left_join(grouped_activity_lookup, by = join_by(activity_group)) %>%
  select(-activity_group) %>%
  rename(stratum = type) %>% 
  semi_join(
    status_quo,
    by = join_by(grts_address, stratum, activity_group_id)
  ) %>%
  mutate(date_id = row_number(), .by = c("grts_address", "stratum", "activity_group_id"))


versions <- mnmgwdb$query_table("Versions")
```


```{r filter-gw-unchanged}
status_quo %>%
  semi_join(
    calender_new,
    by = join_by(grts_address, stratum, activity_group_id, date_start)
  ) %>% arrange(archive_version_id) %>% 
  knitr::kable()

status_changed <- status_quo %>%
  anti_join(
    calender_new,
    by = join_by(grts_address, stratum, activity_group_id, date_start)
  ) %>% arrange(grts_address, stratum, activity_group_id, date_start) 

glimpse(status_changed) %>% knitr::kable()
```



```{r join-changes}

status_changed %>%
  left_join(
    calender_new,
    by = join_by(grts_address, stratum, activity_group_id),
    suffix = c("","_new"),
    relationship = "many-to-many"
  ) %>%
  filter(
    date_id == date_id_new,
    (archive_version_id == 3)
    # | ( done_planning) # is.na(archive_version_id) &
  ) %>% 
  mutate(across(c(date_start, date_start_new), as.character)) %>% 
  write.csv2("dumps/fieldwork_calendar_poc0140_mnmgwdb.csv")

```


```
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 6086 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 6110 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9366 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 13574 AND stratum = '91E0_va' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 20274 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 30153 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 65529 AND stratum = '6430_hf' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 70250 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 82654 AND stratum = '4010' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 111542 AND stratum = '91E0_vo' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 425702 AND stratum = '7140_meso' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 498886 AND stratum = '6410_mo' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 539957 AND stratum = '2190_a_0_1' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 606290 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 662802 AND stratum = '3260' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1129886 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1735814 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3673653 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3812142 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4740049 AND stratum = '6230_hmo' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 19752678 AND stratum = '3130_aom_0_1' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 27584145 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48457497 AND stratum = '7220' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 11 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 13 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 11 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 13 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 6086 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 6110 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 9366 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 13574 AND stratum = '91E0_va' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 20274 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 30153 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 65529 AND stratum = '6430_hf' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 70250 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 82654 AND stratum = '4010' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 111542 AND stratum = '91E0_vo' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 425702 AND stratum = '7140_meso' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 498886 AND stratum = '6410_mo' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 539957 AND stratum = '2190_a_0_1' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 606290 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 662802 AND stratum = '3260' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1129886 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 1735814 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 3673653 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 3812142 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 4740049 AND stratum = '6230_hmo' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 19752678 AND stratum = '3130_aom_0_1' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 27584145 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-01-01' WHERE grts_address = 48457497 AND stratum = '7220' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 11 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 13 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 11 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 13 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-10-01' WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-07-01' WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2026-04-01' WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 6086 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 6110 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9366 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 13574 AND stratum = '91E0_va' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 20274 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 30153 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 65529 AND stratum = '6430_hf' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 70250 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 82654 AND stratum = '4010' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 111542 AND stratum = '91E0_vo' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 425702 AND stratum = '7140_meso' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 498886 AND stratum = '6410_mo' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 539957 AND stratum = '2190_a_0_1' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 606290 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 662802 AND stratum = '3260' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1129886 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1735814 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3673653 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 3812142 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4740049 AND stratum = '6230_hmo' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 19752678 AND stratum = '3130_aom_0_1' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 27584145 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48457497 AND stratum = '7220' AND activity_group_id = 15 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 11 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 13 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 11 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 13 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 6086 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 6110 AND stratum = '9120' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 9366 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 13574 AND stratum = '91E0_va' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 20274 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 30153 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 65529 AND stratum = '6430_hf' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 70250 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 82654 AND stratum = '4010' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 111542 AND stratum = '91E0_vo' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 299701 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 306713 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 312857 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 327153 AND stratum = '6510_hua' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 425702 AND stratum = '7140_meso' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 455349 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 498886 AND stratum = '6410_mo' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 539957 AND stratum = '2190_a_0_1' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 587382 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 606290 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 662802 AND stratum = '3260' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 673910 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 702674 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 717750 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 859446 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 878290 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 880094 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 915062 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1006889 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1129886 AND stratum = '91E0_vn' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1203497 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1363273 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 1371953 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1375541 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 1472305 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1576233 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1584945 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1660081 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1676465 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1677870 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1723145 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 1735814 AND stratum = '9160' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 1896241 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 1899829 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 3673653 AND stratum = '6510_hu' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 3812142 AND stratum = '9190' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 4026486 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 4537673 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 4740049 AND stratum = '6230_hmo' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 4799817 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 4878210 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 9431346 AND stratum = '7140_mrd' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 18526001 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 19752678 AND stratum = '3130_aom_0_1' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 27584145 AND stratum = '6510_hua' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 44831413 AND stratum = '1330_hpr' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 47583517 AND stratum = '6430_mr' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-01-01' WHERE grts_address = 48457497 AND stratum = '7220' AND activity_group_id = 15 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 48933681 AND stratum = '2190_overig' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 11 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 13 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49757406 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 11 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 13 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2025-10-01' WHERE grts_address = 49779889 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 49877622 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-10-01' WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 9 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 50042033 AND stratum = '2190_mp' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-07-01' WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 9 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2026-04-01' WHERE grts_address = 51535145 AND stratum = '6430_hw' AND activity_group_id = 28 AND date_start = '2025-10-01';

UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2029-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2029-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2029-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2029-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2029-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 7069106 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2027-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 13688242 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2029-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2028-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2028-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 53206450 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2029-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-01-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-07-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-01-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-04-01' WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-04-01' WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2027-04-01' WHERE grts_address = 7069106 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-04-01' WHERE grts_address = 13688242 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2028-07-01' WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2028-07-01' WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-04-01' WHERE grts_address = 53206450 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2029-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2029-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2029-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2029-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2029-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 7069106 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2027-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 13688242 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2029-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2028-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2028-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 53206450 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2029-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-01-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-07-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-01-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-04-01' WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-04-01' WHERE grts_address = 5527750 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2027-04-01' WHERE grts_address = 7069106 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-04-01' WHERE grts_address = 13688242 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2028-07-01' WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 4 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2028-07-01' WHERE grts_address = 47517086 AND stratum = '6510_hus' AND activity_group_id = 28 AND date_start = '2025-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-04-01' WHERE grts_address = 53206450 AND stratum = '9130_fm' AND activity_group_id = 28 AND date_start = '2025-07-01';

UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9262 AND stratum = '9120' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 4 AND date_start = '2031-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2031-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 88274 AND stratum = '9190' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 4 AND date_start = '2031-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 28 AND date_start = '2031-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 211193 AND stratum = '91E0_vc' AND activity_group_id = 28 AND date_start = '2032-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 236530 AND stratum = '4010' AND activity_group_id = 28 AND date_start = '2032-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 4 AND date_start = '2032-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 28 AND date_start = '2032-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2031-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2032-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2032-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1736754 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2031-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1902553 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2031-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1904953 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2029-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-10-01' WHERE grts_address = 9262 AND stratum = '9120' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-04-01' WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-04-01' WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-10-01' WHERE grts_address = 88274 AND stratum = '9190' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-07-01' WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-07-01' WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2032-04-01' WHERE grts_address = 211193 AND stratum = '91E0_vc' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2032-04-01' WHERE grts_address = 236530 AND stratum = '4010' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2032-04-01' WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2032-04-01' WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-10-01' WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-10-01' WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2032-07-01' WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2032-07-01' WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-07-01' WHERE grts_address = 1736754 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-01-01' WHERE grts_address = 1902553 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2031-10-01' WHERE grts_address = 1904953 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "outbound"."FieldworkCalendar"  SET date_start = '2029-07-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 9262 AND stratum = '9120' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 4 AND date_start = '2031-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2031-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 88274 AND stratum = '9190' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 4 AND date_start = '2031-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 28 AND date_start = '2031-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 211193 AND stratum = '91E0_vc' AND activity_group_id = 28 AND date_start = '2032-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 236530 AND stratum = '4010' AND activity_group_id = 28 AND date_start = '2032-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 4 AND date_start = '2032-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 28 AND date_start = '2032-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2031-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2032-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2032-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1736754 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2031-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1902553 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2031-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 1904953 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2031-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2024-01-01', archive_version_id = 3 WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2029-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-10-01' WHERE grts_address = 9262 AND stratum = '9120' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-04-01' WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 4 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-04-01' WHERE grts_address = 22726 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-10-01' WHERE grts_address = 88274 AND stratum = '9190' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-07-01' WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-07-01' WHERE grts_address = 114454 AND stratum = '6430_hf' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2032-04-01' WHERE grts_address = 211193 AND stratum = '91E0_vc' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2032-04-01' WHERE grts_address = 236530 AND stratum = '4010' AND activity_group_id = 28 AND date_start = '2026-07-01';
UPDATE  "inbound"."Visits"  SET date_start = '2032-04-01' WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2032-04-01' WHERE grts_address = 709330 AND stratum = '7140_meso' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-10-01' WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-10-01' WHERE grts_address = 780114 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2032-07-01' WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 4 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2032-07-01' WHERE grts_address = 1032326 AND stratum = '6230_hmo' AND activity_group_id = 28 AND date_start = '2026-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-07-01' WHERE grts_address = 1736754 AND stratum = '9160' AND activity_group_id = 28 AND date_start = '2026-01-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-01-01' WHERE grts_address = 1902553 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2025-10-01';
UPDATE  "inbound"."Visits"  SET date_start = '2031-10-01' WHERE grts_address = 1904953 AND stratum = '9130_end' AND activity_group_id = 28 AND date_start = '2026-04-01';
UPDATE  "inbound"."Visits"  SET date_start = '2029-07-01' WHERE grts_address = 5471538 AND stratum = '7140_oli' AND activity_group_id = 9 AND date_start = '2026-07-01';


```

```{sql}
#| eval: false
\COPY (
SELECT * FROM "outbound"."FieldworkCalendar"
WHERE done_planning
OR fieldworkcalendar_id IN (
  SELECT fieldworkcalendar_id FROM "inbound"."Visits" WHERE visit_done
)
) TO '/data/mnm_db_backups/check_fwcal_mnmgwdb.csv' With CSV DELIMITER ',' HEADER;
```


```{r find_by_grts}
source("MNMLibraryCollection.R")
load_database_interaction_libraries()

grts_archived_locations <- c(
  114454, 9262, 22726, 42070750, 41313630, 1032326, 22726, 299701, 7069106, 4211622, 1904953, 53206450, 1176286, 1736754, 1032326, 88274, 114454, 131806, 131806, 211193, 709330, 709330, 236530, 455349, 455349, 780114, 1176286, 1902553, 4772254, 5471538, 5471538, 5471538, 5471538, 5471538, 5471538, 5527750, 5527750, 6417454, 8826293, 8826293, 12773714, 12773714, 13688242, 15026297, 15026297, 17912057, 17912057, 42070750, 43623186, 43623186, 43623186, 47517086, 47517086, 43623186, 780114, 21323197 
)


calender_check <- readRDS("dumps/fieldwork_calendar_poc0140.rds") %>%
  filter(grts_address %in% grts_archived_locations) %>%
  filter(activity_group == "GWINSTPIEZWELL")


```
