---
title: "Sample Unit Overview"
date: today
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
  pdf:
    toc: false
    margin-left: 1cm
    margin-top: 1cm
    margin-rechts: 1cm
    margin-bottom: 1cm
knitr:
  opts_chunk:
    echo: false
---



```{r libraries}

source("MNMLibraryCollection.R")
load_database_interaction_libraries()

source("MNMDatabaseConnection.R")
source("MNMDatabaseToolbox.R")

# credentials are stored for easy access
config_filepath <- file.path("./mnm_database_connection.conf")

# suffix <- "-staging" # "-testing"
suffix <- ""
```


choose a GRTS


```{r choose-grts}
# filter(grts_address %in% c(1999406, 6417454))
#
grts <- c(9488370) # clean and samp activity not matching for Q3 2026 # also 1062930
  # c(1466998) # no replacement cells visible
  # c(289513)
  # c(84598, 871030) # replacement mishap
  # c(1995094) # question by @TDD via chat 20260428 loceval not forwarded
  # c(2742, 18877110) # loceval not passed through to mnmgwdb
  # c(50120690, 51169266) # delayed push of locevals 20260601
  # c(83694, 364822, 1519830) #, 70530, 25236354) # in monitoring zones of other institute
  # c(31414) # loceval not possible due to erroneous ofo disapproval
  # c(1126121, 1995222, 29258198) # yet another loceval double registration (the latter two are local replacement)
# grts <- c(1999406, 6417454) # replacement happened; but location went to archive 7
    # c(6110, 1118141,   18986217,  9366, 12592278) # accidental retrospective fill-in of a frozen location 
# grts <- c(1946498, 4354946, 1353694, 1118141, 29258198, 7853673) # new uploads rep update snips 0.15.0
    # c(12401, 11825, 13686)
    # c(50354734, 20994606) # replacement happened; but location went to archive 7
    # c(22021842) # potential frozen duplicate
    # c(437685, 8826293) # grts from shortterm gpkg which did not appear on database
    # c(11561) # favorite testing location in Kruibeke
    # c(21329) # random SOIL_03.2 location
    # c(111326, 881374) # MNM team praatje location -> fieldwork knowledge transfer 20260203
    # c(11561, 8400169) # test case for 091a overhaul
    # c(826486, 51158134)
    # c(23238, 6314694, 23091910) # Hellebos!
    # c(4229394) # an installed, but archived installation
    # c(50725598) # a loceval on archive: replacement required, but none selected
    # c(1202926, 10640110) # more missed archives
    # c(24774) # forest location where the first choice of point should be cell center; MHQ assessment unclear
    # c(1205598, 41313630) # replacement cell missing from updated plans
    # c(49896893, 21323197) # first sideload: visit with issues must be repeated
    # c(908981)#, 59629237) # dismissed -> no replacements
    # c(1205598, 41313630) # replacement from previous POC version -> sideloaded
    # c(5193397, 59719349) # LOST?! NO! -> just mistyped the replacer GRTS. But it is archived.
    # c(3554997, 29769397) # early bird ZEB/achterhaven
    # c(1999406, 6417454)
    # c(53206450) # victim to the Dolle Dromedaris
    # c(13688242) # victim to the Dolle Dromedaris
    # c(53662, 4772254) # victim to the Dolle Dromedaris
    # c(41313630) # installed location, not planned anymore
    # c(49896893, 21323197)

    # c(1902553) # info INST op foute regel (planning oud: 2025-10-01; nieuw: 2025-07-01)
    # c(6092977) # info INST on wrong row

    # c(3554997, 29769397)
    # c(5234357, 19914421)
    # c(5193397, 59719349) # left-over WIA
    # SELECT * FROM "inbound"."WellInstallationActivities" WHERE grts_address = 59719349;
    # UPDATE "inbound"."WellInstallationActivities" SET grts_address = 59719349 WHERE grts_address = 5193397;

    # c(4163858, 29329682)
    # c(415022, 3560750)
    # c(122549)
    # c(49896893, 21323197) # "Putten West"; disappeared with POC update 0.14 (TODO)
    # c(3554997, 29769397)
    # c(51221550, 16470006) # WIA/CSA mismatch 20251016 -> special activities seem missed on replacement processing (091_)
    # c(120110) # dual replacement
    # c(23257, 60185305) # visit by Wouter 20/8
    # c(1920534) # cell lost upon update loceval
    # c(2136622, 1677870)
    # c(53438326, 57632630)
    # c(437685, 8826293)
    # c(24774)
    # c(1280278)
    # c(4761777)
    # c(10119474) # this is only LOCEVAL <- SURF_03.4_lentic
    # c(1202926, 10640110) more missed archives
    # c(219694, 9525806) # was partially replaced and therefore archived
    # c(1999406, 6417454) # was falsely archived
    # c(31496054)
    # c(219694)

```

# MNMSYNCDB: `r as.character(grts)`

```{r connect-syncdb}
database_label <- "mnmsyncdb"

### connect to database
mnmdb <- connect_mnm_database(
  config_filepath,
  database_mirror = glue::glue("{database_label}{suffix}"),
  user = "monkey",
  password = NA
)
# keyring::keyring_delete(keyring = "mnmdb_temp")
message(mnmdb$shellstring)

```


```{r syncdb-infos}

infos <- mnmdb$query_table("LocationInfos") %>%
  filter(grts_address %in% grts)

sync_print_infos <- function() {
  infos %>%
    dplyr::rename(
      grts = grts_address,
      liid = locationinfo_id,
      inaccess = accessibility_inaccessible,
      hints = recovery_hints
    ) %>%
    dplyr::select(
      liid,
      grts,
      inaccess,
      hints
    ) %>%
    knitr::kable()
}

```


```{r syncdb-lojos}

lojos <- mnmdb$query_table("LocationJournals") %>%
  filter(grts_address %in% grts)

sync_print_lojos <- function() {
  lojos %>%
    dplyr::rename(
      grts = grts_address,
      ljid = locationjournal_id,
      src = source,
      agid = activity_group_id,
      types = type_subset
    ) %>%
    dplyr::count(
      grts,
      types,
      agid,
      src
    ) %>%
    knitr::kable()
}

```


```{r syncdb-replacements}

replacements <- bind_rows(
  mnmdb$query_table("ReplacementData") %>%
    filter(grts_address_original %in% grts),
  mnmdb$query_table("ReplacementData") %>%
    filter(grts_address_replacement %in% grts)
  ) %>%
  distinct()

sync_print_replacements <- function() {
  replacements %>%
    dplyr::rename(
      typ = type,
      grts = grts_address_original,
      rep = grts_address_replacement,
      rank = replacement_rank,
      lat = is_latest_replacement
    ) %>%
    dplyr::select(
      typ,
      grts,
      rep,
      rank,
      lat
    ) %>%
    knitr::kable()
}

```


```{r sync-print}
sync_print_infos()
sync_print_lojos()
sync_print_replacements()

```



# LOCEVAL: `r as.character(grts)`

```{r connect-loceval}
database_label <- "loceval"

### connect to database
mnmdb <- connect_mnm_database(
  config_filepath,
  database_mirror = glue::glue("{database_label}{suffix}"),
  user = "monkey",
  password = NA
)
# keyring::keyring_delete(keyring = "mnmdb_temp")
message(mnmdb$shellstring)

```


```{r helper-loceval-activity-groups}

join_activity_groups <- function(df) {
  df %>% dplyr::left_join(
      mnmdb$query_columns(
        "GroupedActivities",
        c(
          "activity_group_id",
          "activity_group"
        )
      ) %>% dplyr::distinct(),
      by = dplyr::join_by(activity_group_id)
    ) %>%
  return()
}

```


```{r sample-units}

sunit <- mnmdb$query_table("SampleUnits") %>%
  filter(grts_address %in% grts)


loc_ids <- mnmdb$pull_column("Locations", "location_id")
loc_cells <- mnmdb$pull_column("LocationCells", "location_id")
loc_infos <- mnmdb$pull_column("LocationInfos", "location_id")

sunit <- sunit %>%
  mutate(
    has_loc = location_id %in% loc_ids,
    has_cell = location_id %in% loc_cells,
    has_infos = location_id %in% loc_infos,
    archived = isFALSE(is.na(archive_version_id))
  )

eva_print_sunit <- function() {
  sunit %>%
    dplyr::rename(
      suid = sampleunit_id,
      lid = location_id,
      replaced = is_replaced,
      mhq = in_mhq_samples,
      forest = is_forest,
      typ_weg = type_is_absent,
      grts = grts_address
    ) %>%
    dplyr::select(
      grts,
      type,
      domain_part,
      schemes,
      lid,
      suid,
      replaced,
      has_loc,
      has_cell,
      has_infos,
      mhq,
      forest,
      typ_weg,
      archived
    ) %>%
    t() %>% 
    knitr::kable()
}

```


```{r loceval-ofos}

ofos <- mnmdb$query_table("LocationAssessments") %>%
  filter(grts_address %in% grts)

eva_print_ofos <- function() {
  ofos %>%
    dplyr::rename(
      lid = location_id,
      suid = sampleunit_id,
      grts = grts_address,
      dis = cell_disapproved,
      done_a = assessment_done
    ) %>%
    arrange(type, dis, done_a) %>% 
    dplyr::select(
      suid,
      grts,
      type,
      dis,
      done_a
    ) %>%
    knitr::kable()
}

```


```{r loceval-calendar}

facal <- mnmdb$query_table("FieldCalendars") %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups() # %>%

eva_print_facal <- function() {
  facal %>%
    dplyr::rename(
      fcid = fieldcalendar_id,
      suid = sampleunit_id,
      agid = activity_group_id,
      archv = archive_version_id,
      done_p = done_planning,
      frz = is_frozen,
      no_vis = no_visit_planned
    ) %>%
    dplyr::select(
      type,
      suid,
      fcid,
      agid,
      activity_group,
      date_start,
      archv,
      frz,
      no_vis,
      done_p
    ) %>%
    arrange(type, date_start, agid) %>% 
    knitr::kable()
}

```

```{r loceval-visits}

visits <- mnmdb$query_table("Visits") %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups()

eva_print_visits <- function() {
  visits %>%
    dplyr::rename(
      grts = grts_address,
      lid = location_id,
      suid = sampleunit_id,
      agid = activity_group_id,
      fcid = fieldcalendar_id,
      archv = archive_version_id,
      vid = visit_id
    ) %>%
    dplyr::select(
      grts,
      type,
      lid,
      suid,
      fcid,
      vid,
      agid,
      date_start,
      archv,
      date_visit
    ) %>%
    arrange(type, date_start, agid) %>% 
    knitr::kable()
}

```


```{r loceval-infos}

infos <- mnmdb$query_table("LocationInfos") %>%
  filter(grts_address %in% grts)

eva_print_infos <- function() {
  infos %>%
    dplyr::rename(
      grts = grts_address,
      liid = locationinfo_id,
      lid = location_id,
      inaccess = accessibility_inaccessible,
      hints = recovery_hints
    ) %>%
    dplyr::select(
      liid,
      grts,
      lid,
      inaccess,
      hints
    ) %>%
    knitr::kable()
}

```


```{r loceval-lojos}

lojos <- mnmdb$query_table("LocationJournals") %>%
  filter(grts_address %in% grts)

eva_print_lojos <- function() {
  lojos %>%
    dplyr::rename(
      grts = grts_address,
      ljid = locationjournal_id,
      lid = location_id,
      src = source,
      agid = activity_group_id,
      tps = type_subset
    ) %>%
    dplyr::select(
      grts,
      ljid,
      tps,
      lid,
      src,
      agid
    ) %>%
    knitr::kable()
}

```


```{r loceval-replacements}

replacements <- mnmdb$query_table("Replacements") %>%
  filter(grts_address %in% grts)

eva_print_replacements <- function() {
  replacements %>%
    dplyr::rename(
      grts = grts_address,
      typ = type,
      suid = sampleunit_id,
      rep = grts_address_replacement,
      rank = replacement_rank,
      sel = is_selected,
      tsug = type_suggested
    ) %>%
    dplyr::select(
      grts,
      typ,
      rank,
      rep,
      sel,
      tsug
    ) %>%
    knitr::kable()
}

```



```{=latex} 
\pagebreak 
```

## sample units
```{r eva-print-sunit}
#| echo: false
eva_print_sunit()
```

## ofos
```{r eva-print-ofos}
#| echo: false
eva_print_ofos()
```

## field activities
```{r eva-print-cal}
#| echo: false
eva_print_facal()
```

```{r eva-print-visits}
#| echo: false
eva_print_visits()
```

## infos
```{r eva-print-infos}
#| echo: false
eva_print_infos()
```

## journals
```{r eva-print-lojos}
#| echo: false
eva_print_lojos()
```

## replacements
```{r eva-print-replacements}
#| echo: false
eva_print_replacements()
```


```{=latex} 
\pagebreak 
```


# MNMGWDB: `r as.character(grts)`

```{r noop-gw}
#| eval: false
#| echo: false
# source('080_connected_by_GRTS.R')
```

```{r gwdb-connection}
database_label <- "mnmgwdb"

### connect to database
mnmdb <- connect_mnm_database(
  config_filepath,
  database_mirror = glue::glue("{database_label}{suffix}"),
  user = "monkey",
  password = NA
)
# keyring::keyring_delete(keyring = "mnmdb_temp")
message(mnmdb$shellstring)

```

-- helpers

```{r helper-gwdb-activity-groups}

join_activity_groups <- function(df) {
  df %>% dplyr::left_join(
      mnmdb$query_columns(
        "GroupedActivities",
        c(
          "activity_group_id",
          "activity_group"
        )
      ) %>% dplyr::distinct(),
      by = dplyr::join_by(activity_group_id)
    ) %>%
  return()
}

```


```{r helper-query-activities-gwdb}

query_special_activity <- function(shorthand) {

  if (shorthand == "WIA") {
    table_label <- "InstallationVisits"
    id_column <- "installationvisit_id"
  } else if (shorthand == "CSA") {
    table_label <- "SamplingVisits"
    id_column <- "samplingvisit_id"
  } else if (shorthand == "SPA") {
    table_label <- "PositioningVisits"
    id_column <- "positioningvisit_id"
  }

  mnmdb$query_table(table_label) %>%
  dplyr::mutate(act = shorthand) %>%
  return()
}

```


-- The Backbone: Sample Unit // Sample Location

```{r sample-locations}

slocs <- mnmdb$query_table("SampleLocations") %>%
  filter(grts_address %in% grts)


loc_ids <- mnmdb$pull_column("Locations", "location_id")
loc_cells <- mnmdb$pull_column("LocationCells", "location_id")
loc_infos <- mnmdb$pull_column("LocationInfos", "location_id")

slocs <- slocs %>%
  mutate(
    has_loc = location_id %in% loc_ids,
    has_cell = location_id %in% loc_cells,
    has_infos = location_id %in% loc_infos,
    archived = isFALSE(is.na(archive_version_id))
  )

gw_print_slocs <- function() {
  slocs %>%
    dplyr::rename(
      slid = samplelocation_id,
      lid = location_id,
      replaced = is_replacement,
    ) %>%
    dplyr::select(
      grts_address,
      strata,
      domain_part,
      schemes,
      lid,
      slid,
      replaced,
      has_loc,
      has_cell,
      has_infos,
      archived
    ) %>%
    t() %>% 
    knitr::kable()
}

```


-- The Work: Calendar and Visits

```{r fieldwork-calendar}

fwcal <- mnmdb$query_table("FieldworkCalendar") %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups() # %>%
  # left_join(
  #   mnmdb$query_table("Visits"),
  #   by = join_by(fieldworkcalendar_id),
  #   suffix = c("", "_vis")
  # )

gw_print_fwcal <- function() {
  fwcal %>%
    dplyr::rename(
      grts = grts_address,
      fcid = fieldworkcalendar_id,
      slid = samplelocation_id,
      agid = activity_group_id,
      frz = is_frozen,
      archv = archive_version_id,
      done_p = done_planning
    ) %>%
    dplyr::select(
      grts,
      stratum,
      slid,
      fcid,
      agid,
      activity_group,
      date_start,
      frz,
      archv,
      # teammember_assigned,
      # date_visit_planned,
      done_p
    ) %>%
    arrange(stratum, date_start, agid) %>% 
    knitr::kable()
}

```

```{r visits-gwdb}

visits <- mnmdb$query_table("Visits") %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups()

gw_print_visits <- function() {
  visits %>%
    dplyr::rename(
      grts = grts_address,
      lid = location_id,
      slid = samplelocation_id,
      agid = activity_group_id,
      fcid = fieldworkcalendar_id,
      archv = archive_version_id,
      vid = visit_id,
      tid = teammember_id
    ) %>%
    dplyr::select(
      grts,
      stratum,
      lid,
      slid,
      fcid,
      vid,
      agid,
      date_start,
      archv,
      tid,
      issues,
      date_visit
    ) %>%
    arrange(stratum, date_start, agid) %>% 
    knitr::kable()
}

```



```{r special-activities-gwdb}

activities <- bind_rows(
    query_special_activity("WIA"),
    query_special_activity("CSA"),
    query_special_activity("SPA")
  ) %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups()

gw_print_special_activities <- function() {
  activities %>%
    dplyr::rename(
      grts = grts_address,
      slid = samplelocation_id,
      agid = activity_group_id,
      fcid = fieldworkcalendar_id,
      vid = visit_id,
    ) %>%
    dplyr::select(
      act,
      grts,
      stratum,
      fcid,
      vid,
      agid,
      date_start
    ) %>%
    arrange(stratum, date_start, agid) %>% 
    knitr::kable()
}

```


```{r location-infos-gwdb}

infos <- mnmdb$query_table("LocationInfos") %>%
  filter(grts_address %in% grts)

gw_print_infos <- function() {
  infos %>%
    dplyr::rename(
      grts = grts_address,
      liid = locationinfo_id,
      lid = location_id,
      inaccess = accessibility_inaccessible,
      hints = recovery_hints,
      tina1 = watina_code_1,
      tina2 = watina_code_2
    ) %>%
    dplyr::select(
      liid,
      grts,
      lid,
      inaccess,
      hints,
      tina1,
      tina2
    ) %>%
    knitr::kable()
}
```


```{r gw-lojos}

lojos <- mnmdb$query_table("LocationJournals") %>%
  filter(grts_address %in% grts)

gw_print_lojos <- function() {
  lojos %>%
    dplyr::rename(
      grts = grts_address,
      ljid = locationjournal_id,
      lid = location_id,
      src = source,
      agid = activity_group_id,
      types = type_subset
    ) %>%
    dplyr::count(
      grts,
      types,
      lid,
      src,
      agid
    ) %>%
    knitr::kable()
}

```



```{r gw-replacements}


repdat <- mnmdb$query_table("ReplacementData") %>%
  filter((grts_address_original %in% grts) | (grts_address_replacement %in% grts))

gw_print_replacement <- function() {
  repdat %>%
    dplyr::rename(
      grts = grts_address_original,
      rep = grts_address_replacement,
      ldat = loceval_date,
      slid = samplelocation_id
    ) %>%
    dplyr::select(
      type,
      grts,
      rep,
      ldat,
      slid
    ) %>%
    knitr::kable()
}

```



```{=latex} 
\pagebreak 
```

# Overview: `r as.character(grts)`

## sample location

```{r print-sloc-gwdb}
#| echo: false
gw_print_slocs()
```


## calendar

```{r print-fwcal-gwdb}
#| echo: false
gw_print_fwcal()
```


## visits

```{r print-visit-gwdb}
#| echo: false
gw_print_visits()
```

special activities (well installation, chem sampling, positioning)

```{r print-special-activities-gwdb}
#| echo: false
gw_print_special_activities()
```

## location infos

```{r print-infos-gwdb}
#| echo: false
gw_print_infos()
```

## location journals

```{r gw-print-lojos}
#| echo: false
gw_print_lojos()
```

## replacement
```{r print-replacements-gwdb}
#| echo: false
gw_print_replacement()
```



# MNMSURFDB: `r as.character(grts)`

```{r noop-surf}
#| eval: false
#| echo: false
# source('080_connected_by_GRTS.R')
```

```{r surfdb-connection}
database_label <- "mnmsurfdb"

### connect to database
mnmdb <- connect_mnm_database(
  config_filepath,
  database_mirror = glue::glue("{database_label}{suffix}"),
  user = "monkey",
  password = NA
)
# keyring::keyring_delete(keyring = "mnmdb_temp")
message(mnmdb$shellstring)

```

-- helpers

```{r helper-surfdb-activity-groups}

join_activity_groups <- function(df) {
  df %>% dplyr::left_join(
      mnmdb$query_columns(
        "GroupedActivities",
        c(
          "activity_group_id",
          "activity_group"
        )
      ) %>% dplyr::distinct(),
      by = dplyr::join_by(activity_group_id)
    ) %>%
  return()
}

```


```{r helper-query-activities-surfdb}

query_special_activity <- function(shorthand) {

  if (shorthand == "LOT") {
    table_label <- "LoticVisits"
    id_column <- "loticvisit_id"
  } else if (shorthand == "LENT") {
    table_label <- "LenticVisits"
    id_column <- "lenticvisit_id"
  } else if (shorthand == "OTH") {
    table_label <- "OtherVisits"
    id_column <- "othervisit_id"
  }

  mnmdb$query_table(table_label) %>%
  dplyr::mutate(act = shorthand) %>%
  return()
}

```


-- The Backbone: Sample Unit // Sample Location

```{r sample-units-surfdb}

units <- mnmdb$query_table("SampleUnits") %>%
  filter(grts_address %in% grts)


loc_ids <- mnmdb$pull_column("Locations", "location_id")
loc_cells <- mnmdb$pull_column("LocationCells", "location_id")
loc_infos <- mnmdb$pull_column("LocationInfos", "location_id")

units <- units %>%
  mutate(
    has_loc = location_id %in% loc_ids,
    has_cell = location_id %in% loc_cells,
    has_infos = location_id %in% loc_infos,
    archived = isFALSE(is.na(archive_version_id))
  )

surf_print_slocs <- function() {
  units %>%
    dplyr::rename(
      suid = sampleunit_id,
      lid = location_id,
      replaced = is_replacement,
    ) %>%
    dplyr::select(
      grts_address,
      stratum,
      domain_part,
      schemes,
      lid,
      suid,
      replaced,
      has_loc,
      has_cell,
      has_infos,
      archived
    ) %>%
    t() %>% 
    knitr::kable()
}

```


-- The Work: Calendar and Visits

```{r field-calendar}

fwcal <- mnmdb$query_table("FieldCalendar") %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups() # %>%

surf_print_fwcal <- function() {
  fwcal %>%
    dplyr::rename(
      grts = grts_address,
      fcid = fieldcalendar_id,
      suid = sampleunit_id,
      agid = activity_group_id,
      frz  = is_frozen,
      archv = archive_version_id,
      done_p = done_planning
    ) %>%
    dplyr::select(
      grts,
      stratum,
      suid,
      fcid,
      agid,
      activity_group,
      date_start,
      frz,
      archv,
      # teammember_assigned,
      # date_visit_planned,
      done_p
    ) %>%
    arrange(stratum, date_start, agid) %>% 
    knitr::kable()
}

```

```{r visits-surfdb}

visits <- mnmdb$query_table("Visits") %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups()

surf_print_visits <- function() {
  visits %>%
    dplyr::rename(
      grts = grts_address,
      lid = location_id,
      suid = sampleunit_id,
      agid = activity_group_id,
      fcid = fieldcalendar_id,
      archv = archive_version_id,
      vid = visit_id,
      tid = teammember_id
    ) %>%
    dplyr::select(
      grts,
      stratum,
      lid,
      suid,
      fcid,
      vid,
      agid,
      date_start,
      archv,
      tid,
      issues,
      date_visit
    ) %>%
    arrange(stratum, date_start, agid) %>% 
    knitr::kable()
}

```



```{r special-activities-surfdb}

activities <- bind_rows(
    query_special_activity("LOT"),
    query_special_activity("LENT"),
    query_special_activity("OTH")
  ) %>%
  filter(grts_address %in% grts) %>%
  join_activity_groups()

surf_print_special_activities <- function() {
  activities %>%
    dplyr::rename(
      grts = grts_address,
      suid = sampleunit_id,
      agid = activity_group_id,
      fcid = fieldcalendar_id,
      vid = visit_id,
    ) %>%
    dplyr::select(
      act,
      grts,
      stratum,
      fcid,
      vid,
      agid,
      date_start
    ) %>%
    arrange(stratum, date_start, agid) %>% 
    knitr::kable()
}

```


```{r location-infos-surfdb}

infos <- mnmdb$query_table("LocationInfos") %>%
  filter(grts_address %in% grts)

surf_print_infos <- function() {
  infos %>%
    dplyr::rename(
      grts = grts_address,
      liid = locationinfo_id,
      lid = location_id,
      inaccess = accessibility_inaccessible,
      hints = recovery_hints
    ) %>%
    dplyr::select(
      liid,
      grts,
      lid,
      inaccess,
      hints
    ) %>%
    knitr::kable()
}
```


```{r surf-lojos}

lojos <- mnmdb$query_table("LocationJournals") %>%
  filter(grts_address %in% grts)

surf_print_lojos <- function() {
  lojos %>%
    dplyr::rename(
      grts = grts_address,
      ljid = locationjournal_id,
      lid = location_id,
      src = source,
      agid = activity_group_id,
      tps = type_subset
    ) %>%
    dplyr::select(
      grts,
      ljid,
      tps,
      lid,
      src,
      agid
    ) %>%
    knitr::kable()
}

```



```{r surf-replacements}


repdat <- mnmdb$query_table("ReplacementData") %>%
  filter((grts_address_original %in% grts) | (grts_address_replacement %in% grts))

surf_print_replacement <- function() {
  repdat %>%
    dplyr::rename(
      typ = type,
      grts = grts_address_original,
      rep = grts_address_replacement,
      ldate = loceval_date,
      suid = sampleunit_id
    ) %>%
    dplyr::select(
      typ,
      grts,
      rep,
      ldate,
      suid
    ) %>%
    knitr::kable()
}

```



```{=latex} 
\pagebreak 
```

# Overview: `r as.character(grts)`

## sample units

```{r print-suints-surfdb}
#| echo: false
surf_print_slocs()
```


## calendar

```{r print-fwcal-surfdb}
#| echo: false
surf_print_fwcal()
```


## visits

```{r print-visit-surfdb}
#| echo: false
surf_print_visits()
```

special activities (well installation, chem sampling, positioning)

```{r print-special-activities-surfdb}
#| echo: false
surf_print_special_activities()
```

## location infos

```{r print-infos-surfdb}
#| echo: false
surf_print_infos()
```

## location journals

```{r surf-print-lojos}
#| echo: false
surf_print_lojos()
```

## replacement
```{r print-replacements-surfdb}
#| echo: false
surf_print_replacement()
```
