---
title: "Data Update: GroupedActivities"
date: "20260619"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---


# Changelog

- 20260619 init: preview REP 0.17.0 -> `SURF_03.4_LENTIC`


# Preparations

## libraries and variables

```{r libraries}

# libraries
source("MNMLibraryCollection.R")
load_database_interaction_libraries()

# the database connection object
source("MNMDatabaseConnection.R")

# more specific database tools
source("MNMDatabaseToolbox.R")


# library("mapview") # debugging only
# mapviewOptions(platform = "mapdeck")

```


## info stream from REP


```{r source-code-snippets}

tic <- function(toc) round(Sys.time() - toc, 1)
toc <- Sys.time()

snippet_base_path <<- rprojroot::find_root(rprojroot::is_git_root)
# # TEMPORARY adjustment pointing to adjacent branch (wip)
# snippet_base_path <<- normalizePath(file.path(snippet_base_path, "..", "n2khab-mne-monitoring_support"))

fresh_snippet_path <- file.path("data", "fresh_snippet_workspace.RData")
reload_rep_code_snippets(fresh_snippet_path)
message(glue::glue("Good morning!
  Loading the REP data and snippets took {tic(toc)} seconds today."
))


# grts - geometry - relation
grts_mh <- n2khab::read_GRTSmh()

grts_mh_index <- dplyr::tibble(
    id = seq_len(terra::ncell(grts_mh)),
    grts_address = values(grts_mh)[, 1]
  ) %>%
  dplyr::filter(!is.na(grts_address))


# check REP data
verify_rep_objects()

if (nrow(different_checksums) > 0) {
  knitr::kable(different_checksums)
}

```



## database connection


```{r connect-databases}

database <- "loceval"
# suffix <- ""
# suffix <- "-staging"
suffix <- "-testing"


config_filepath <- file.path("./mnm_database_connection.conf")
# connect loceval
locevaldb_mirror <- glue::glue("{database}{suffix}")

locevaldb <- connect_mnm_database(
  config_filepath,
  database_mirror = locevaldb_mirror
) 
# keyring::keyring_delete(keyring = "mnmdb_temp")

```


```{r upd-casc-lku}

message(glue::glue("connected: psql {locevaldb$shellstring}"))
# update_cascade_lookup <- parametrize_cascaded_update(locevaldb)

```


## version

:::{callout-warning}
Latest / new version must already be on the server.
:::

```{r query-version-id}
version_id <- locevaldb$load_latest_version_id()
```


# Load Data

## new REP

```{r find-secc-activities}
activities %>% 
  filter(activity %in% c("SURFLENTSECC", "SURFLOTSECC"))

activity_sequences %>%
  distinct(activity_group, activity) %>% 
  filter(activity %in% c("SURFLENTSECC", "SURFLOTSECC"))

field_activity_sequences %>%
  filter(field_activity %in% c("SURFLENTSECC", "SURFLOTSECC"))

```

```{r load-new-grouped-activities}

activity_group_lookup <-
  activity_sequences %>%
    distinct(activity_group, activity)

grouped_activities_rep <-
  activities %>%
  left_join(
    activity_group_lookup,
    join_by(activity),
    relationship = "one-to-many"
  )


# TODO persistent IDs
grouped_activities_rep <- grouped_activities_rep %>%
  mutate_at(
    vars(activity_group, activity, activity_name, protocol),
    as.character
  ) %>%
  mutate(
    activity_group = ifelse(is.na(activity_group), activity, activity_group)
  )
# %>% select(activity, activity_group) %>% tail(10) %>% knitr::kable()


grouped_activities_rep <- grouped_activities_rep %>%
  arrange(activity) %>%
  group_by(activity) %>%
  mutate(activity_id = cur_group_id()) %>%
  ungroup %>%
  arrange(activity_group) %>%
  group_by(activity_group) %>%
  mutate(activity_group_id = cur_group_id()) %>%
  ungroup %>%
  arrange(activity_group, activity) %>%
  group_by(
    activity_group,
    activity
  ) %>%
  mutate(grouped_activity_id = cur_group_id()) %>%
  ungroup %>%
  relocate(
    grouped_activity_id,
    activity_group_id,
    activity_group,
    activity_id,
    activity,
    .before = 1
  )


# tag activities for biotic location evaluation
source(here::here(
  "metadata",
  "associate_grouped_activities_with_fieldtaskforces.R"
))

grouped_activities_rep %<>% associate_grouped_activities_with_fieldtaskforces()

```


:::{.callout-warning}
Columns `activity_group_id`, `activity_id`, and `grouped_activity_id` of the REP is not real; it is counted above as it was counted in the very first upload.
:::

```{r remove-false-id-columns}
grouped_activities_rep %<>% 
  select(-ends_with("_id"))
```

## database status quo

```{r database-load-status-quo}

existing_grouped_activities <- locevaldb$query_table("GroupedActivities") %>% 
  arrange(activity_group, activity) %>% 
  relocate(activity_group, activity)

```


# Comparison

## Ensemble

```{r compare-grouped-activities}

# waldo::compare(
#   grouped_activities_rep,
#   existing_grouped_activities %>%
#     select(tidyselect::all_of(names(grouped_activities_rep)))
# )
#
#

# novel GAs: in the REP, but not in the DB
novel_grouped_activities <- grouped_activities_rep %>% 
  anti_join(
    existing_grouped_activities,
    by = join_by(activity_group, activity)
  )

novel_grouped_activities %>%
  select(activity_group, activity) %>%
  knitr::kable()


# obsolete GAs: in the DB, but not in the REP any more
obsolete_grouped_activities <- existing_grouped_activities %>% 
  anti_join(
    grouped_activities_rep,
    by = join_by(activity_group, activity)
  )

obsolete_grouped_activities %>% 
  select(
    grouped_activity_id,
    activity_group_id, activity_group,
    activity_id, activity,
    archive_version_id
  ) %>%
  knitr::kable()

```

## A Complicated Two-Level Indexing System

The whole database is indexed on on `activity_group` / `activity_group_id`.

```{r distinct-activity-groups}
activity_groups_rep <- grouped_activities_rep %>%
  distinct(activity_group)

activity_groups_db <- existing_grouped_activities %>%
  distinct(activity_group, activity_group_id)

```


```{r compare-grouped-activities}

# novel AGs: in the REP, but not in the DB
novel_groups <- activity_groups_rep %>% 
  anti_join(
    activity_groups_db,
    by = join_by(activity_group)
  )

novel_groups %>%
  knitr::kable()


# obsolete AGs: in the DB, but not in the REP any more
obsolete_groups <- activity_groups_db %>% 
  anti_join(
    activity_groups_rep,
    by = join_by(activity_group)
  )

obsolete_groups %>% 
  knitr::kable()

```




# join protocol id

```{r join-protocol-id}
stop("not ready for this.")

protocol_lookup <- locevaldb$query_columns(
    "Protocols",
    c("protocol_code", "protocol_version", "protocol_id")
  ) %>%
  group_by(protocol_code) %>%
  filter(protocol_version == max(protocol_version)) %>%
  ungroup() %>% 
  rename(protocol = protocol_code) %>%
  select(-protocol_version)

# protocol_lookup %>%
#   count(protocol) %>% arrange(desc(n))


grouped_activities_new <- grouped_activities %>%
  left_join(
    protocol_lookup,
    by = join_by(protocol),
    relationship = "many-to-one",
    na_matches = "never"
  ) %>% select(-protocol) %>%
  arrange(activity_group, activity) %>%
  relocate(activity_group, activity)


```

# Manual Flow

```{r export-manually}
existing_grouped_activities %>%
  left_join(
    locevaldb$query_columns(
      "Protocols", c("protocol_id", "protocol_code", "protocol_version")
    ),
    by = join_by(protocol_id)
  ) %>% 
  write.table(
    file = "./dumps/2026xx_grouped_activities_dump.csv",
    col.names = TRUE,
    dec = ".",
    sep = ";",
    quote = TRUE
  )

grouped_activities_rep %>% 
  write.table(
    file = "./dumps/2026xx_grouped_activities_rep.csv",
    col.names = TRUE,
    dec = ".",
    sep = ";",
    quote = TRUE
  )

```
