---
title: "REP Data Re-Upload - loceval"
date: "20260527"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---

# Changelog

- 20250924 init
- 20260309 refresher (incl. `Replacements` / `ReplacementArchives`)
- 20260319 REP update - major overhaul:
  - auxiliary FAGs
  - data fixing / freeze
- 20260527 REP update


# TODO


# Preparations

## structure changes
Download the latest structure sheets for the production mirror.
Otherwise, the list of update columns might be incomplete.

## sync staging mirror
  
```{sh sync-staging}
#| eval: false
pg_dump -U <backup_user> -h <host> -p <port> -d <database> -N tiger -N public -c > /tmp/<database>_db_dump.txt \
        && psql -U <database_user> -h <host> -p <port> -d <database>_staging -W < /tmp/<database>_db_dump.txt \
        && rm /tmp/<database>_db_dump.txt
```

## libraries and variables

```{r libraries}
# libraries
source("MNMLibraryCollection.R")
load_database_interaction_libraries()

# the database connection object
source("MNMDatabaseConnection.R")

# more specific database tools
source("MNMDatabaseToolbox.R")


# library("mapview") # debugging only
# mapviewOptions(platform = "mapdeck")

```


## info stream from REP

First, there is the `.RData` file, along with proccessing outcome of the code snippets.

::: {.callout-note snippets}
- check for changes on every update, e.g. with `meld`:
  `meld 020_fieldwork_organization/code_snippets.R 900_database_organization/401_snippet_selection.R`
- bake fresh snippets every morning:
  `Rscript 403_precalculate_fresh_snippets.R`
:::

```{r source-code-snippets}

tic <- function(toc) round(Sys.time() - toc, 1)
toc <- Sys.time()

snippet_base_path <<- rprojroot::find_root(rprojroot::is_git_root)
# # TEMPORARY adjustment pointing to adjacent branch (wip)
# snippet_base_path <<- normalizePath(file.path(snippet_base_path, "..", "n2khab-mne-monitoring_support"))

fresh_snippet_path <- file.path("data", "fresh_snippet_workspace.RData")
reload_rep_code_snippets(fresh_snippet_path)
message(glue::glue("Good morning!
  Loading the REP data and snippets took {tic(toc)} seconds today."
))

verify_rep_objects()

if (nrow(different_checksums) > 0) {
  knitr::kable(different_checksums)
}

```


## database connection


```{r connect-databases}

database <- "loceval"
config_filepath <- file.path("./mnm_database_connection.conf")
# suffix <- ""
suffix <- "-staging"


# connect loceval
locevaldb_mirror <- glue::glue("{database}{suffix}")

locevaldb <- connect_mnm_database(
  config_filepath,
  database_mirror = locevaldb_mirror
) 
# keyring::keyring_delete(keyring = "mnmdb_temp")

message(glue::glue("connected: psql {locevaldb$shellstring}"))
update_cascade_lookup <- parametrize_cascaded_update(locevaldb)

```


## dump all data, for safety

```{r step-1-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")

if (isFALSE(grepl("-staging", locevaldb_mirror))) {
  locevaldb$dump_all(
    here::here("dumps", glue::glue("rep_pre_update_{locevaldb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```


# Gather and Upload - locevaldb

## database versioning

```{r version}

if (FALSE) {

  # manually set a new version
  # the first part indicates the "snippet" version tag, the second one the REP tag.
  # see:
  #   - https://github.com/inbo/n2khab-mne-monitoring/tags
  #   - https://github.com/inbo/n2khab-mne-designs/tags
  # version_tag <- "≤v0.11.0_poc0.13.1"
  # version_tag <- "v0.12.0_poc0.14.0"
  # version_tag <- "v0.12.0_rvp0.14.0" # data_iteration = 2
  # version_tag <- "snip:0.15.0_rep:0.15.0" # data_iteration = 1
  # version_tag <- "snip:0.15.0_rep:0.15.0" # data_iteration = 1
  # version_tag <- "snip:0.15.1_rep:0.15.0" # data_iteration = 1

  version_tag <- "snip:0.16_rep:0.16" # data_iteration = 1
  version_notes <-
    "REP + snippets update 0.16"
  version_date_applied <- as.integer(format(Sys.time(), "%Y%m%d"))
  version_date_fixing <- as.Date("2025-12-31")

  version_id <- locevaldb$tag_new_version(
    new_version_tag = version_tag,
    new_version_notes =  version_notes,
    new_date_applied = version_date_applied,
    new_date_fixing = version_date_fixing
  )

  # SELECT * FROM "metadata"."Versions";

} else {
  # per default, the latest version is taken
  version_id <- locevaldb$load_latest_version_id()
}

if (FALSE) {
  # ... ad hoc / testing: delete version again
  table_label <- "Versions"
  data_iteration = 2
  glue::glue("
  DELETE FROM {locevaldb$get_namestring(table_label)}
  WHERE version_tag = '{version_tag}'
    AND data_iteration = {data_iteration}
  ;
  ")
  # locevaldb$set_sequence_key("Versions", "max", verbose = TRUE)
  
  glue::glue("
  UPDATE {locevaldb$get_namestring(table_label)}
  SET notes = E'{version_notes}',
      date_fixing = '{version_date_fixing}'
  WHERE version_tag = '{version_tag}'
    AND data_iteration = {data_iteration}
  ;
  ")

  # 'SELECT * FROM "metadata"."Versions";'
    
}

# TODO: I still have to make up my mind whether to archive everything.
#       For now, I will preliminarily keep it with an "archive_id" column.
```



# Protocols, Activities, TeamMembers

:::{callout-warning}
Any news?
Now is the chance!
:::



# Let's Do This

## prerequisite_lookups

```{r gather-lookups}

n2khabstrata_lookup <- locevaldb$query_lookup(
  "N2kHabStrata",
  characteristic_columns = c("stratum")
)

activity_groupid_lookup <- locevaldb$query_columns(
    "GroupedActivities",
    c("activity_group", "activity_group_id")
  ) %>%
  distinct()

```


```{r load-activities}

loceval_field_activities_db <- locevaldb$query_table("GroupedActivities") %>%
  filter(is_loceval_activity, is_field_activity) %>%
  distinct(activity_group, activity, fag_is_auxiliary, fag_is_preponable)

```


## Freeze Past Fixture

Here, it would be time to generate the latest FREEZE,
but only if the `date_fixing` changed in the latest `"metadata"."Versions"`.

TODO: new columns to work into the freeze (need to get set with a correct value)
+ `wait_obsolete_types` (20260521)

```{r generate_freeze_calendar}
#| eval: false

out <- processx::run(
  "Rscript",
  c("405_freeze_calendar.R", suffix),
  spinner = TRUE,
  echo = TRUE
  )
# message(out$stderr)

```


```{r load-freeze}

loceval_freeze <- read.csv(
    file = file.path("sideload", glue::glue("freeze_locevaldb{suffix}.csv"))
  ) %>%
  mutate(across(c(
      date_start,
      date_end,
      mhq_assessment_date
    ), as.Date)
  ) %>% 
  mutate(across(c(
      previous_notes
    ), as.character)
  )

# loceval_freeze %>% glimpse()
# loceval_freeze %>%
#   filter(grts_address == 6110) %>% 
#   glimpse()
```


## Sample Units

TODO: need to sideload future units from LocationAssessments

```{r assemble-sample-units}
# `date_start`, `date_end`, `field_activity_group`, and `rank`

sample_unit_columns <- c(
  "grts_address",
  "type",
  "schemes",
  # "schemes_served_all", # renamed to schemes
  "grts_join_method",
  # "is_current_occasion", # TODO
  "is_forest",
  "in_mhq_samples",
  "mhq_assessment_date", 
  "has_mhq_assessment", 
  "domain_part",
  "scheme_ps_targetpanels",
  "previous_notes"
)

sample_units_updated <- fag_stratum_grts_calendar_shortterm_attribs %>%
  rename_grts_address_final_to_grts_address(keep_original = FALSE) %>%
  # only retain the activities for biotic tasks
  # otherwise there are duplicates
  #     (`schemes` filled differently on other activities)
  semi_join(
    loceval_field_activities_db,
    by = join_by(field_activity_group == activity_group)
  ) %>% 
  rename(
    has_mhq_assessment = last_type_assessment_in_field,
    mhq_assessment_date = last_type_assessment,
    schemes = schemes_served_all
  ) %>%
  relocate(grts_address) %>%
  relocate(grts_join_method, .after = grts_address) %>%
  mutate(
    previous_notes = NA # FUTURE TODO
  ) %>% 
  rename(type = stratum) %>% 
  distinct(!!!rlang::syms(sample_unit_columns)) %>% 
  mutate(across(c(
      grts_join_method,
      scheme_ps_targetpanels,
      schemes,
      type,
      domain_part,
      previous_notes
    ), as.character)
  )


# sample_units_updated %>% glimpse()
# sample_units_updated %>% distinct(grts_address, type) %>% nrow()

```


Re-establish SampleUnits from `the freeze`.

::: {.callout-note}
Sample units can 

- appear (only pesent in `_updated`)
- disappear (only pesent in `_retained`)
- stay or change (pesent in *both*, before and after update).

We UNION the updated and retained; for *changed* units the novel plan (`_updated`) is the reference.
Association with old schemes is not relevant.

:::


```{r frozen-units}
# loceval_freeze %>% names()

sample_units_retained <- loceval_freeze %>%
  distinct(!!!rlang::syms(sample_unit_columns)) %>%
  anti_join(
    sample_units_updated,
    by = join_by(grts_address, type)
  )

sample_units_retained %>% 
  glimpse()

```


Join updated and frozen sample locations:

```{r combined_sample_units}

sample_units <- bind_rows(
  sample_units_retained,
  sample_units_updated
)

# sample_units %>% sample_n(3) %>% t() %>% knitr::kable()

```


## Locations

```{r assemble-locations}

locations_grts_collection <- bind_rows(
    locevaldb$query_columns("Locations", c("grts_address")),
    sample_units %>% select(grts_address),
    locevaldb$query_columns("LocationInfos", c("grts_address")),
    locevaldb$query_columns("LocationAssessments", c("grts_address")),
    locevaldb$query_columns("FieldActivityCalendar", c("grts_address")),
    locevaldb$query_columns("Visits", c("grts_address")),
    locevaldb$query_columns("Replacements", c("grts_address_replacement", "is_selected")) %>% 
      filter(is_selected) %>%
      select(-is_selected) %>% 
      rename(grts_address = grts_address_replacement)
  ) %>%
  mutate(grts_address = as.integer(grts_address)) %>%
  distinct() 

# locations_grts_collection %>% 
#   count(grts_address) %>%
#   arrange(desc(n))

# join geometry column
grts_mh <- n2khab::read_GRTSmh()

grts_mh_index <- dplyr::tibble(
    id = seq_len(terra::ncell(grts_mh)),
    grts_address = values(grts_mh)[, 1]
  ) %>%
  dplyr::filter(!is.na(grts_address))

locations <- locations_grts_collection %>% 
  add_point_coords_grts(
    grts_var = "grts_address",
    spatrast = grts_mh,
    spatrast_index = grts_mh_index
  )

sf::st_geometry(locations) <- "wkb_geometry"


# table_label <- "Locations"
# data_nouveau <- locations %>% sf::st_drop_geometry()# %>% select(-wkb_geometry)
# index_column <- locevaldb$get_primary_key(table_label)
# characteristic_columns <- c("grts_address")
# 
# distribution <- categorize_data_update(
#   mnmdb = locevaldb,
#   table_label = table_label,
#   data_future = data_nouveau,
#   input_precedence_columns = precedence_columns[[table_label]],
#   characteristic_columns = characteristic_columns,
#   exclude_columns = c("wkb_geometry")
# )
# print_category_count(distribution, table_label)
# 
# # distribution$to_upload %>% knitr::kable()

```


```{r update-locations}
locations_lookup <- update_cascade_lookup(
  table_label = "Locations",
  new_data = locations,
  index_columns = c("location_id"),
  characteristic_columns = c("grts_address"),
  tabula_rasa = FALSE,
  verbose = TRUE
)


```

20260511: the "redistribution" seems to ignore empty geometries

```{r update-locations-erroneous}
#| eval: false

# locations_lookup <- redistribute_calendar_data(
#   mnmdb = locevaldb,
#   table_label = table_label,
#   distribution = distribution,
#   index_columns = c(index_column),
#   characteristic_columns = characteristic_columns,
#   skip = list("update" = FALSE, "upload" = FALSE, "archive" = TRUE)
# )


```


... and stitch
```{r reconnect-locations-to-sampleunits}

out <- processx::run(
  "Rscript",
  c("102_re_link_foreign_keys.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```


## location cells

```{r new-location-cells}

units_cell_polygon[["grts_address_final"]] <-
  as.integer(units_cell_polygon[["grts_address_final"]])

# unit geometries (cells):
location_cells <-
  units_cell_polygon %>%
  inner_join(
    locations_lookup,
    by = join_by(grts_address_final == grts_address),
    relationship = "one-to-many",
    unmatched = "drop"
  ) %>%
  select(-grts_address_final) %>%
  relocate(geometry, .after = last_col())

sf::st_geometry(location_cells) <- "wkb_geometry"
# glimpse(location_cells)

message("________________________________________________________________")
message(glue::glue("DELETE/INSERT of metadata.LocationCells"))

locevaldb$execute_sql(
  glue::glue('DELETE  FROM "metadata"."LocationCells";'),
  verbose = TRUE
)

locevaldb$insert_data(
  table_label = "LocationCells",
  upload_data = location_cells
)

```


## Sample Units

```{r porcess-sample-units}

if ("location_id" %in% names(sample_units)) {
  # should not be the case in a continuous script;
  # this is extra safety for debugging and de-serial execution
  sample_units <- sample_units %>%
    select(-location_id)#, -location_id.x, -location_id.y)
}
sample_units <- sample_units %>%
  left_join(
    locevaldb$query_columns("Locations", c("grts_address", "location_id")),
    by = join_by(grts_address),
    relationship = "many-to-one"
  ) %>%
  distinct()

# sample_units %>%
#   filter(grts_address == 22107438) %>%
#   t() %>% knitr::kable()

table_label <- "SampleUnits"
data_nouveau <- sample_units
characteristic_columns <- c("grts_address", "type") # , "location_id"
index_column <- locevaldb$get_primary_key(table_label)
# locevaldb$query_columns(table_label, characteristic_columns)

distribution <- categorize_data_update(
  mnmdb = locevaldb,
  table_label = table_label,
  data_future = data_nouveau,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = characteristic_columns,
)
print_category_count(distribution, table_label)

# distribution$changed
# distribution$to_archive
# distribution$reactivate
# distribution$to_archive
# distribution$to_upload

# TODO is -staging on the latest state?

```





```{r update-sample-locations}

distribution$to_upload <- distribution$to_upload %>% 
  mutate(
    # log_user = "maintenance",
    # log_update = convert_timestamp_to_ms_character(Sys.time()),
    replacement_ongoing = FALSE,
    is_replaced = FALSE,
    type_is_absent = FALSE
  ) 

sampleunits_lookup <- redistribute_calendar_data(
  mnmdb = locevaldb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = characteristic_columns,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)

```


## FieldActivityCalendar

Starting at `fieldwork_shortterm_prioritization_by_stratum`, which is already filtered and prioritized.


```{r assemble-fieldwork-calendar}

# sampleunits_lookup <- locevaldb$query_columns("SampleUnits", c("grts_address", "type", "sampleunit_id"))

fieldwork_calendar_columns <- c(
  "grts_address",
  "type",
  "sampleunit_id",
  "activity_group_id",
  "activity_rank",
  "date_start",
  "date_end",
  "date_interval",
  "priority",
  "wait_any",
  "wait_watersurface",
  "wait_3260",
  "wait_7220",
  "wait_floating",
  "wait_obsolete_types",
  "is_frozen"
)


fieldcalendar_characols <- c(
  "grts_address",
  "type",
  "activity_group_id",
  "date_start"
)



fieldwork_calendar_updated <- fieldwork_shortterm_prioritization_by_stratum %>%
  rename_grts_address_final_to_grts_address() %>%
  rename(type = stratum) %>%
  inner_join(
    sampleunits_lookup,
    by = join_by(grts_address, type),
    relationship = "many-to-one"
  ) %>%
  relocate(grts_address, type, sampleunit_id) %>%
  rename(
    activity_rank = rank,
    activity_group = field_activity_group
  ) %>%
  semi_join(loceval_field_activities_db, by = join_by(activity_group)) %>%
  left_join(
    activity_groupid_lookup,
    by = join_by(activity_group),
    relationship = "many-to-one"
  ) %>%
  select(-activity_group) %>%
  mutate(
    across(c(
        type,
        grts_join_method,
        date_interval,
        domain_part,
        date_interval
      ),
      as.character
    )
  ) %>%
  mutate(is_frozen = FALSE) %>% 
  select(!!!rlang::syms(fieldwork_calendar_columns))

# fieldwork_calendar_updated %>% glimpse()

```


Normally, all calendar entries from the `freeze` have already be removed, so the `anti_join` is a no-op.


```{r assemble-fieldwork-calendar-freeze}

fieldwork_calendar_retained <- loceval_freeze %>%
  select(tidyselect::any_of(c(fieldwork_calendar_columns, "done_planning"))) %>% 
  anti_join(
    fieldwork_calendar_updated,
    by = join_by(!!!rlang::syms(fieldcalendar_characols))
  ) %>%
  select(-is_frozen) %>%
  mutate(is_frozen = TRUE) %>%
  left_join(
    loceval_field_activities_db %>%
      distinct(activity_group) %>% 
      left_join(activity_groupid_lookup, by = join_by(activity_group)) %>%
      select(activity_group_id) %>%
      mutate(is_loceval_activity = TRUE),
    by = join_by(activity_group_id)
  ) %>% 
  filter(done_planning | is_loceval_activity) %>%
  select(-done_planning, -is_loceval_activity)
  

# fieldwork_calendar_retained %>% glimpse()
# loceval_freeze %>% count(activity_group_id, done_planning, visit_done)

```



```{r union-fieldwork-calendar}

fieldwork_calendar_new <- bind_rows(
    fieldwork_calendar_retained,
    fieldwork_calendar_updated
  )

```


```{r stitch-fwcal-to-sunits}

# link FieldworkCalender back to SampleUnits
stitch_table_connection(
  mnmdb = locevaldb,
  table_label = "FieldActivityCalendar",
  reference_table = "SampleUnits",
  link_key_column = "sampleunit_id",
  lookup_columns = c("grts_address", "type")
)

```


Link dates of current calendar table to new calendar

```{r link-dates}

startdate_updates_happened <- associate_and_shift_start_dates(
  mnmdb = locevaldb,
  table_label = "FieldActivityCalendar",
  data_future = fieldwork_calendar_new,
  characteristic_columns = fieldcalendar_characols,
  other_table_labels = c("Visits")
) 

if (startdate_updates_happened) message("Startdate updates happened!")

```


```{r categorize-fieldworkcalendar}

table_label <- "FieldActivityCalendar"
data_nouveau <- fieldwork_calendar_new
characteristic_columns <- fieldcalendar_characols
index_column <- locevaldb$get_primary_key(table_label)
# data_nouveau %>% head(3) %>% t() %>% knitr::kable()
# data_nouveau %>% filter(grts_address == 1677870) %>% t() %>% knitr::kable()


distribution <- categorize_data_update(
  mnmdb = locevaldb,
  table_label = table_label,
  data_future = data_nouveau,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = characteristic_columns,
  exclude_columns = c("sampleunit_id") #, "fieldactivitycalendar_id") # , "archive_version_id"
)
print_category_count(distribution, table_label)

# distribution$changed %>% head(3) %>% knitr::kable()
# distribution$to_archive %>% filter(grts_address == 3202741) %>% t() %>% knitr::kable()
# distribution$reactivate %>% filter(grts_address == 3202741) %>% t() %>% knitr::kable()
```


```{r sync-fieldworkcalendar}

distribution$to_upload <- distribution$to_upload %>% 
  mutate(
    log_user = "maintenance",
    log_update = convert_timestamp_to_ms_character(Sys.time()),
    excluded = FALSE,
    no_visit_planned = FALSE,
    done_planning = FALSE,
    is_frozen = FALSE
  )


fieldworkcalendar_lookup <- redistribute_calendar_data(
  mnmdb = locevaldb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = characteristic_columns,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)


```



```{r re-inspect-fieldworkcalendar}

locevaldb$query_table("FieldActivityCalendar") %>% 
  count(is.na(sampleunit_id)) %>%
  knitr::kable()

# compare stored to true sample location
locevaldb$query_table("FieldActivityCalendar") %>%
  left_join(
    locevaldb$query_table("SampleUnits"),
    by = join_by(grts_address, type)
  ) %>%
  filter(sampleunit_id.x != sampleunit_id.y)

```


## Visits

```{r stitch-visits}

stitch_visits <- function() {
  # link Visits back to upstream tables
  stitch_table_connection(
    mnmdb = locevaldb,
    table_label = "Visits",
    reference_table = "FieldActivityCalendar",
    link_key_column = "fieldactivitycalendar_id",
    lookup_columns = c("grts_address", "type", "activity_group_id", "date_start")
  )
  
  stitch_table_connection(
    mnmdb = locevaldb,
    table_label = "Visits",
    reference_table = "SampleUnits",
    link_key_column = "sampleunit_id",
    lookup_columns = c("grts_address", "type")
  )
  
  stitch_table_connection(
    mnmdb = locevaldb,
    table_label = "Visits",
    reference_table = "Locations",
    link_key_column = "location_id",
    lookup_columns = c("grts_address")
  )
}
stitch_visits()

```


```{r assemble-new-visits}
# stop("WAIT which wone was it?")

visits_characols <- fieldcalendar_characols
# visits_characols <- c("fieldactivitycalendar_id", fieldcalendar_characols)

potential_visits <- fieldworkcalendar_lookup %>%
  select(
    !!!rlang::syms(c("fieldactivitycalendar_id", visits_characols))
  ) %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address)
  ) %>%
  mutate(
    log_user = "maintenance",
    log_update = convert_timestamp_to_ms_character(Sys.time()),
    visit_done = FALSE
  )


visits_upload <- potential_visits %>%
  anti_join(
    locevaldb$query_table("Visits"),
    by = join_by(!!!rlang::syms(fieldcalendar_characols))
  ) %>%
  left_join(
    sampleunits_lookup,
    by = join_by(grts_address, type)
  )

visits_lookup <- update_cascade_lookup(
  table_label = "Visits",
  new_data = visits_upload,
  index_columns = c("visit_id"),
  characteristic_columns = visits_characols,
  tabula_rasa = FALSE,
  verbose = TRUE
)

```


```{r post-update-check-visits}

locevaldb$query_table("Visits") %>% 
  count(is.na(fieldactivitycalendar_id)) %>%
  knitr::kable()

```


```{r reconnect-visits}

stitch_visits()


locevaldb$query_table("Visits") %>% 
  count(is.na(sampleunit_id), is.na(fieldactivitycalendar_id)) %>%
  knitr::kable()


```


archive visits of archived FWCals

```{r archive-visits-fwcal}

trgtab <- locevaldb$get_namestring("Visits")
srctab <- locevaldb$get_namestring("FieldActivityCalendar")
link_key_column <- "archive_version_id"
lookup_criteria <- c("TRGTAB.fieldactivitycalendar_id = SRCTAB.fieldactivitycalendar_id")

update_string <- glue::glue("
  UPDATE {trgtab} AS TRGTAB
    SET
      {link_key_column} = SRCTAB.{link_key_column}
    FROM {srctab} AS SRCTAB
    WHERE
     ({paste0(lookup_criteria, collapse = ') AND (')})
  ;")

locevaldb$execute_sql(update_string)

locevaldb$query_table("FieldActivityCalendar") %>%
  anti_join(
    locevaldb$query_table("Visits"),
    by = join_by(fieldactivitycalendar_id, archive_version_id)
  ) %>% nrow()


```



## LocationInfos

```{r update-locationinfos}

new_locinfos <- sample_units %>%
  distinct(
    grts_address
  ) %>%
  mutate(
    log_creator = "maintenance",
    log_creation = convert_timestamp_to_ms_character(Sys.time()),
    log_user = "maintenance",
    log_update = convert_timestamp_to_ms_character(Sys.time())
  )

new_locinfos <- new_locinfos %>%
  anti_join(
    locevaldb$query_table("LocationInfos"),
    by = join_by(grts_address)
  ) %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address),
  )


locationinfo_lookup <- update_cascade_lookup(
  table_label = "LocationInfos",
  new_data = new_locinfos,
  index_columns = c("locationinfo_id"),
  characteristic_columns = c("grts_address"),
  tabula_rasa = FALSE,
  verbose = TRUE
)
```


## landuse

```{r update-landuse}
update_landuse_in_locationinfos(locevaldb)
```



# Replacements

Updating local replacement candidates is tricky.

- If cells have been selected previously, they should not be overwritten.
- Type may be totally absent (`type_is_absent`). Then none of the replacements remains valid...
- ... unless new replacement candidates appear in case of changed habitat polygons.
- Inappropriateness of other cells is determined *en passant*, which is relevant information.
- Random order might change, but the information of prior visits must be retained.
- HOWEVER, there might be future `loceval` activities on the disapproved cells.

A simple solution is to freeze replacements for cells where `visit_done == TRUE`.
Only the others will be updated.

TODO we will have to re-activate/refresh the frozen replacement candidates later.


## prepare

```{r stitch-replacements}

# update the foreign key to match, for correct lookup
stitch_table_connection(
  mnmdb = locevaldb,
  table_label = "Replacements",
  reference_table = "SampleUnits",
  link_key_column = "sampleunit_id",
  lookup_columns = c("grts_address", "type")
)

# characteristic columns of replacement candidate cells
replacement_characols <- c(
    "grts_address",
    "type",
    "grts_address_replacement",
    "replacement_rank"
  )

```


## replacements archive

One could argue that "no message is also a message",
but for data efficiency I opt to rather only keep the 

```{r archive-previously-visited-replacements}

prior_loceval_visits <- locevaldb$query_table("Visits") %>%
  filter(visit_done) %>%
  semi_join(
    # only LOCEVAL activities are considered (not: LSVI)
    activity_groupid_lookup %>%
      filter(stringr::str_detect(activity_group, "LOCEVAL")),
    by = join_by(activity_group_id)
  ) %>% 
  select(grts_address, type, date_visit) # , date_start)

prior_loceval_visit_duplicate_check <- prior_loceval_visits %>% 
  count(grts_address, type, date_visit) %>%
  filter(n > 1)

if (nrow(prior_loceval_visit_duplicate_check) > 0) {
  prior_loceval_visit_duplicate_check %>% knitr::kable()
  stop("There are duplicate loceval visits (same date_visit on grts+type).")
}

# only the latest loceval visit will stay relevant for replacement
latest_loceval_visits <- prior_loceval_visits %>% 
  arrange(desc(date_visit)) %>% 
  group_by(grts_address, type) %>% 
  slice_head(n = 1)

previously_visited_replacements <- locevaldb$query_table("Replacements") %>%
  inner_join(
    latest_loceval_visits,
    by = join_by(grts_address, type),
    relationship = "many-to-one"
  ) %>% 
  select(-wkb_geometry) %>%
  filter(
    is_inappropriate
    | is_selected
    | (!is.na(type_suggested))
    | (implications_habitatmap)
    | (!is.na(notes))
  )



previously_visited_replacements %>%
  filter(grts_address %in% c(6110, 1118141, 1995222)) %>%
  t() %>% knitr::kable()

replacement_archives <- previously_visited_replacements %>%
  inner_join(
    locevaldb$query_columns(
      "SampleUnits",
      c(
        "sampleunit_id",
        "replacement_reason",
        "replacement_permanence",
        "type_is_absent"
        )
      ),
    by = join_by(sampleunit_id)
  ) %>%
  select(-replacement_id, -sampleunit_id) %>% 
  mutate(version_id = version_id)
 
glimpse(replacement_archives)

reparchs_characols = c(
    "grts_address",
    "grts_address_replacement",
    "type",
    "replacement_rank",
    "version_id"
  )

if (nrow(replacement_archives) > 0) {
  # previously_visited_replacements %>% select(starts_with("grts_address"))
  replacement_archives %>%
    count(!!!rlang::syms(reparchs_characols)) %>%
    arrange(desc(n))

  replacement_archive_lookup <- update_cascade_lookup(
    table_label = "ReplacementArchives",
    new_data = replacement_archives,
    index_columns = c("replacementarchive_id"),
    characteristic_columns = reparchs_characols,
    tabula_rasa = FALSE,
    verbose = TRUE
  )
}

```


## restore

In principle, we can sideload replacements.

```{r sideload-replacements}
# NOTE this is the place to sideload extra replacements
# e.g. the ones from the `archive`?

replacements_sideload <- load_table_sideload_content(
  mnmdb = locevaldb,
  table_label = "Replacements",
  characteristic_columns = c("grts_address", "type", "grts_address_replacement"),
  data_filepath = "sideload/loceval_replacements.csv",
  reload_previous = FALSE
)

```


Two original sources: 

- replacements from REP,
- sideloaded replacements

```{r new-replacements}

replacements_rep <- 
  stratum_schemepstargetpanel_spsamples_terr_replacementcells %>%
  select(stratum, grts_address, replacement_cells) %>%
  unnest(replacement_cells) %>%
  filter(!is.na(cellnr_replac)) %>%
  left_join(
    n2khab_strata,
    by = join_by(stratum),
    relationship = "many-to-many" # TODO
  ) %>%
  select(-stratum) %>%
  rename(
    cellnr_replacement = cellnr_replac,
    grts_address_replacement = grts_address_replac,
    replacement_rank = ranknr
  ) 
    
    
replacements <- bind_rows(
    replacements_rep,
    replacements_sideload 
  ) %>% 
  inner_join(
    sampleunits_lookup %>%
      select(type, grts_address, sampleunit_id),
    by = join_by(type, grts_address),
    relationship = "many-to-many", # TODO
    unmatched = "drop"
  )

```


Join the `ReplacementArchives` to see which have been visited before.
Keeping all relevant information from those previous Visits.

```{r join-previously-visited}

replacements_new <- replacements %>%
  left_join(
    previously_visited_replacements,
    by = join_by(!!!rlang::syms(replacement_characols)),
    suffix = c("", "_prev")
  ) %>%
  select(-replacement_id, -sampleunit_id_prev, -cellnr_replacement) %>%
  arrange(!!!rlang::syms(replacement_characols)) %>% 
  # mutate(replacement_id = seq_len(n())) %>%
  # relocate(replacement_id)
  mutate(
    is_inappropriate = coalesce(is_inappropriate_prev, is_inappropriate, FALSE),
    is_selected = coalesce(is_selected_prev, is_selected, FALSE),
    implications_habitatmap = coalesce(
      implications_habitatmap_prev,
      implications_habitatmap,
      FALSE
    ),
    notes = coalesce(notes_prev, notes),
    type_suggested = coalesce(type_suggested_prev, type_suggested)
  ) %>%
  select(
    -is_inappropriate_prev,
    -is_selected_prev,
    -implications_habitatmap_prev,
    -notes_prev,
    -type_suggested_prev,
    -date_visit
  )

# previously_visited_replacements %>% filter(is_selected)
# glimpse(replacements_new %>% filter(is_selected))
# glimpse(replacements_new %>% filter(!is.na(type_suggested)))
# glimpse(replacements_new %>% filter(!is.na(date_visit)))

replacements_upload <- replacements_new %>%
  add_point_coords_grts(
    grts_var = "grts_address_replacement",
    spatrast = grts_mh,
    spatrast_index = grts_mh_index
  )

sf::st_geometry(replacements_upload) <- "wkb_geometry"

# glimpse(replacements_upload)


# upload new replacements, TABULA RASA
replacements_lookup <- update_cascade_lookup(
  table_label = "Replacements",
  new_data = replacements_upload,
  index_columns = c("replacement_id"),
  characteristic_columns = replacement_characols,
  tabula_rasa = TRUE,
  verbose = TRUE
)

```

if it fails: `DELETE FROM "outbound"."Replacements";`


## connect

```{r stitch-previous-replacements}

trgtab <- locevaldb$get_namestring("SampleUnits")
srctab <- locevaldb$get_namestring("Replacements")
lookup_columns <- c("grts_address", "type")
link_key_column <- "replacement_id"

lookup_criteria <- unlist(lapply(
  lookup_columns,
  FUN = function(col) glue::glue("TRGTAB.{col} = SRCTAB.{col}")
))

srctab_query <- glue::glue("
  SELECT {paste0(lookup_columns, collapse = ', ')}, {link_key_column}
  FROM {srctab}
  WHERE is_selected
")

# reset reference
locevaldb$execute_sql(
 glue::glue("
   UPDATE {trgtab} AS TRGTAB
     SET
       {link_key_column} = NULL;
   "),
 verbose = TRUE
)

update_string <- glue::glue("
  UPDATE {trgtab} AS TRGTAB
    SET
      {link_key_column} = SRCTAB.{link_key_column}
    FROM ({srctab_query}) AS SRCTAB
    WHERE
     ({paste0(lookup_criteria, collapse = ') AND (')})
  ;"
)

locevaldb$execute_sql(update_string, verbose = TRUE)


```

to check: `SELECT * FROM "outbound"."SampleUnits" WHERE replacement_id IS NOT NULL;`


## replacement cells

```{r new-replacement-cells}

replacement_cell_rast <-
  locevaldb$pull_column(
    "Replacements",
    "grts_address_replacement"
  ) %>%
  filter_grtsraster_by_address(spatrast = grts_mh, spatrast_index = grts_mh_index)

set.names(replacement_cell_rast, "grts_address_replacement")

replacement_cell_polygons <-
  replacement_cell_rast %>%
  as.polygons(aggregate = FALSE) %>%
  sf::st_as_sf()

replacement_cells <- replacement_cell_polygons %>%
  # to prefer the tibble approach in sf, we need to convert forth and back
  as_tibble() %>%
  mutate(grts_address_replacement = as.integer(grts_address_replacement)) %>%
  # it appears that the CRS is actually retrieved from the tibble, but I don't
  # understand how (so the crs argument below isn't needed)
  st_as_sf(crs = "EPSG:31370")

replacement_cells <-
  replacement_cells %>%
  inner_join(
    replacements_lookup,
    by = join_by(grts_address_replacement),
    relationship = "one-to-many",
    unmatched = "drop"
  ) %>%
  select(replacement_id)

sf::st_geometry(replacement_cells) <- "wkb_geometry"

message("________________________________________________________________")
message(glue::glue("DELETE/INSERT of outbound.ReplacementCells"))

locevaldb$execute_sql(
  glue::glue('DELETE  FROM "outbound"."ReplacementCells";'),
  verbose = TRUE
)

locevaldb$insert_data(
  table_label = "ReplacementCells",
  upload_data = replacement_cells
)

```

# Habitat Map Polygons aka SampleUnitPolygons

```{r update-habitatmap-polygons}

sampleunits_for_polygons <- locevaldb$query_columns(
    "SampleUnits",
    c("grts_address", "type", "sampleunit_id")
  )

sampleunit_grts_cellcenters_for_polygons <- sampleunits_for_polygons %>%
  add_point_coords_grts(
    grts_var = "grts_address",
    spatrast = grts_mh,
    spatrast_index = grts_mh_index
  )

habmap_filepath <- file.path(
    "/data/sources/bwk_2025/"
  ) # actually, using the folder path is better
# terra::vect(habmap_filepath)

habmap_unique_polygons <- terra::vect(habmap_filepath) %>%
  .[terra::vect(sampleunit_grts_cellcenters_for_polygons)] %>%
  as.polygons() %>%
  sf::st_as_sf() %>%
  st_transform(31370) %>% 
  select(geometry)

# note that polygons are multiplicated with this method if
# they contain multiple sample units.
sampleunit_polygons <- cbind(
  sampleunit_grts_cellcenters_for_polygons %>%
    sf::st_drop_geometry(),
  habmap_unique_polygons[
  sampleunit_grts_cellcenters_for_polygons %>%
    sf::st_nearest_feature(habmap_unique_polygons)
  , ]
  ) %>%
  # (FM just copied this from FV)
  # to prefer the tibble approach in sf, we need to convert forth and back
  as_tibble() %>%
  # it appears that the CRS is actually retrieved from the tibble, but I don't
  # understand how (so the crs argument below isn't needed)
  st_as_sf(crs = "EPSG:31370") %>%
  select(sampleunit_id) %>%
  anti_join(
    # filter "waiting" types
    locevaldb$query_columns(
      "FieldActivityCalendar",
      c("sampleunit_id", "wait_any")
    ) %>%
    distinct() %>% 
    filter(wait_any),
    by = join_by(sampleunit_id)
  )


sf::st_geometry(sampleunit_polygons) <- "wkb_geometry"
# mapview::mapview(sampleunit_polygons)


message("________________________________________________________________")
message(glue::glue("DELETE/INSERT of outbound.SampleUnitPolygons"))

locevaldb$execute_sql(
  glue::glue('DELETE  FROM "outbound"."SampleUnitPolygons";'),
  verbose = TRUE
)

locevaldb$insert_data(
  table_label = "SampleUnitPolygons",
  upload_data = sampleunit_polygons
)


```


# Wrap-up


```{r stitched-up}

out <- processx::run(
  "Rscript",
  c("102_re_link_foreign_keys.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```


```{r step-n-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")

if (isFALSE(grepl("-staging", locevaldb_mirror))) {
  locevaldb$dump_all(
    here::here("dumps", glue::glue("rep_post_update_{locevaldb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```


```{r launch-consistency-dashboard}
out <- processx::run(
  "quarto",
  c("render", "045_loceval_consistency_dashboard.qmd", "--to", "html"),
  echo = TRUE,
  spinner = TRUE
)

```


Done.
