---
title: "REP Data Re-Upload"
date: "2026-05-27"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---



:::{.callout-note title="Purpose"}
Let's bring the sample to the field - again!

(... and again, and again, and again...)
:::


# Changelog

- 20250627, 20250904, 20260309, 20260326: <undocumented>
- 20260527 REP update


# TODO


# Preparations

## structure changes
Download the latest structure sheets for the production mirror.
Otherwise, the list of update columns might be incomplete.

## sync staging mirror

In all brevity, I collect steps here to get a new REP to the database.
staging`, first.
  - The `testing` mirror (data sync with `033_populate_testing_db.R`) is open for play and can taken even rough rides, and for that user permissions differ on there. No guarantee that the data is correct.
  - On `staging`, everything is exactly identical to the production server (even permissions and user roles), because it gets synced with the dump/restore commands below.
  - use the `suffix` to control database connections below.
  
  
Syncing the `*_staging` database mirrors:

  - has to be done for `loceval` and `mnmgwdb` 
  - if necessary, re-instantiate the mirror prior to data upload via `postgres`/`dropdb`+`createdb` intervention on the host system (and then run `110_*` and `210_*`, if necessary)
  - Finally, use the `pg_dump | psql` commands as follows:

  
```{sh sync-staging}
#| eval: false
pg_dump -U <backup_user> -h <host> -p <port> -d <database> -N tiger -N public -c > /tmp/<database>_db_dump.txt \
        && psql -U <database_user> -h <host> -p <port> -d <database>_staging -W < /tmp/<database>_db_dump.txt \
        && rm /tmp/<database>_db_dump.txt
```

## structure changes?
Download the latest structure sheets for the production mirror.
Otherwise, the list of update columns might be incomplete.

## libraries and variables

```{r libraries}
# libraries
source("MNMLibraryCollection.R")
load_database_interaction_libraries()

# the database connection object
source("MNMDatabaseConnection.R")

# more specific database tools
source("MNMDatabaseToolbox.R")


# library("mapview") # debugging only
# mapviewOptions(platform = "mapdeck")

```


## info stream from REP

First, there is the `.RData` file, along with proccessing outcome of the code snippets.

::: {.callout-note snippets}
- check for changes on every update, e.g. with `meld`:
  `meld 020_fieldwork_organization/code_snippets.R 900_database_organization/401_snippet_selection.R`
- bake fresh snippets every morning:
  `Rscript 403_precalculate_fresh_snippets.R`
:::

```{r source-code-snippets}

tic <- function(toc) round(Sys.time() - toc, 1)
toc <- Sys.time()

snippet_base_path <<- rprojroot::find_root(rprojroot::is_git_root)
# # TEMPORARY adjustment pointing to adjacent branch (wip)
# snippet_base_path <<- normalizePath(file.path(snippet_base_path, "..", "n2khab-mne-monitoring_support"))

fresh_snippet_path <- file.path("data", "fresh_snippet_workspace.RData")
reload_rep_code_snippets(fresh_snippet_path)
message(glue::glue("Good morning!
  Loading the REP data and snippets took {tic(toc)} seconds today."
))

verify_rep_objects()

if (nrow(different_checksums) > 0) {
  knitr::kable(different_checksums)
}

```


## database connection


```{r connect-databases}

config_filepath <- file.path("./mnm_database_connection.conf")
suffix <- "-staging"
# suffix <- ""

# ... and mnmgwdb
mnmgwdb_mirror <- glue::glue("mnmgwdb{suffix}")

mnmgwdb <- connect_mnm_database(
  config_filepath,
  database_mirror = mnmgwdb_mirror
) 

```

```{r connect-databases}

# keyring::keyring_delete(keyring = "mnmdb_temp")
message(glue::glue("connected: psql {mnmgwdb$shellstring}"))
update_cascade_lookup <- parametrize_cascaded_update(mnmgwdb)

```


## dump all data, for safety

```{r step-1-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")

if (isFALSE(grepl("-staging", mnmgwdb_mirror))) {
  mnmgwdb$dump_all(
    here::here("dumps", glue::glue("rep_pre_update_{mnmgwdb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```


# Gather and Upload - mnmgwdb

## database versioning

```{r version}

if (FALSE) {

  # manually set a new version
  #    v1 <- "≤v0.9.0_rvp0.13.0"
  #    v2 <- "v0.11.0_rvp0.13.1"
  # version_tag <- "v0.12.0_rvp0.14.0"
  # version_tag <- "snip:0.15.0_rep:0.15.0" # data_iteration = 1
  # version_tag <- "snip:0.15.1_rep:0.15.0"
  #   # "snippets update 0.15.1 (revert temporal prioritization breeding season)"

  version_tag <- "snip:0.16_rep:0.16" # data_iteration = 1
  version_notes <-
    "REP + snippets update 0.16"
  version_date_applied <- as.integer(format(Sys.time(), "%Y%m%d"))
  version_date_fixing <- as.Date("2025-12-31")

  version_id <- mnmgwdb$tag_new_version(
    new_version_tag = version_tag,
    new_version_notes =  version_notes,
    new_date_applied = version_date_applied,
    new_date_fixing = version_date_fixing
  )

  # SELECT * FROM "metadata"."Versions";

} else {
  # per default, the latest version is taken
  version_id <- mnmgwdb$load_latest_version_id()
}

if (FALSE) {
  # ... ad hoc / testing: delete version again
  table_label <- "Versions"
  glue::glue("
  DELETE FROM {mnmgwdb$get_namestring(table_label)}
  WHERE version_tag = '{version_tag}'
    AND data_iteration = {data_iteration}
  ;
  ")
}


# TODO: I still have to make up my mind whether to archive everything.
#       For now, I will preliminarily keep it with an "archive_id" column.
```


# Protocols, Activities, TeamMembers

:::{callout-warning}
Any news?
Now is the time!
:::


# Discarded Consideration: Prune Unused Rows

I would tend to delete unused calendar entries.
However, these should be regarded by the distribution procedure itself.

Even more important, the `precedence_columns` keep input fields from being considered.





# Let's Do This

## prerequisite_lookups

```{r gather-lookups}

n2khabstrata_lookup <- mnmgwdb$query_lookup(
  "N2kHabStrata",
  characteristic_columns = c("stratum")
)

activity_groupid_lookup <- mnmgwdb$query_columns(
    "GroupedActivities",
    c("activity_group", "activity_group_id")
  ) %>%
  distinct()

```


```{r load-activities}

gw_field_activities_db <- mnmgwdb$query_table("GroupedActivities") %>%
  filter(is_gw_activity, is_field_activity) %>%
  distinct(activity_group, activity, fag_is_auxiliary, fag_is_preponable)

```


:::{.callout-note}
`SSPSTaPas` are phasing out.
:::

I had the idea that `stratum_scheme_panelset_targetpanels` could be abbreviated to 
`sspstapas`.
Unfortunately, I did not keep up with the speed of things.

```{r ssps-tapas-fake}
# TODO sspstapas are obsolete and this function is a fake addition

replace_sspstapa_by_lookup <- function(df) {
  df_new <- df %>%
    mutate(sspstapa_id = NA) %>% 
    # left_join(
    #   sspstapas,
    #   by = join_by(stratum_scheme_ps_targetpanels),
    #   relationship = "many-to-one"
    # ) %>%
    relocate(
      sspstapa_id,
      .after = stratum_scheme_ps_targetpanels
    ) %>%
    select(-stratum_scheme_ps_targetpanels)

  return(df_new)
}

```



## Freeze Past Fixture

Here, it would be time to generate the latest FREEZE,
but only if the `date_fixing` changed in the latest `"metadata"."Versions"`.

TODO: new columns to work into the freeze (need to get set with a correct value)
+ `wait_obsolete_types` (20260521)

```{r generate_freeze_calendar}
#| eval: false
out <- processx::run(
  "Rscript",
  c("405_freeze_calendar.R", suffix),
  spinner = TRUE,
  echo = TRUE
  )
# message(out$stderr)

```


```{r load-freeze}

mnmgwdb_freeze <-
  read.csv(file = file.path("sideload", glue::glue("freeze_mnmgwdb{suffix}.csv"))) %>%
  mutate(across(c(
      date_start,
      date_end
    ), as.Date)
  )

# mnmgwdb_freeze %>% glimpse()
# mnmgwdb_freeze %>%
#   filter(grts_address %in% c(1999406, 6417454)) %>% 
#   t() %>% knitr::kable()
```


## Replacements

```{r refresh-replacements}
#| eval: false

out <- processx::run(
  "Rscript",
  c("111a_push_loceval_to_mnmgwdb.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```

```{r load-replacement-lookup}

replacement_lookup <- mnmgwdb$query_columns(
    "ReplacementData",
    c(
      "grts_address",
      "type",
      "grts_address_replacement"
    )
  ) %>% 
  rename(stratum = type)

apply_local_replacement_to_grts <- function(df, typecolumn = "stratum") {
  lookup <- replacement_lookup %>%
    mutate(is_replacement = TRUE)
  names(lookup)[names(lookup) == "stratum"] <- typecolumn 

  df %>%
    dplyr::left_join(
      lookup,
      by = dplyr::join_by(!!!c("grts_address", typecolumn))
    ) %>%
    mutate(
      grts_address = dplyr::coalesce(grts_address_replacement, grts_address),
      is_replacement = dplyr::coalesce(is_replacement, FALSE)
    ) %>% 
    select(-grts_address_replacement) %>%
    return()
}

```


## Sample Units


```{r assemble-sample-units}

sample_unit_columns <- c(
  "grts_address",
  "strata",
  "schemes",
  # "schemes_served_all", # -> renamed to schemes
  "scheme_ps_targetpanels",
  "domain_part",
  # "sp_poststratum",
  # "grts_join_method",
  # "is_current_occasion", # TODO
  # "schemes_served_all",
  "is_forest",
  "in_mhq_samples",
  # "mhq_assessment_date", 
  "has_mhq_assessment", 
  # "previous_notes",
  "is_replacement"
)


sample_units_updated <- fag_stratum_grts_calendar_shortterm_attribs %>%
  rename_grts_address_final_to_grts_address(keep_original = FALSE) %>%
  # only retain the activities for this scheme
  # otherwise there are duplicates (schemes filled differently on LOCEVAL)
  semi_join(
    gw_field_activities_db,
    by = join_by(field_activity_group == activity_group)
  ) %>% 
  rename(
    has_mhq_assessment = last_type_assessment_in_field,
    mhq_assessment_date = last_type_assessment,
    schemes = schemes_served_all
  ) %>%
  relocate(grts_address) %>%
  relocate(grts_join_method, .after = grts_address) %>%
  mutate(
    previous_notes = NA # FUTURE TODO
  ) %>% 
  apply_local_replacement_to_grts() %>% 
  rename(strata = stratum) %>% 
  # extract_and_flatten_scheme_from_scheme_ps_targetpanels() %>% # rather take _all
  distinct(!!!rlang::syms(sample_unit_columns)) %>% 
  mutate(across(c(
      scheme_ps_targetpanels,
      strata,
      domain_part
    ), as.character)
  )

# sample_units_updated %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()
# fag_stratum_grts_calendar_shortterm_attribs %>%
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

```


Re-establish SampleUnits from `the freeze`.

::: {.callout-note}
Sample units can 

- appear (only pesent in `_updated`)
- disappear (only pesent in `_retained`)
- stay or change (pesent in *both*, before and after update).

We UNION the updated and retained; for *changed* units the novel plan (`_updated`) is the reference.
Association with old schemes is not relevant.

:::

```{r frozen-units}
# mnmgwdb_freeze %>% names()

sample_units_retained <- mnmgwdb_freeze %>%
  distinct(!!!rlang::syms(sample_unit_columns)) %>%
  anti_join(
    sample_units_updated,
    by = join_by(grts_address, strata)
  )

sample_units_retained %>% 
  glimpse()

```


Join updated and frozen sample locations:

```{r combined_sample_units}

sample_units <- bind_rows(
  sample_units_retained,
  sample_units_updated
)

# # sample_units %>% sample_n(3) %>% t() %>% knitr::kable()
# sample_units_retained %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

```


## Locations

```{r assemble-locations}

locations_grts_collection <- bind_rows(
    mnmgwdb$query_columns("Locations", c("grts_address")),
    sample_units %>% select(grts_address),
    mnmgwdb$query_columns("LocationInfos", c("grts_address"))
  ) %>%
  mutate(grts_address = as.integer(grts_address)) %>%
  distinct()


# join geometry column
grts_mh <- n2khab::read_GRTSmh()

grts_mh_index <- dplyr::tibble(
    id = seq_len(terra::ncell(grts_mh)),
    grts_address = values(grts_mh)[, 1]
  ) %>%
  dplyr::filter(!is.na(grts_address))

locations <- locations_grts_collection %>% 
  add_point_coords_grts(
    grts_var = "grts_address",
    spatrast = grts_mh,
    spatrast_index = grts_mh_index
  )

sf::st_geometry(locations) <- "wkb_geometry"


### 20260511 testing direct write
#       upload_data <- sf::st_as_sf(locations)
#       # type_count <- as_tibble(sf::st_geometry_type(upload_data)) %>%
#       #   count(value)
#       sf::st_geometry(upload_data) <- "wkb_geometry"
# 
#   mnmgwdb$execute_sql(
#     glue::glue("DELETE FROM ONLY {mnmgwdb$get_namestring(table_label)};"),
#     verbose = TRUE
#   )
# 
#       rs <- sf::st_write(
#         upload_data,
#         mnmgwdb$connection,
#         mnmgwdb$get_table_id(table_label),
#         row.names = FALSE,
#         delete_layer = FALSE, # "overwrite"
#         append = TRUE,
#         factorsAsCharacter = TRUE,
#         binary = TRUE
#       )


# table_label <- "Locations"
# data_nouveau <- locations %>% sf::st_drop_geometry()# %>% select(-wkb_geometry)
# index_column <- mnmgwdb$get_primary_key(table_label)
# characteristic_columns <- c("grts_address")
# 
# distribution <- categorize_data_update(
#   mnmdb = mnmgwdb,
#   table_label = table_label,
#   data_future = data_nouveau,
#   input_precedence_columns = precedence_columns[[table_label]],
#   characteristic_columns = characteristic_columns,
#   exclude_columns = c("wkb_geometry")
# )
# print_category_count(distribution, table_label)

# distribution$to_upload %>% glimpse()

```


```{r update-locations}


locations_lookup <- update_cascade_lookup(
  table_label = "Locations",
  new_data = locations,
  index_columns = c("location_id"),
  characteristic_columns = c("grts_address"),
  tabula_rasa = FALSE,
  verbose = TRUE
)

```


20260511: the "redistribution" seems to ignore empty geometries

```{r update-locations-erroneous}
#| eval: false

## the putatively wrong, indirect way
# locations_lookup <- redistribute_calendar_data(
#   mnmdb = mnmgwdb,
#   table_label = table_label,
#   distribution = distribution,
#   index_columns = c(index_column),
#   characteristic_columns = characteristic_columns,
#   skip = list("update" = FALSE, "upload" = FALSE, "archive" = TRUE)
# )

# check <- mnmgwdb$query_table("Locations")

```

... and stitch
```{r stitch}

out <- processx::run(
  "Rscript",
  c("102_re_link_foreign_keys.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

# stitch_table_connection(
#   mnmdb = mnmgwdb,
#   table_label = "SampleLocations",
#   reference_table = "Locations",
#   link_key_column = "location_id",
#   lookup_columns = c("grts_address")
# )

```


## LocationCells

```{r new-location-cells}

units_cell_polygon[["grts_address_final"]] <-
  as.integer(units_cell_polygon[["grts_address_final"]])

# unit geometries (cells):
location_cells <-
  units_cell_polygon %>%
  inner_join(
    locations_lookup,
    by = join_by(grts_address_final == grts_address),
    relationship = "one-to-many",
    unmatched = "drop"
  ) %>%
  select(-grts_address_final) %>%
  relocate(geometry, .after = last_col())

sf::st_geometry(location_cells) <- "wkb_geometry"
# glimpse(location_cells)

message("________________________________________________________________")
message(glue::glue("DELETE/INSERT of metadata.LocationCells"))

mnmgwdb$execute_sql(
  glue::glue('DELETE  FROM "metadata"."LocationCells";'),
  verbose = TRUE
)

mnmgwdb$insert_data(
  table_label = "LocationCells",
  upload_data = location_cells
)

```

extra cells from replacements

```{r extra-ceplacement-locationcells}

loceval_sideload <- connect_mnm_database(
  config_filepath = config_filepath,
  database = "loceval",
  user = "monkey",
  password = NA
)

extra_cells <- loceval_sideload$query_table("ReplacementCells") %>%
  left_join(
    loceval_sideload$query_table("Replacements") %>%
      select(-wkb_geometry),
    by = join_by(replacement_id)
  ) %>%
  select(-grts_address) %>%
  rename(grts_address = grts_address_replacement) %>%
  inner_join(
    locations_lookup,
    by = join_by(grts_address)
  ) %>%
  select(location_id, wkb_geometry) %>%
  distinct %>%
  anti_join(
    location_cells,
    by = join_by(location_id)
  )

mnmgwdb$insert_data(
  table_label = "LocationCells",
  upload_data = extra_cells
)


```


## Sample Locations

:::{.callout-note title="Replacements!"}
Note to future me:

Local Replacements are applied by directly modifying `grts_address` in calendar/visits.
The original sample location gets archived during the next REP update script - here.

At the time of writing, this seems to be a logical solution. 
However, on a real REP update, i.e. when the info of replacements has trickled up to the REP, 
the locations to archive because of local replacement ("downstream" archives) get mixed with actual REP changes ("upstream").

Go figure that out!
:::



```{r process-sample-locations}

if ("location_id" %in% names(sample_units)) {
  # should not be the case in a continuous script;
  # this is extra safety for debugging and de-serial execution
  sample_units <- sample_units %>%
    select(-location_id)#, -location_id.x, -location_id.y)
}

sample_units <- sample_units %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address),
    relationship = "many-to-one"
  ) %>%
  mutate_at(
    # some locations on `oldpanels` have as.character('NA') values in bool columns
    vars(is_forest, in_mhq_samples), \(x) ifelse(is.na(x) | grepl('NA', x), FALSE, x)
  ) %>%
  distinct()


# sample_units %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()
```


```{r prepare-slocs}

table_label <- "SampleLocations"
data_nouveau <- sample_units
sampleunit_characols <- c("grts_address", "strata") # ERROR location_id was in here ☠
index_column <- mnmgwdb$get_primary_key(table_label)

distribution <- categorize_data_update(
  mnmdb = mnmgwdb,
  table_label = table_label,
  data_future = data_nouveau,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = sampleunit_characols,
)
print_category_count(distribution, table_label)

# distribution$to_archive %>% knitr::kable()
# distribution$reactivate %>% knitr::kable()
# distribution$to_upload %>% knitr::kable()
# distribution$changed %>% knitr::kable()

```


```{r update-sample-locations}

distribution$to_upload <- distribution$to_upload %>%
  mutate(
    # log_user = "maintenance",
    # log_update = as.POSIXct(Sys.time()),
    # is_replacement = FALSE
  )


samplelocations_lookup <- redistribute_calendar_data(
  mnmdb = mnmgwdb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = sampleunit_characols,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)

```



## FieldActivityCalendar

```{r assemble-fieldwork-calendar}
# samplelocations_lookup <- mnmgwdb$query_columns("SampleLocations", c("grts_address", "type", "samplelocation_id"))

fieldwork_calendar_columns <- c(
  "grts_address",
  "stratum",
  "samplelocation_id",
  "activity_group_id",
  "activity_rank",
  "date_start",
  "date_end",
  "date_interval",
  "priority",
  "wait_any",
  "wait_watersurface",
  "wait_3260",
  "wait_7220",
  "wait_floating",
  "wait_obsolete_types",
  "is_sideloaded",
  "is_frozen"
)


fieldcalendar_characols <- c(
  "grts_address",
  "stratum",
  "activity_group_id",
  "date_start"
)


fieldwork_shortterm_prioritization_by_stratum %>%
  apply_local_replacement_to_grts() %>% 
  filter(grts_address %in% c(1999406, 6417454)) %>%
  t() %>% knitr::kable()
samplelocations_lookup %>% 
  filter(grts_address %in% c(1999406, 6417454)) %>%
  t() %>% knitr::kable()

fieldwork_calendar_updated <- fieldwork_shortterm_prioritization_by_stratum %>%
  rename_grts_address_final_to_grts_address() %>%
  apply_local_replacement_to_grts() %>% 
  # rename(type = stratum) %>%
  inner_join(
    samplelocations_lookup %>% rename(stratum = strata),
    by = join_by(grts_address, stratum),
    relationship = "many-to-one"
  ) %>%
  relocate(grts_address, stratum, samplelocation_id) %>%
  rename(
    activity_rank = rank,
    activity_group = field_activity_group
  ) %>%
  semi_join(gw_field_activities_db, by = join_by(activity_group)) %>%
  left_join(
    activity_groupid_lookup,
    by = join_by(activity_group),
    relationship = "many-to-one"
  ) %>%
  select(-activity_group) %>%
  mutate(
    across(c(
        stratum,
        grts_join_method,
        domain_part,
        date_interval
      ),
      as.character
    )
  ) %>%
  mutate(is_frozen = FALSE, is_sideloaded = FALSE) %>% 
  select(!!!rlang::syms(fieldwork_calendar_columns))

# fieldwork_calendar_updated %>% glimpse()
# fieldwork_calendar_updated %>% count(priority)

# fieldwork_calendar_updated %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

```


Normally, all calendar entries from the `freeze` have already be removed, so the `anti_join` is a no-op.


```{r assemble-fieldwork-calendar-freeze}

fieldwork_calendar_retained <- mnmgwdb_freeze %>%
  select(tidyselect::any_of(c(fieldwork_calendar_columns, "done_planning"))) %>% 
  anti_join(
    fieldwork_calendar_updated,
    by = join_by(!!!rlang::syms(fieldcalendar_characols))
  ) %>%
  select(-is_frozen) %>% mutate(is_frozen = TRUE) %>%
  left_join(
    gw_field_activities_db %>%
      distinct(activity_group) %>% 
      left_join(activity_groupid_lookup, by = join_by(activity_group)) %>%
      select(activity_group_id) %>%
      mutate(is_gw_activity = TRUE),
    by = join_by(activity_group_id)
  ) %>% 
  filter(done_planning | is_gw_activity) %>%
  select(-done_planning, -is_gw_activity)
  


# fieldwork_calendar_retained %>% glimpse()
# mnmgwdb_freeze %>% count(activity_group_id, done_planning, visit_done)

```


```{r union-fieldwork-calendar}

fieldwork_calendar_new <- bind_rows(
    fieldwork_calendar_retained,
    fieldwork_calendar_updated
  ) %>% 
  mutate(sspstapa_id = NA)

```


```{r stitch-fwcal-to-slocs}

# link FieldworkCalender back to SampleLocations
stitch_table_connection(
  mnmdb = mnmgwdb,
  table_label = "FieldworkCalendar",
  reference_table = "SampleLocations",
  link_key_column = "samplelocation_id",
  lookup_columns = c("grts_address", "stratum"),
  reference_mod = function(x) if (x == "stratum") {"strata"} else {x}
)

```



```{r sideload-extra-calendar-entries}

# sideloading: extra activities e.g. to follow up issues in the field
calendar_to_sideload <- load_table_sideload_content(
    mnmdb = mnmgwdb,
    table_label = "FieldworkCalendar",
    characteristic_columns = fieldcalendar_characols,
    data_filepath = "sideload/mnmgwdb_calendars.csv",
    reload_previous = TRUE
  ) %>%
  inner_join(
    samplelocations_lookup %>% rename(stratum = strata),
    by = join_by(grts_address, stratum),
    relationship = "many-to-many", # TODO
    unmatched = "drop"
  ) %>%
  mutate(
    log_user = "maintenance",
    log_update = as.POSIXct(Sys.time()),
    is_sideloaded = TRUE,
    excluded = FALSE,
    no_visit_planned = FALSE,
    done_planning = FALSE
  )

fieldwork_calendar_new <- bind_rows(
  fieldwork_calendar_new,
  calendar_to_sideload %>%
    anti_join(
      fieldwork_calendar_new,
      by = join_by(!!!rlang::syms(fieldcalendar_characols))
    )
  )


```


```{r link-dates}

startdate_updates_happened <- associate_and_shift_start_dates(
  mnmdb = mnmgwdb,
  table_label = "FieldworkCalendar",
  data_future = fieldwork_calendar_new,
  characteristic_columns = fieldcalendar_characols,
  other_table_labels = c("Visits")
) 

if (startdate_updates_happened) message("Startdate updates happened!")

```



```{r categorize-fieldworkcalendar}

table_label <- "FieldworkCalendar"
data_nouveau <- fieldwork_calendar_new
characteristic_columns <- fieldcalendar_characols
index_column <- mnmgwdb$get_primary_key(table_label)


# data_nouveau %>% select(!!!characteristic_columns) %>% saveRDS("./dumps/datelink_older.rds")
# data_nouveau %>% select(!!!characteristic_columns) %>% write.csv2("./dumps/datelink_older.csv")
distribution <- categorize_data_update(
  mnmdb = mnmgwdb,
  table_label = table_label,
  data_future = data_nouveau,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = characteristic_columns,
  exclude_columns = c("samplelocation_id") #, "fieldactivitycalendar_id") # , "archive_version_id"
)
print_category_count(distribution, table_label)

# distribution$to_archive
# distribution$reactivate
# distribution$to_upload

```


```{r sync-fieldworkcalendar}

distribution$to_upload <- distribution$to_upload %>% 
  mutate(
    log_user = "maintenance",
    log_update = as.POSIXct(Sys.time()),
    excluded = FALSE,
    is_frozen = FALSE,
    no_visit_planned = FALSE,
    done_planning = FALSE
  ) 


fieldworkcalendar_lookup <- redistribute_calendar_data(
  mnmdb = mnmgwdb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = characteristic_columns,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)


```


intermediate check

```{r re-inspect-fieldworkcalendar}

mnmgwdb$query_table("FieldworkCalendar") %>% 
  count(is.na(samplelocation_id)) %>%
  knitr::kable()

# compare stored to true sample location
mnmgwdb$query_table("FieldworkCalendar") %>%
  left_join(
    mnmgwdb$query_table("SampleLocations") %>% rename(stratum = strata),
    by = join_by(grts_address, stratum)
  ) %>%
  filter(samplelocation_id.x != samplelocation_id.y)

```


## Visits

```{r stitch-visits}

stitch_visits <- function() {

  stitch_table_connection(
    mnmdb = mnmgwdb,
    table_label = "Visits",
    reference_table = "FieldworkCalendar",
    link_key_column = "fieldworkcalendar_id",
    lookup_columns = c("grts_address", "stratum", "activity_group_id", "date_start")
  )
  
  stitch_table_connection(
    mnmdb = mnmgwdb,
    table_label = "Visits",
    reference_table = "SampleLocations",
    link_key_column = "samplelocation_id",
    lookup_columns = c("grts_address", "stratum"), 
    reference_mod = function(x) if (x == "stratum") {"strata"} else {x}
  )
  
  stitch_table_connection(
    mnmdb = mnmgwdb,
    table_label = "Visits",
    reference_table = "Locations",
    link_key_column = "location_id",
    lookup_columns = c("grts_address")
  )
}
stitch_visits()

```


```{r assemble-new-visits}

visits_characols <- fieldcalendar_characols

potential_visits <- fieldworkcalendar_lookup %>%
  select(
    !!!rlang::syms(c("fieldworkcalendar_id", visits_characols))
  ) %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address)
  ) %>%
  mutate(
    log_user = "maintenance",
    log_update = as.POSIXct(Sys.time()),
    issues = FALSE,
    visit_done = FALSE
  )


visits_upload <- potential_visits %>%
  anti_join(
    mnmgwdb$query_table("Visits"),
    by = join_by(!!!fieldcalendar_characols)
  ) %>%
  left_join(
    samplelocations_lookup %>% rename(stratum = strata),#  %>% select(-location_id),
    by = join_by(grts_address, stratum)
  ) 

```

:::{.callout-note title="All Visits are equal..."}
Note: "special" Visits must be distributed to the respective tables.
These tables inherit columns from `Visits`, adding extra ones.
:::

```{r subset-visits}

# Loop Special Activities
selection_of_activities <- list(
  "InstallationVisits" = activity_groupid_lookup %>%
    filter(grepl("^GWINST", activity_group)) %>%
    pull(activity_group_id) %>% unique, # /WIA
  "SamplingVisits" = activity_groupid_lookup %>%
    filter(activity_group %in%
      c(gw_field_activities_db %>%
        filter(grepl("^GW.*SAMP", activity)) %>%
        pull(activity_group))
      ) %>%
    pull(activity_group_id) %>% unique, # /CSA
  "PositioningVisits" = activity_groupid_lookup %>%
    filter(activity_group %in%
      c(gw_field_activities_db %>%
        filter(grepl("^SPATPOSIT", activity)) %>%
        pull(activity_group))
      ) %>%
    pull(activity_group_id) %>% unique # /SPA
)

append_defaults <- list(
  "InstallationVisits" = function(df) df %>%
    mutate(
      no_diver = FALSE,
      soilprofile_unclear = FALSE
    ) # /WIA
)

```


```{r upload-special-visits}

remaining_new_visits <- visits_upload

# table_label <- "InstallationVisits"
for (table_label in names(selection_of_activities)) {

  # subset the data by using selection_of_activities -> activity_group_id's
  select_activities <- selection_of_activities[[table_label]]
  special_visits <- remaining_new_visits %>%
    filter(activity_group_id %in% select_activities)

  # extra columns
  if (table_label %in% names(append_defaults)) {
    special_visits <- append_defaults[[table_label]](special_visits)
  }

  # append=upload data to the activity table
  # double-check existing to avoid dups
  # existing <- mnmgwdb$query_table(table_label)
  sa_lookup <- upload_and_lookup(
    mnmgwdb,
    table_label = table_label,
    data_to_append = special_visits,
    characteristic_columns = visits_characols,
    index_columns = c("visit_id"),
    verbose = TRUE
  )

  # anti-join remaining_new_visits
  remaining_new_visits <- remaining_new_visits %>%
    anti_join(
      special_visits,
      by = join_by(
        fieldworkcalendar_id,
        grts_address,
        stratum,
        activity_group_id,
        date_start)
    )

}

```

```{r upload-non-special-visits}

only_visits_lookup <- upload_and_lookup(
  mnmgwdb,
  table_label = "Visits",
  data_to_append = remaining_new_visits,
  characteristic_columns = visits_characols,
  index_columns = c("visit_id"),
  verbose = TRUE
)


```



```{r reconnect-visits}

stitch_visits()

mnmgwdb$query_table("Visits") %>% 
  count(
    is.na(location_id),
    is.na(samplelocation_id),
    is.na(fieldworkcalendar_id)
  ) %>%
  knitr::kable()

```


archive visits of archived FWCals

```{r archive-visits-fwcal}

trgtab <- mnmgwdb$get_namestring("Visits")
srctab <- mnmgwdb$get_namestring("FieldworkCalendar")
link_key_column <- "archive_version_id"
lookup_criteria <- c("TRGTAB.fieldworkcalendar_id = SRCTAB.fieldworkcalendar_id")

update_string <- glue::glue("
  UPDATE {trgtab} AS TRGTAB
    SET
      {link_key_column} = SRCTAB.{link_key_column}
    FROM {srctab} AS SRCTAB
    WHERE
     ({paste0(lookup_criteria, collapse = ') AND (')})
  ;")

mnmgwdb$execute_sql(update_string)

mnmgwdb$query_table("FieldworkCalendar") %>%
  anti_join(
    mnmgwdb$query_table("Visits"),
    by = join_by(fieldworkcalendar_id, archive_version_id)
  ) %>% nrow()

```




## LocationInfos

```{r update-locationinfos}

new_locinfos <- sample_units %>%
  distinct(
    grts_address
  ) %>%
  mutate(
    log_creator = "maintenance",
    log_creation = as.POSIXct(Sys.time()),
    log_user = "maintenance",
    log_update = as.POSIXct(Sys.time())
  )

new_locinfos <- new_locinfos %>%
  anti_join(
    mnmgwdb$query_table("LocationInfos"),
    by = join_by(grts_address)
  ) %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address),
  )


locationinfo_lookup <- update_cascade_lookup(
  table_label = "LocationInfos",
  new_data = new_locinfos,
  index_columns = c("locationinfo_id"),
  characteristic_columns = c("grts_address"),
  tabula_rasa = FALSE,
  verbose = TRUE
)


```


## Landuse

```{r update-landuse}
update_landuse_in_locationinfos(mnmgwdb)
```


# post hoc


```{r stitched-up}

out <- processx::run(
  "Rscript",
  c("102_re_link_foreign_keys.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```


```{r step-n-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")

if (isFALSE(grepl("-staging", mnmgwdb_mirror))) {
  mnmgwdb$dump_all(
    here::here("dumps", glue::glue("rep_post_update_{mnmgwdb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```



```{r launch-consistency-dashboard}

out <- processx::run(
  "quarto",
  c("render", "046_mnmgwdb_consistency_dashboard.qmd", "--to", "html"),
  echo = TRUE,
  spinner = TRUE
)

```


# Random Points

```{r recalculate-random-points}

out <- processx::run(
  "Rscript",
  c("118_random_placementpoints_mnmgwdb.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```



```{sql}
--| eval: false
--| echo: true

-- to https://docs.google.com/spreadsheets/d/11_0sACvkvX_teOO_nJmTxYSV4-EzOWtxJYE1QNkStAc/edit
\COPY (
    SELECT samplelocation_id,
      location_id,
      grts_address,
      random_point_rank,
      compass,
      angle,
      angle_look,
      distance_m,
      lambert_lon,
      lambert_lat
    FROM "outbound"."RandomPoints"
    WHERE angle IS NOT NULL
    ORDER BY grts_address ASC, random_point_rank ASC
) TO '/data/mnm_db_backups/randompoints.csv' With CSV DELIMITER ',' HEADER
;

```


```{r done-updating-rep}

message("")
message("________________________________________________________________")
message(" >>>>> Finished REP data update. ")
message("________________________________________________________________")
```

