---
title: "REP Data Re-Upload for mnmSURFdb"
date: "2026-06-15"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---


# Changelog

- 20260615 init: copied from mnmgwdb
- 202606?? REP update


# TODO


# Preparations

## structure changes
Download the latest structure sheets for the production mirror.
Otherwise, the list of update columns might be incomplete.

## sync staging mirror

In all brevity, I collect steps here to get a new REP to the database.
All changes within this update script should be attempted on `staging`, first.
  - use the `suffix` to control database connections below. Empty suffix (`""`) labels the `production` database.
  - The `-testing` mirror (data sync with `033_populate_testing_db.R`) is open to play, and user permissions differ on there. No guarantee that the data is correct.
  - On `-staging`, everything is exactly identical to the production server (even permissions and user roles), because it gets synced with the dump/restore commands below.
  - The `-dev` mirror is usually/mostly empty (except for arranging minimal debugging examples). It is often used for re-initializing the database to apply structural changes: download the structure sheet, then re-initialize the structure to `-dev`, dumping the `stdout` output in a file.
  ```sh
  cd <path/to>/n2khab-mne-monitoring/900_database_organization/
  nvim 701_init_mnmsurfdb.py
  # set `restore_dev = True` but all others False
  source .dbtools/bin/activate.fish # the python venv with all requirements from `python_requirements.txt` installed
  python 701_init_mnmsurfdb.py > dump.txt # Note: if process appears stuck, check dump file for hidden confirmation prompt
  # then get the relevant additions from `dump.txt`
  #    and apply it to the server via direct `psql <...>`
  ```
  
  
  
Syncing the `-staging` database mirrors:

  - has to be done for `loceval`, `mnmgwdb`, and `mnmsurfdb`  
  - if necessary (e.g. on major structural changes), re-instantiate the `-staging` mirror prior to data upload via `postgres`/`dropdb`+`createdb` intervention on the host system (and then run `501_*` and `601_*`, if necessary)
  - Finally, use the `pg_dump | psql` commands as follows:

  
```{sh sync-staging}
#| eval: false
pg_dump -U <backup_user> -h <host> -p <port> -d <database> -N tiger -N public -c > /tmp/<database>_db_dump.txt \
        && psql -U <database_user> -h <host> -p <port> -d <database>_staging -W < /tmp/<database>_db_dump.txt \
        && rm /tmp/<database>_db_dump.txt
```


## libraries and variables

```{r libraries}
# libraries
source("MNMLibraryCollection.R")
load_database_interaction_libraries()

# the database connection object
source("MNMDatabaseConnection.R")

# more specific database tools
source("MNMDatabaseToolbox.R")


# library("mapview") # debugging only
# mapviewOptions(platform = "mapdeck")

```


## info stream from REP

First, there is the `.RData` file, along with proccessing outcome of the code snippets.

::: {.callout-note snippets}
- check for changes on every update, e.g. with `meld`:
  `meld 020_fieldwork_organization/code_snippets.R 900_database_organization/401_snippet_selection.R`
- bake fresh snippets every morning:
  `Rscript 403_precalculate_fresh_snippets.R`
:::

```{r source-code-snippets}

tic <- function(toc) round(Sys.time() - toc, 1)
toc <- Sys.time()

snippet_base_path <<- rprojroot::find_root(rprojroot::is_git_root)
# # TEMPORARY adjustment pointing to adjacent branch (wip)
# snippet_base_path <<- normalizePath(file.path(snippet_base_path, "..", "n2khab-mne-monitoring_support"))

fresh_snippet_path <- file.path("data", "fresh_snippet_workspace.RData")
reload_rep_code_snippets(fresh_snippet_path)
message(glue::glue("Good morning!
  Loading the REP data and snippets took {tic(toc)} seconds today."
))

verify_rep_objects()

if (nrow(different_checksums) > 0) {
  knitr::kable(different_checksums)
}

```


## database connection


```{r connect-databases}

config_filepath <- file.path("./mnm_database_connection.conf")
suffix <- "-staging"
# suffix <- ""

# connect mnmsurfdb
mnmsurfdb_mirror <- glue::glue("mnmsurfdb{suffix}")

mnmsurfdb <- connect_mnm_database(
  config_filepath,
  database_mirror = mnmsurfdb_mirror
) 

```



```{r connect-databases}

# keyring::keyring_delete(keyring = "mnmdb_temp")
message(glue::glue("connected: psql {mnmsurfdb$shellstring}"))
update_cascade_lookup <- parametrize_cascaded_update(mnmsurfdb)

```


## dump all data, for safety

```{r step-1-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")

if (isFALSE(grepl("-staging", mnmsurfdb_mirror))) {
  mnmsurfdb$dump_all(
    here::here("dumps", glue::glue("rep_pre_update_{mnmsurfdb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```


# Gather and Upload - mnmsurfdb

## database versioning

```{r version}

if (FALSE) {

  # manually set a new version
  version_tag <- "mnmsurfdb_initialization" # data_iteration = 1
  version_notes <-
    "REP + snippets update 0.16"
  version_date_applied <- as.integer(format(Sys.time(), "%Y%m%d"))
  version_date_fixing <- as.Date("2025-12-31")

  version_id <- mnmsurfdb$tag_new_version(
    new_version_tag = version_tag,
    new_version_notes =  version_notes,
    new_date_applied = version_date_applied,
    new_date_fixing = version_date_fixing
  )

  # SELECT * FROM "metadata"."Versions";

} else {
  # per default, the latest version is taken
  version_id <- mnmsurfdb$load_latest_version_id()
}

if (FALSE) {
  # ... ad hoc / testing: delete version again
  table_label <- "Versions"
  glue::glue("
  DELETE FROM {mnmsurfdb$get_namestring(table_label)}
  WHERE version_tag = '{version_tag}'
    AND data_iteration = {data_iteration}
  ;
  ")
}


# TODO: I still have to make up my mind whether to archive everything.
#       For now, I will preliminarily keep it with an "archive_id" column.
```


# Protocols, Activities / GroupedActivities / FAGs, TeamMembers

:::{callout-warning}
Any news?
Now is the time!
:::


# Let's Do This

## prerequisite_lookups

```{r gather-lookups}

n2khabstrata_lookup <- mnmsurfdb$query_lookup(
  "N2kHabStrata",
  characteristic_columns = c("stratum")
)

activity_groupid_lookup <- mnmsurfdb$query_columns(
    "GroupedActivities",
    c("activity_group", "activity_group_id")
  ) %>%
  distinct()

```


```{r load-activities}

surf_field_activities_db <- mnmsurfdb$query_table("GroupedActivities") %>%
  filter(is_surf_activity, is_field_activity) %>%
  distinct(activity_group, activity, fag_is_auxiliary, fag_is_preponable)

```



## Freeze Past Fixture

Here, it would be time to generate the latest FREEZE,
but only if the `date_fixing` changed in the latest `"metadata"."Versions"`.

TODO: new columns to work into the freeze (need to get set with a correct value)
+ `wait_obsolete_types` (20260521)
+ `is_surf_activity` (20260615)

```{r generate_freeze_calendar}
#| eval: false
out <- processx::run(
  "Rscript",
  c("405_freeze_calendar.R", suffix),
  spinner = TRUE,
  echo = TRUE
  )
# message(out$stderr)

```


```{r load-freeze}

mnmsurfdb_freeze <-
  read.csv(file = file.path("sideload", glue::glue("freeze_mnmsurfdb{suffix}.csv"))) %>%
  mutate(across(c(
      date_start,
      date_end
    ), as.Date)
  )

# TODO annoyingly, an empty `freeze` gets quite arbitrary data types in R

# mnmsurfdb_freeze %>% glimpse()
# mnmsurfdb_freeze %>%
#   filter(grts_address %in% c(1999406, 6417454)) %>% 
#   t() %>% knitr::kable()
```


## Replacements

```{r refresh-replacements}
#| eval: false

out <- processx::run(
  "Rscript",
  c("111_distribute_loceval_via_mnmsyncdb.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```



```{r load-replacement-lookup}

replacement_lookup <- mnmsurfdb$query_columns(
    "ReplacementData",
    c(
      "grts_address_original",
      "type",
      "grts_address_replacement"
    )
  ) %>% 
  rename(
    grts_address = grts_address_original,
    stratum = type
  )

apply_local_replacement_to_grts <- function(df, typecolumn = "stratum") {
  lookup <- replacement_lookup %>%
    dplyr::mutate(is_replacement = TRUE)
  names(lookup)[names(lookup) == "stratum"] <- typecolumn

  df %>%
    dplyr::left_join(
      lookup,
      by = dplyr::join_by(!!!c("grts_address", typecolumn))
    ) %>%
    dplyr::mutate(
      grts_address = dplyr::coalesce(grts_address_replacement, grts_address),
      is_replacement = dplyr::coalesce(is_replacement, FALSE)
    ) %>% 
    dplyr::select(-grts_address_replacement) %>%
    return()
}

```


## Sample Units


```{r assemble-sample-units}

sample_unit_columns <- c(
  "grts_address",
  "stratum",
  "scheme_ps_targetpanels",
  "schemes",
  "domain_part",
  "is_forest",
  "in_mhq_samples",
  "has_mhq_assessment",
  "is_replacement",
  "was_replaced_by_grts"
)


sample_units_updated <- fag_stratum_grts_calendar_shortterm_attribs %>%
  rename_grts_address_final_to_grts_address(keep_original = FALSE) %>%
  # only retain the activities for this scheme
  # otherwise there are duplicates (schemes filled differently on LOCEVAL)
  semi_join(
    surf_field_activities_db,
    by = join_by(field_activity_group == activity_group)
  ) %>% 
  rename(
    has_mhq_assessment = last_type_assessment_in_field,
    mhq_assessment_date = last_type_assessment,
    schemes = schemes_served_all
  ) %>%
  relocate(grts_address) %>%
  relocate(grts_join_method, .after = grts_address) %>%
  mutate(
    previous_notes = NA # FUTURE TODO
  ) %>% 
  apply_local_replacement_to_grts() %>% 
  mutate(
    # TODO should this be handled by `apply_local_replacement_to_grts`?
    was_replaced_by_grts = NA
  ) %>%
  distinct(!!!rlang::syms(sample_unit_columns)) %>% 
  mutate(across(c(
      scheme_ps_targetpanels,
      stratum,
      domain_part
    ), as.character)
  )

# sample_units_updated %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()
# fag_stratum_grts_calendar_shortterm_attribs %>%
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

```


Re-establish SampleUnits from `the freeze`.

::: {.callout-note}
Sample units can 

- appear (only pesent in `_updated`)
- disappear (only pesent in `_retained`)
- stay or change (pesent in *both*, before and after update).

We UNION the updated and retained; for *changed* units the novel plan (`_updated`) is the reference.
Association with old schemes is not relevant.

:::

```{r frozen-units}
# mnmsurfdb_freeze %>% names()

if (nrow(mnmsurfdb_freeze) == 0) {
  # adjust freeze data types to ensure compatibility
  mnmsurfdb_freeze <- sample_units_updated %>%
    filter(FALSE)
} 

sample_units_retained <- mnmsurfdb_freeze %>%
  distinct(!!!rlang::syms(sample_unit_columns)) %>%
  anti_join(
    sample_units_updated,
    by = join_by(grts_address, stratum)
  )

sample_units_retained %>% 
  glimpse()

```


Join updated and frozen sample locations:

```{r combined_sample_units}

sample_units <- bind_rows(
  sample_units_retained,
  sample_units_updated
)

# # sample_units %>% sample_n(3) %>% t() %>% knitr::kable()
# sample_units_retained %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

```


## Locations

```{r assemble-locations}

locations_grts_collection <- bind_rows(
    mnmsurfdb$query_columns("Locations", c("grts_address")),
    sample_units %>% distinct(grts_address),
    mnmsurfdb$query_columns("LocationInfos", c("grts_address")),
    mnmsurfdb$query_columns("ReplacementData", c("grts_address_original")) %>%
      rename(grts_address = grts_address_original)
  ) %>%
  mutate(grts_address = as.integer(grts_address)) %>%
  distinct() %>%
  arrange(grts_address)


# join geometry column
grts_mh <- n2khab::read_GRTSmh()

grts_mh_index <- dplyr::tibble(
    id = seq_len(terra::ncell(grts_mh)),
    grts_address = values(grts_mh)[, 1]
  ) %>%
  dplyr::filter(!is.na(grts_address))

locations <- locations_grts_collection %>% 
  add_point_coords_grts(
    grts_var = "grts_address",
    spatrast = grts_mh,
    spatrast_index = grts_mh_index
  )

sf::st_geometry(locations) <- "wkb_geometry"

# DONE directly update locations?
# stop("location update not clear (merge conflict 20260603)")
# -> in accordance with `510_loceval_update_REP.qmd`,
#    update_cascade_lookup should do fine

### 20260511 testing direct write
#       upload_data <- sf::st_as_sf(locations)
#       # type_count <- as_tibble(sf::st_geometry_type(upload_data)) %>%
#       #   count(value)
#       sf::st_geometry(upload_data) <- "wkb_geometry"
# 
#   mnmsurfdb$execute_sql(
#     glue::glue("DELETE FROM ONLY {mnmsurfdb$get_namestring(table_label)};"),
#     verbose = TRUE
#   )
# 
#       rs <- sf::st_write(
#         upload_data,
#         mnmsurfdb$connection,
#         mnmsurfdb$get_table_id(table_label),
#         row.names = FALSE,
#         delete_layer = FALSE, # "overwrite"
#         append = TRUE,
#         factorsAsCharacter = TRUE,
#         binary = TRUE
#       )


# table_label <- "Locations"
# data_nouveau <- locations %>% sf::st_drop_geometry()# %>% select(-wkb_geometry)
# index_column <- mnmsurfdb$get_primary_key(table_label)
# characteristic_columns <- c("grts_address")
# 
# distribution <- categorize_data_update(
#   mnmdb = mnmsurfdb,
#   table_label = table_label,
#   data_future = data_nouveau,
#   input_precedence_columns = precedence_columns[[table_label]],
#   characteristic_columns = characteristic_columns,
#   exclude_columns = c("wkb_geometry")
# )
# print_category_count(distribution, table_label)

# distribution$to_upload %>% glimpse()

```


```{r update-locations}


locations_lookup <- update_cascade_lookup(
  table_label = "Locations",
  new_data = locations,
  index_columns = c("location_id"),
  characteristic_columns = c("grts_address"),
  tabula_rasa = FALSE,
  verbose = TRUE
)

```


```{r update-locations-check-empty}

check_empty_geoms <- mnmsurfdb$query_table("Locations") %>%
  filter(sf::st_is_empty(wkb_geometry))

if (nrow(check_empty_geoms) > 0) {
  print(check %>% knitr::kable())
  stop("There are empty geometries in the `Locations` table!")
}

```

... and stitch
```{r stitch}

out <- processx::run(
  "Rscript",
  c("102_re_link_foreign_keys.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```


## LocationCells

```{r new-location-cells}

units_cell_polygon[["grts_address_final"]] <-
  as.integer(units_cell_polygon[["grts_address_final"]])

# unit geometries (cells):
location_cells <-
  units_cell_polygon %>%
  inner_join(
    locations_lookup,
    by = join_by(grts_address_final == grts_address),
    relationship = "one-to-many",
    unmatched = "drop"
  ) %>%
  select(-grts_address_final) %>%
  relocate(geometry, .after = last_col())

sf::st_geometry(location_cells) <- "wkb_geometry"
# glimpse(location_cells)

message("________________________________________________________________")
message(glue::glue("DELETE/INSERT of metadata.LocationCells"))

mnmsurfdb$execute_sql(
  glue::glue('DELETE  FROM "metadata"."LocationCells";'),
  verbose = TRUE
)

mnmsurfdb$insert_data(
  table_label = "LocationCells",
  upload_data = location_cells
)

```

extra cells from replacements

```{r extra-ceplacement-locationcells}

loceval_sideload <- connect_mnm_database(
  config_filepath = config_filepath,
  database = "loceval",
  user = "monkey",
  password = NA
)

extra_cells <- loceval_sideload$query_table("ReplacementCells") %>%
  left_join(
    loceval_sideload$query_table("Replacements") %>%
      select(-wkb_geometry),
    by = join_by(replacement_id)
  ) %>%
  select(-grts_address) %>%
  rename(grts_address = grts_address_replacement) %>%
  inner_join(
    locations_lookup,
    by = join_by(grts_address)
  ) %>%
  select(location_id, wkb_geometry) %>%
  distinct %>%
  anti_join(
    location_cells,
    by = join_by(location_id)
  )

mnmsurfdb$insert_data(
  table_label = "LocationCells",
  upload_data = extra_cells
)


```


## Sample Units

:::{.callout-note title="Replacements!"}
Note to future me:

Local Replacements are applied by directly modifying `grts_address` in calendar/visits.
The original sample location gets archived during the next REP update script - here.

At the time of writing, this seems to be a logical solution. 
However, on a real REP update, i.e. when the info of replacements has trickled up to the REP, 
the locations to archive because of local replacement ("downstream" archives) get mixed with actual REP changes ("upstream").

Go figure that out!
:::



```{r process-sample-locations}

if ("location_id" %in% names(sample_units)) {
  # should not be the case in a continuous script;
  # this is extra safety for debugging and de-serial execution
  sample_units <- sample_units %>%
    select(-location_id)#, -location_id.x, -location_id.y)
}

sample_units <- sample_units %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address),
    relationship = "many-to-one"
  ) %>%
  mutate_at(
    # some locations on `oldpanels` have as.character('NA') values in bool columns
    vars(is_forest, in_mhq_samples), \(x) ifelse(is.na(x) | grepl('NA', x), FALSE, x)
  ) %>%
  distinct()


# sample_units %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()
```


```{r prepare-sunits}

table_label <- "SampleUnits"
data_nouveau <- sample_units
sampleunit_characols <- c("grts_address", "stratum")
index_column <- mnmsurfdb$get_primary_key(table_label)

distribution <- categorize_data_update(
  mnmdb = mnmsurfdb,
  table_label = table_label,
  data_future = data_nouveau,
  input_precedence_columns = precedence_columns[[table_label]],
  characteristic_columns = sampleunit_characols,
)
print_category_count(distribution, table_label)

# distribution$to_archive %>% knitr::kable()
# distribution$reactivate %>% knitr::kable()
# distribution$to_upload %>% knitr::kable()
# distribution$changed %>% knitr::kable()

# waldo::compare(
#   data_nouveau %>%
#     semi_join(
#       distribution$changed,
#       by = join_by(!!!rlang::syms(sampleunit_characols))
#     ),
#   distribution$changed
# )

```


```{r update-sample-locations}

distribution$to_upload <- distribution$to_upload %>%
  mutate(
    # log_user = "maintenance",
    # log_update = as.POSIXct(lubridate::floor_date(Sys.time(), unit = ".001s")),
    # is_replacement = FALSE
  )


sampleunits_lookup <- redistribute_calendar_data(
  mnmdb = mnmsurfdb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = sampleunit_characols,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)

```



## FieldCalendar

```{r assemble-field-calendar}
# sampleunits_lookup <- mnmsurfdb$query_columns("SampleUnits", c("grts_address", "type", "sampleunit_id"))

fieldcalendar_columns <- c(
  "sampleunit_id",
  "grts_address",
  "stratum",
  "activity_group_id",
  "date_start",
  "date_end",
  "date_interval",
  "activity_rank",
  "priority",
  "wait_any",
  "wait_watersurface",
  "wait_3260",
  "wait_7220",
  "wait_floating",
  "wait_obsolete_types",
  "is_sideloaded",
  "is_frozen"
)


fieldcalendar_characols <- c(
  "grts_address",
  "stratum",
  "activity_group_id",
  "date_start"
)


# fieldwork_shortterm_prioritization_by_stratum %>%
#   apply_local_replacement_to_grts() %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()
# sampleunits_lookup %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

fieldcalendar_updated <- fieldwork_shortterm_prioritization_by_stratum %>%
  rename_grts_address_final_to_grts_address() %>%
  apply_local_replacement_to_grts() %>% 
  # rename(type = stratum) %>%
  inner_join(
    sampleunits_lookup,
    by = join_by(grts_address, stratum),
    relationship = "many-to-one"
  ) %>%
  relocate(grts_address, stratum, sampleunit_id) %>%
  rename(
    activity_rank = rank,
    activity_group = field_activity_group
  ) %>%
  semi_join(surf_field_activities_db, by = join_by(activity_group)) %>%
  left_join(
    activity_groupid_lookup,
    by = join_by(activity_group),
    relationship = "many-to-one"
  ) %>%
  select(-activity_group) %>%
  mutate(
    across(c(
        stratum,
        grts_join_method,
        domain_part,
        date_interval
      ),
      as.character
    )
  ) %>%
  mutate(is_frozen = FALSE, is_sideloaded = FALSE) %>% 
  select(!!!rlang::syms(fieldcalendar_columns))

# fieldcalendar_updated %>% glimpse()
# fieldcalendar_updated %>% count(priority)

# fieldcalendar_updated %>% 
#   filter(grts_address %in% c(1999406, 6417454)) %>%
#   t() %>% knitr::kable()

```


Normally, all calendar entries from the `freeze` have already be removed, so the `anti_join` is a no-op.


```{r assemble-fieldcalendar-freeze}

if (nrow(mnmsurfdb_freeze) == 0) {
  # adjust freeze data types to ensure compatibility
  mnmsurfdb_freeze <- fieldcalendar_updated %>%
    filter(FALSE) %>% 
    select(-sampleunit_id) %>% 
    mutate(done_planning = FALSE)
} 


fieldcalendar_retained <- mnmsurfdb_freeze %>%
  select(tidyselect::any_of(c(fieldcalendar_columns, "done_planning"))) %>% 
  anti_join(
    fieldcalendar_updated,
    by = join_by(!!!rlang::syms(fieldcalendar_characols))
  ) %>%
  select(-is_frozen) %>% mutate(is_frozen = TRUE) %>%
  left_join(
    surf_field_activities_db %>%
      distinct(activity_group) %>% 
      left_join(activity_groupid_lookup, by = join_by(activity_group)) %>%
      select(activity_group_id) %>%
      mutate(is_surf_activity = TRUE),
    by = join_by(activity_group_id)
  ) %>% 
  filter(done_planning | is_surf_activity) %>%
  select(-done_planning, -is_surf_activity)
  


# fieldcalendar_retained %>% glimpse()
# mnmsurfdb_freeze %>% count(activity_group_id, done_planning, visit_done)

```


```{r union-fieldcalendar}

fieldcalendar_new <- bind_rows(
    fieldcalendar_retained,
    fieldcalendar_updated
  ) 

```


```{r stitch-fwcal-to-sunits}

# link FieldCalender back to SampleUnits
stitch_table_connection(
  mnmdb = mnmsurfdb,
  table_label = "FieldCalendar",
  reference_table = "SampleUnits",
  link_key_column = "sampleunit_id",
  lookup_columns = c("grts_address", "stratum")
)

```



```{r sideload-extra-calendar-entries}

# sideloading: extra activities e.g. to follow up issues in the field
calendar_to_sideload <- load_table_sideload_content(
    mnmdb = mnmsurfdb,
    table_label = "FieldCalendar",
    characteristic_columns = fieldcalendar_characols,
    data_filepath = "sideload/mnmsurfdb_calendars.csv",
    # data_filepath = "sideload/mnmsurfdb_calendars.csv",
    reload_previous = TRUE
  ) %>%
  select(-tidyselect::any_of(c("sampleunit_id"))) %>% 
  inner_join(
    sampleunits_lookup, 
    by = join_by(grts_address, stratum),
    relationship = "many-to-many", # TODO
    unmatched = "drop",
    suffix = c("", "_lookup")
  ) %>%
  mutate(
    log_user = "maintenance",
    log_update = convert_timestamp_to_ms_character(Sys.time()),
    is_sideloaded = TRUE,
    excluded = FALSE,
    no_visit_planned = FALSE,
    done_planning = FALSE
  )

fieldcalendar_new <- bind_rows(
  fieldcalendar_retained,
  fieldcalendar_updated,
  calendar_to_sideload %>%
    select(tidyselect::any_of(names(fieldcalendar_updated))) %>% 
    anti_join(
      fieldcalendar_retained,
      by = join_by(!!!rlang::syms(fieldcalendar_characols))
    ) %>% 
    anti_join(
      fieldcalendar_updated,
      by = join_by(!!!rlang::syms(fieldcalendar_characols))
    )
  ) %>%
  mutate(priority = tidyr::replace_na(priority, 0))



  # %>% mutate(log_update = convert_timestamp_to_ms_character(log_update)),
```



```{r link-dates}

startdate_updates_happened <- associate_and_shift_start_dates(
  mnmdb = mnmsurfdb,
  table_label = "FieldCalendar",
  data_future = fieldcalendar_new,
  characteristic_columns = fieldcalendar_characols,
  other_table_labels = c("Visits")
) 

if (startdate_updates_happened) message("Startdate updates happened!")

```



```{r categorize-fieldcalendar}

table_label <- "FieldCalendar"
data_nouveau <- fieldcalendar_new
characteristic_columns <- fieldcalendar_characols
index_column <- mnmsurfdb$get_primary_key(table_label)


# data_nouveau %>% select(!!!characteristic_columns) %>% saveRDS("./dumps/datelink_older.rds")
# data_nouveau %>% select(!!!characteristic_columns) %>% write.csv2("./dumps/datelink_older.csv")
distribution <- categorize_data_update(
  mnmdb = mnmsurfdb,
  table_label = table_label,
  data_future = data_nouveau,
  input_precedence_columns = precedence_columns[[glue::glue("{table_label}")]],
  characteristic_columns = characteristic_columns,
  exclude_columns = c("sampleunit_id") #, "fieldactivitycalendar_id") # , "archive_version_id"
)
print_category_count(distribution, table_label)

# distribution$to_archive
# distribution$reactivate
# distribution$to_upload

# waldo::compare(
#   data_nouveau %>%
#     semi_join(
#       distribution$changed,
#       by = join_by(!!!rlang::syms(fieldcalendar_characols))
#     ),
#   distribution$changed
# )
```


```{r sync-fieldcalendar}

distribution$to_upload <- distribution$to_upload %>% 
  mutate(
    log_user = "maintenance",
    log_update = as.POSIXct(lubridate::floor_date(Sys.time(), unit = ".001s")),
    excluded = FALSE,
    is_frozen = FALSE,
    no_visit_planned = FALSE,
    done_planning = FALSE
  ) 


fieldcalendar_lookup <- redistribute_calendar_data(
  mnmdb = mnmsurfdb,
  table_label = table_label,
  distribution = distribution,
  index_columns = c(index_column),
  characteristic_columns = characteristic_columns,
  skip = list("update" = FALSE, "upload" = FALSE, "archive" = FALSE)
)


```


intermediate check

```{r re-inspect-fieldcalendar}

mnmsurfdb$query_table("FieldCalendar") %>% 
  count(is.na(sampleunit_id)) %>%
  knitr::kable()

# compare stored to true sample location
mnmsurfdb$query_table("FieldCalendar") %>%
  left_join(
    mnmsurfdb$query_table("SampleUnits"),
    by = join_by(grts_address, stratum)
  ) %>%
  filter(sampleunit_id.x != sampleunit_id.y)

```


## Visits

```{r stitch-visits}

stitch_visits <- function() {

  stitch_table_connection(
    mnmdb = mnmsurfdb,
    table_label = "Visits",
    reference_table = "FieldCalendar",
    link_key_column = "fieldcalendar_id",
    lookup_columns = c("grts_address", "stratum", "activity_group_id", "date_start")
  )
  
  stitch_table_connection(
    mnmdb = mnmsurfdb,
    table_label = "Visits",
    reference_table = "SampleUnits",
    link_key_column = "sampleunit_id",
    lookup_columns = c("grts_address", "stratum")
  )
  
  stitch_table_connection(
    mnmdb = mnmsurfdb,
    table_label = "Visits",
    reference_table = "Locations",
    link_key_column = "location_id",
    lookup_columns = c("grts_address")
  )
}
stitch_visits()

```


```{r assemble-new-visits}

visits_characols <- fieldcalendar_characols

potential_visits <- fieldcalendar_lookup %>%
  select(
    !!!rlang::syms(c("fieldcalendar_id", visits_characols))
  ) %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address)
  ) %>%
  mutate(
    log_user = "maintenance",
    log_update = as.POSIXct(lubridate::floor_date(Sys.time(), unit = ".001s")),
    issues = FALSE,
    visit_done = FALSE
  )


visits_upload <- potential_visits %>%
  anti_join(
    mnmsurfdb$query_table("Visits"),
    by = join_by(!!!visits_characols)
  ) %>%
  left_join(
    sampleunits_lookup, #  %>% select(-location_id),
    by = join_by(grts_address, stratum)
  ) 

```

:::{.callout-note title="All Visits are equal..."}
Note: "special" Visits must be distributed to the respective tables.
These tables inherit columns from `Visits`, adding extra ones.
:::

```{r subset-visits}

# Loop Special Activities
selection_of_activities <- list(
  "InstallationVisits" = activity_groupid_lookup %>%
    filter(grepl("^SURFINST", activity_group)) %>%
    pull(activity_group_id) %>% unique, # /WIA
  # "PositioningVisits" = activity_groupid_lookup %>%
  #   filter(grepl("^SPATPOSIT", activity_group)) %>%
  #   pull(activity_group_id) %>% unique, # /SPA
  "SamplingVisits" = activity_groupid_lookup %>%
    filter(grepl("^SURF.*SAMP", activity_group)) %>%
    pull(activity_group_id) %>% unique # /CSA
)

append_defaults <- list(
  # "InstallationVisits" = function(df) df %>%
  #   mutate(
  #     no_diver = FALSE,
  #     soilprofile_unclear = FALSE
  #   ) # /WIA
)


```


```{r upload-special-visits}

remaining_new_visits <- visits_upload

# table_label <- "InstallationVisits"
for (table_label in names(selection_of_activities)) {

  # subset the data by using selection_of_activities -> activity_group_id's
  select_activities <- selection_of_activities[[table_label]]
  special_visits <- remaining_new_visits %>%
    filter(activity_group_id %in% select_activities)

  # extra columns
  if (table_label %in% names(append_defaults)) {
    special_visits <- append_defaults[[table_label]](special_visits)
  }

  # append=upload data to the activity table
  # double-check existing to avoid dups
  # existing <- mnmsurfdb$query_table(table_label)
  sa_lookup <- upload_and_lookup(
    mnmsurfdb,
    table_label = table_label,
    data_to_append = special_visits,
    characteristic_columns = visits_characols,
    index_columns = c("visit_id"),
    verbose = TRUE
  )

  # anti-join remaining_new_visits
  remaining_new_visits <- remaining_new_visits %>%
    anti_join(
      special_visits,
      by = join_by(
        fieldcalendar_id,
        grts_address,
        stratum,
        activity_group_id,
        date_start)
    )

}

```

```{r upload-non-special-visits}

other_visits_lookup <- upload_and_lookup(
  mnmsurfdb,
  table_label = "OtherVisits",
  data_to_append = remaining_new_visits,
  characteristic_columns = visits_characols,
  index_columns = c("othervisit_id"),
  verbose = TRUE
)


```



```{r reconnect-visits}

stitch_visits()

mnmsurfdb$query_table("Visits") %>% 
  count(
    is.na(location_id),
    is.na(sampleunit_id),
    is.na(fieldcalendar_id)
  ) %>%
  knitr::kable()

```


archive visits of archived FWCals

```{r archive-visits-fwcal}

trgtab <- mnmsurfdb$get_namestring("Visits")
srctab <- mnmsurfdb$get_namestring("FieldCalendar")
link_key_column <- "archive_version_id"
lookup_criteria <- c("TRGTAB.fieldcalendar_id = SRCTAB.fieldcalendar_id")

update_string <- glue::glue("
  UPDATE {trgtab} AS TRGTAB
    SET
      {link_key_column} = SRCTAB.{link_key_column}
    FROM {srctab} AS SRCTAB
    WHERE
     ({paste0(lookup_criteria, collapse = ') AND (')})
  ;")

mnmsurfdb$execute_sql(update_string)

mnmsurfdb$query_table("FieldCalendar") %>%
  anti_join(
    mnmsurfdb$query_table("Visits"),
    by = join_by(fieldcalendar_id, archive_version_id)
  ) %>% nrow()

```




## LocationInfos

```{r update-locationinfos}

new_locinfos <- sample_units %>%
  distinct(
    grts_address
  ) %>%
  mutate(
    log_creator = "maintenance",
    log_creation = as.POSIXct(lubridate::floor_date(Sys.time(), unit = ".001s")),
    log_user = "maintenance",
    log_update = as.POSIXct(lubridate::floor_date(Sys.time(), unit = ".001s"))
  )

new_locinfos <- new_locinfos %>%
  anti_join(
    mnmsurfdb$query_table("LocationInfos"),
    by = join_by(grts_address)
  ) %>%
  left_join(
    locations_lookup,
    by = join_by(grts_address),
  )


locationinfo_lookup <- update_cascade_lookup(
  table_label = "LocationInfos",
  new_data = new_locinfos,
  index_columns = c("locationinfo_id"),
  characteristic_columns = c("grts_address"),
  tabula_rasa = FALSE,
  verbose = TRUE
)


```


## Landuse

```{r update-landuse}
update_landuse_in_locationinfos(mnmsurfdb)
```


# post hoc


```{r stitched-up}

out <- processx::run(
  "Rscript",
  c("102_re_link_foreign_keys.R", suffix),
  spinner = TRUE,
  echo = TRUE
)

```


```{r step-n-safety-dump}

now <- format(Sys.time(), "%Y%m%d%H%M")

if (isFALSE(grepl("-staging", mnmsurfdb_mirror))) {
  mnmsurfdb$dump_all(
    here::here("dumps", glue::glue("rep_post_update_{mnmsurfdb$database}_{now}.sql")),
    exclude_schema = c("tiger", "public")
  )
}

```



```{r launch-consistency-dashboard}

out <- processx::run(
  "quarto",
  c("render", "046_mnmsurfdb_consistency_dashboard.qmd", "--to", "html"),
  echo = TRUE,
  spinner = TRUE
)

```


```{r done-updating-rep}

message("")
message("________________________________________________________________")
message(" >>>>> Finished REP data update. ")
message("________________________________________________________________")

```

