---
title: "Migrate Special Activities"
date: "2026-03-01"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---


# Structure


:::{.callout-warning}
Working on the structure is tricky,
especially on `_staging`.

Some structural changes on the mirror will prohibit the `pg_dump` update to work;
re-initialization, dump, and re-run of the changes will fix it.

:::

## Create New Tables

### `InstallationVisits`

```{sql}
--| eval: false

SET standard_conforming_strings = ON;
-- SET search_path TO pg_catalog,public,"inbound";

BEGIN;
DROP TABLE IF EXISTS "inbound"."InstallationVisits" CASCADE;

CREATE TABLE "inbound"."InstallationVisits"()
INHERITS ("inbound"."Visits")
;

COMMENT ON TABLE "inbound"."InstallationVisits" IS E'extra information collected for certain activities (well installations); subset of Visits';

ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN installationvisit_id int NOT NULL; 
COMMENT ON COLUMN "inbound"."InstallationVisits".installationvisit_id IS E'technical index (extra, on top of visit_id)';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN photo_soil_1_peilbuis varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".photo_soil_1_peilbuis IS E'photo of the soil drill profile: peilbuis';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN photo_soil_2_piezometer varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".photo_soil_2_piezometer IS E'photo of the soil drill profile: piezometer';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN photo_well varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".photo_well IS E'photo of the placed well/pair';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN watina_code_used_1_peilbuis varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".watina_code_used_1_peilbuis IS E'watina code of the `odd` subset of wells';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN watina_code_used_2_piezometer varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".watina_code_used_2_piezometer IS E'watina code of the `even` subset of wells';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN soilprofile_notes varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".soilprofile_notes IS E'notes about the soil profiles';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN soilprofile_unclear boolean NOT NULL DEFAULT FALSE; 
COMMENT ON COLUMN "inbound"."InstallationVisits".soilprofile_unclear IS E'help requested for evaluation of the soil profile';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN random_point_number smallint; 
COMMENT ON COLUMN "inbound"."InstallationVisits".random_point_number IS E'if so, which random point was chosen';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN no_diver boolean NOT NULL DEFAULT FALSE; 
COMMENT ON COLUMN "inbound"."InstallationVisits".no_diver IS E'highlight issues (use notes to specify)';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN diver_id varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".diver_id IS E'link to the table of available divers';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN free_diver varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".free_diver IS E'free field to enter a non-registered diver code';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN reused_existing_well boolean DEFAULT FALSE; 
COMMENT ON COLUMN "inbound"."InstallationVisits".reused_existing_well IS E'flag if an existing installation was reused';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN reused_with_replacement boolean DEFAULT FALSE; 
COMMENT ON COLUMN "inbound"."InstallationVisits".reused_with_replacement IS E'whether an existing installation was reused and refreshed';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN used_water_from_tap boolean; 
COMMENT ON COLUMN "inbound"."InstallationVisits".used_water_from_tap IS E'whether or not tap water was used for installation';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN used_water_source varchar; 
COMMENT ON COLUMN "inbound"."InstallationVisits".used_water_source IS E'source of the water used for facilitating installation';
ALTER TABLE "inbound"."InstallationVisits" ADD COLUMN is_cattleproof boolean; 
COMMENT ON COLUMN "inbound"."InstallationVisits".is_cattleproof IS E'indicate installations with extra cattle protection';

COMMIT;

-- sequence installationvisit_id
CREATE SEQUENCE "inbound".seq_installationvisit_id
INCREMENT BY 1
MINVALUE 0
MAXVALUE 2147483647
START WITH 1
CACHE 1
NO CYCLE
OWNED BY "inbound"."InstallationVisits".installationvisit_id;
ALTER TABLE "inbound"."InstallationVisits" ALTER COLUMN installationvisit_id
 SET DEFAULT nextval('inbound.seq_installationvisit_id'::regclass);

GRANT USAGE ON SEQUENCE "inbound"."seq_installationvisit_id" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk, ward, monkey;
GRANT SELECT ON SEQUENCE "inbound"."seq_installationvisit_id" TO monkey;

GRANT SELECT ON "inbound"."InstallationVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk, ward, monkey;

GRANT INSERT ON "inbound"."InstallationVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;
GRANT UPDATE ON "inbound"."InstallationVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;
GRANT DELETE ON "inbound"."InstallationVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;


```

### `SamplingVisits`

```{sql}
--| eval: false

SET standard_conforming_strings = ON;
-- SET search_path TO pg_catalog,public,"inbound";

DROP TABLE IF EXISTS "inbound"."SamplingVisits" CASCADE;

BEGIN;
CREATE TABLE "inbound"."SamplingVisits"()
INHERITS ("inbound"."Visits")
;

COMMENT ON TABLE "inbound"."SamplingVisits" IS E'extra information collected for certain activities (chemical sampling); subset of Visits';

ALTER TABLE "inbound"."SamplingVisits" ADD COLUMN samplingvisit_id int NOT NULL; 
COMMENT ON COLUMN "inbound"."SamplingVisits".samplingvisit_id IS E'technical index (extra, on top of visit_id)';
ALTER TABLE "inbound"."SamplingVisits" ADD COLUMN project_code varchar; 
COMMENT ON COLUMN "inbound"."SamplingVisits".project_code IS E'LIMS project code of this sample';
ALTER TABLE "inbound"."SamplingVisits" ADD COLUMN recipient_code varchar; 
COMMENT ON COLUMN "inbound"."SamplingVisits".recipient_code IS E'LIMS recipient code of this sample';

COMMIT;

-- sequence samplingvisit_id
CREATE SEQUENCE "inbound".seq_samplingvisit_id
INCREMENT BY 1
MINVALUE 0
MAXVALUE 2147483647
START WITH 1
CACHE 1
NO CYCLE
OWNED BY "inbound"."SamplingVisits".samplingvisit_id;
ALTER TABLE "inbound"."SamplingVisits" ALTER COLUMN samplingvisit_id
 SET DEFAULT nextval('inbound.seq_samplingvisit_id'::regclass);

GRANT USAGE ON SEQUENCE "inbound"."seq_samplingvisit_id" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk, ward, monkey;
GRANT SELECT ON SEQUENCE "inbound"."seq_samplingvisit_id" TO monkey;

GRANT SELECT ON "inbound"."SamplingVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk, ward, monkey;

GRANT INSERT ON "inbound"."SamplingVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;
GRANT UPDATE ON "inbound"."SamplingVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;
GRANT DELETE ON "inbound"."SamplingVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;


```


### `PositioningVisits`

```{sql}
--| eval: false
SET standard_conforming_strings = ON;
-- SET search_path TO pg_catalog,public,"inbound";

DROP TABLE IF EXISTS "inbound"."PositioningVisits" CASCADE;

BEGIN;
CREATE TABLE "inbound"."PositioningVisits"()
INHERITS ("inbound"."Visits")
;

COMMENT ON TABLE "inbound"."PositioningVisits" IS E'extra information collected for certain activities (spatial positioning); subset of Visits';

ALTER TABLE "inbound"."PositioningVisits" ADD COLUMN positioningvisit_id int NOT NULL; 
COMMENT ON COLUMN "inbound"."PositioningVisits".positioningvisit_id IS E'technical index (extra, on top of visit_id)';

ALTER TABLE "inbound"."PositioningVisits" ADD COLUMN require_total_station boolean; 
COMMENT ON COLUMN "inbound"."PositioningVisits".require_total_station IS E'whether or not total station will be / was required for sattelite connection upon positioning';

COMMIT;

-- sequence positioningvisit_id
CREATE SEQUENCE "inbound".seq_positioningvisit_id
INCREMENT BY 1
MINVALUE 0
MAXVALUE 2147483647
START WITH 1
CACHE 1
NO CYCLE
OWNED BY "inbound"."PositioningVisits".positioningvisit_id;
ALTER TABLE "inbound"."PositioningVisits" ALTER COLUMN positioningvisit_id
 SET DEFAULT nextval('inbound.seq_positioningvisit_id'::regclass);


GRANT USAGE ON SEQUENCE "inbound"."seq_positioningvisit_id" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk, ward, monkey;
GRANT SELECT ON SEQUENCE "inbound"."seq_positioningvisit_id" TO monkey;

GRANT SELECT ON "inbound"."PositioningVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk, ward, monkey;

GRANT INSERT ON "inbound"."PositioningVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;
GRANT UPDATE ON "inbound"."PositioningVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;
GRANT DELETE ON "inbound"."PositioningVisits" TO tom, yglinga, jens, lise, wouter, floris, karen, janne, falk;

```


## Fill With Data

### prep

> this is somewhat more complex;
> I need to capture the data before DELETE FROM ONLY "inbound"."Visits" ;
> or move the rows with INSERT... SELECT FROM ONLY;
> but all that while respecting uniqueness constraints.
> Maybe better have an R script? -> no, should work with "INSERT INTO"

(that was past me... now everything seems to be good.)

There were several _id linkage issues.
!!! link tables (first, the old way)
```{r}
source("095_re_link_foreign_keys_optional_old.R")
```

### fill `InstallationVisits`

```{sql}
--| eval: false
-- BEGIN;

INSERT INTO "inbound"."InstallationVisits" (
  log_user,
  log_update,
  samplelocation_id,
  fieldworkcalendar_id,
  grts_address,
  stratum,
  activity_group_id,
  date_start,
  teammember_id,
  date_visit,
  notes,
  photo,
  issues,
  visit_done,
  archive_version_id,
  photo_soil_1_peilbuis,
  photo_soil_2_piezometer,
  photo_well,
  watina_code_used_1_peilbuis,
  watina_code_used_2_piezometer,
  soilprofile_notes,
  soilprofile_unclear,
  random_point_number,
  no_diver,
  diver_id,
  free_diver,
  reused_existing_well,
  reused_with_replacement,
  used_water_from_tap,
  used_water_source
)
SELECT
  WIA.log_user,
  WIA.log_update,
  VIS.samplelocation_id,
  VIS.fieldworkcalendar_id,
  VIS.grts_address,
  VIS.stratum,
  VIS.activity_group_id,
  VIS.date_start,
  VIS.teammember_id,
  VIS.date_visit,
  VIS.notes,
  VIS.photo,
  VIS.issues,
  VIS.visit_done,
  VIS.archive_version_id,
  WIA.photo_soil_1_peilbuis,
  WIA.photo_soil_2_piezometer,
  WIA.photo_well,
  WIA.watina_code_used_1_peilbuis,
  WIA.watina_code_used_2_piezometer,
  WIA.soilprofile_notes,
  WIA.soilprofile_unclear,
  WIA.random_point_number,
  WIA.no_diver,
  WIA.diver_id,
  WIA.free_diver,
  WIA.reused_existing_well,
  WIA.reused_with_replacement,
  WIA.used_water_from_tap,
  WIA.used_water_source
FROM "inbound"."WellInstallationActivities" AS WIA, "inbound"."Visits" AS VIS
WHERE VIS.visit_id = WIA.visit_id
  AND VIS.grts_address = WIA.grts_address
  AND VIS.stratum = WIA.stratum
  AND VIS.date_start = WIA.date_start
  AND VIS.activity_group_id = 4
  AND WIA.activity_group_id = 4
  AND VIS.activity_group_id = WIA.activity_group_id
  -- AND WIA.grts_address = 23238
;


DELETE
-- SELECT *
FROM ONLY "inbound"."Visits" 
WHERE activity_group_id = 4
AND fieldworkcalendar_id IN (
  SELECT DISTINCT fieldworkcalendar_id
  FROM "inbound"."InstallationVisits"
)
;

```


### fill `SamplingVisits`

```{sql}
--| eval: false
-- BEGIN;
-- SELECT DISTINCT activity_group_id FROM "inbound"."ChemicalSamplingActivities" AS CSA;

INSERT INTO "inbound"."SamplingVisits" (
  log_user,
  log_update,
  samplelocation_id,
  fieldworkcalendar_id,
  grts_address,
  stratum,
  activity_group_id,
  date_start,
  teammember_id,
  date_visit,
  notes,
  photo,
  issues,
  visit_done,
  archive_version_id,
  project_code,
  recipient_code
)
SELECT
  CSA.log_user,
  CSA.log_update,
  VIS.samplelocation_id,
  VIS.fieldworkcalendar_id,
  VIS.grts_address,
  VIS.stratum,
  VIS.activity_group_id,
  VIS.date_start,
  VIS.teammember_id,
  VIS.date_visit,
  VIS.notes,
  VIS.photo,
  VIS.issues,
  VIS.visit_done,
  VIS.archive_version_id,
  CSA.project_code,
  CSA.recipient_code
FROM "inbound"."ChemicalSamplingActivities" AS CSA, "inbound"."Visits" AS VIS
WHERE VIS.visit_id = CSA.visit_id
  AND VIS.grts_address = CSA.grts_address
  AND VIS.stratum = CSA.stratum
  AND VIS.date_start = CSA.date_start
  AND VIS.activity_group_id IN (13, 16)
  AND CSA.activity_group_id IN (13, 16)
  AND VIS.activity_group_id = CSA.activity_group_id
  -- AND CSA.grts_address = 23238
;


DELETE
-- SELECT *
FROM ONLY "inbound"."Visits" 
WHERE activity_group_id IN (13, 16)
AND fieldworkcalendar_id IN (
  SELECT DISTINCT fieldworkcalendar_id
  FROM "inbound"."InstallationVisits"
)
;

```


### fill `PositioningVisits`

```{sql}
--| eval: false
-- BEGIN;
-- SELECT DISTINCT activity_group_id FROM "inbound"."SpatialPositioningActivities" AS SPA;

INSERT INTO "inbound"."PositioningVisits" (
  log_user,
  log_update,
  samplelocation_id,
  fieldworkcalendar_id,
  grts_address,
  stratum,
  activity_group_id,
  date_start,
  teammember_id,
  date_visit,
  notes,
  photo,
  issues,
  visit_done,
  archive_version_id,
  require_total_station
)
SELECT
  SPA.log_user,
  SPA.log_update,
  VIS.samplelocation_id,
  VIS.fieldworkcalendar_id,
  VIS.grts_address,
  VIS.stratum,
  VIS.activity_group_id,
  VIS.date_start,
  VIS.teammember_id,
  VIS.date_visit,
  VIS.notes,
  VIS.photo,
  VIS.issues,
  VIS.visit_done,
  VIS.archive_version_id,
  SPA.require_total_station
FROM "inbound"."SpatialPositioningActivities" AS SPA, "inbound"."Visits" AS VIS
WHERE VIS.visit_id = SPA.visit_id
  AND VIS.grts_address = SPA.grts_address
  AND VIS.stratum = SPA.stratum
  AND VIS.date_start = SPA.date_start
  AND VIS.activity_group_id IN (27, 28)
  AND SPA.activity_group_id IN (27, 28)
  AND VIS.activity_group_id = SPA.activity_group_id
  -- AND SPA.grts_address = 23238
;


DELETE
-- SELECT *
FROM ONLY "inbound"."Visits" 
WHERE activity_group_id IN (27, 28)
AND fieldworkcalendar_id IN (
  SELECT DISTINCT fieldworkcalendar_id
  FROM "inbound"."PositioningVisits"
)
;

```



### post

!!! link tables (the new way)
```{r}
source("095_re_link_foreign_keys_optional.R")
```


## Redirect Traffic

<https://stackoverflow.com/questions/12343984/insert-trigger-to-update-another-table-using-postgresql>

All updates on the old table should be reflected in the new one.
Users do not do inserts etc.


```{sql redirect-wia}
--| eval: false

DROP FUNCTION IF EXISTS "metadata".sync_wia CASCADE;
CREATE FUNCTION "metadata".sync_wia() RETURNS trigger AS $sync_wia$
BEGIN

  UPDATE "inbound"."InstallationVisits"
  SET 
      photo_soil_1_peilbuis = NEW.photo_soil_1_peilbuis,
      photo_soil_2_piezometer = NEW.photo_soil_2_piezometer,
      photo_well = NEW.photo_well,
      watina_code_used_1_peilbuis = NEW.watina_code_used_1_peilbuis,
      watina_code_used_2_piezometer = NEW.watina_code_used_2_piezometer,
      soilprofile_notes = NEW.soilprofile_notes,
      soilprofile_unclear = NEW.soilprofile_unclear,
      random_point_number = NEW.random_point_number,
      no_diver = NEW.no_diver,
      diver_id = NEW.diver_id,
      free_diver = NEW.free_diver,
      reused_existing_well = NEW.reused_existing_well,
      reused_with_replacement = NEW.reused_with_replacement,
      used_water_from_tap = NEW.used_water_from_tap,
      used_water_source = NEW.used_water_source
  WHERE grts_address = NEW.grts_address
    AND stratum = NEW.stratum
    AND activity_group_id = 4
    AND date_start = NEW.date_start
  ;
  
  RETURN NEW;
END;
$sync_wia$ LANGUAGE plpgsql;

DROP TRIGGER IF EXISTS wia_sync_trigger ON "inbound"."WellInstallationActivities";
CREATE TRIGGER wia_sync_trigger
BEFORE UPDATE ON "inbound"."WellInstallationActivities"
FOR EACH ROW EXECUTE PROCEDURE "metadata".sync_wia();

-- COMMIT;
```



```{sql redirect-csa}
--| eval: false

DROP FUNCTION IF EXISTS "metadata".sync_csa CASCADE;
CREATE FUNCTION "metadata".sync_csa() RETURNS trigger AS $sync_csa$
BEGIN

  UPDATE "inbound"."SamplingVisits"
  SET 
    project_code = NEW.project_code,
    recipient_code = NEW.recipient_code
  WHERE grts_address = NEW.grts_address
    AND stratum = NEW.stratum
    AND activity_group_id IN (13, 16)
    AND activity_group_id = NEW.activity_group_id
    AND date_start = NEW.date_start
  ;
  
  RETURN NEW;
END;
$sync_csa$ LANGUAGE plpgsql;

DROP TRIGGER IF EXISTS csa_sync_trigger ON "inbound"."ChemicalSamplingActivities";
CREATE TRIGGER csa_sync_trigger
BEFORE UPDATE ON "inbound"."ChemicalSamplingActivities"
FOR EACH ROW EXECUTE PROCEDURE "metadata".sync_csa();

-- COMMIT;
```



```{sql redirect-spa}
--| eval: false

DROP FUNCTION IF EXISTS "metadata".sync_spa CASCADE;
CREATE FUNCTION "metadata".sync_spa() RETURNS trigger AS $sync_spa$
BEGIN

  UPDATE "inbound"."PositioningVisits"
  SET 
    require_total_station = NEW.require_total_station
  WHERE grts_address = NEW.grts_address
    AND stratum = NEW.stratum
    AND activity_group_id IN (27, 28)
    AND activity_group_id = NEW.activity_group_id
    AND date_start = NEW.date_start
  ;
  
  RETURN NEW;
END;
$sync_spa$ LANGUAGE plpgsql;

DROP TRIGGER IF EXISTS spa_sync_trigger ON "inbound"."SpatialPositioningActivities";
CREATE TRIGGER spa_sync_trigger
BEFORE UPDATE ON "inbound"."SpatialPositioningActivities"
FOR EACH ROW EXECUTE PROCEDURE "metadata".sync_spa();

-- COMMIT;
```


:::{.callout-note}
Whoohoo, it works!
:::



Test redirect (on `_staging`):

```{sql}
--| eval: false
SELECT grts_address, stratum, activity_group_id, date_start, date_visit
FROM "inbound"."Visits" AS VIS
WHERE VIS.grts_address = 23238 AND activity_group_id = 4;

SELECT grts_address, stratum, activity_group_id, date_start, date_visit, random_point_number
FROM "inbound"."InstallationVisits"
WHERE grts_address = 23238;

SELECT grts_address, stratum, activity_group_id, date_start, date_visit, project_code
FROM "inbound"."SamplingVisits"
WHERE grts_address = 23238;

SELECT grts_address, stratum, activity_group_id, date_start, date_visit, require_total_station
FROM "inbound"."PositioningVisits"
WHERE grts_address = 23238;


SELECT VIS.visit_id, WIA.grts_address, WIA.stratum, WIA.activity_group_id, WIA.date_start, VIS.date_visit, WIA.random_point_number
FROM "inbound"."WellInstallationActivities" AS WIA
LEFT JOIN "inbound"."Visits" AS VIS
ON VIS.visit_id = WIA.visit_id
WHERE WIA.grts_address = 23238;
-- this one should be empty now; however, it somehow tripled on a prev attempt.



-- all-in-one testing!
SELECT grts_address, stratum, activity_group_id, date_start, date_visit,
random_point_number, project_code, require_total_station
FROM ONLY "inbound"."Visits"
NATURAL FULL JOIN "inbound"."InstallationVisits"
NATURAL FULL JOIN "inbound"."SamplingVisits"
NATURAL FULL JOIN "inbound"."PositioningVisits"
WHERE grts_address = 23238;


UPDATE "inbound"."WellInstallationActivities"
SET random_point_number = 1
WHERE grts_address = 23238;

UPDATE "inbound"."ChemicalSamplingActivities"
SET project_code = 'abc123'
WHERE grts_address = 23238;

UPDATE "inbound"."SpatialPositioningActivities"
SET require_total_station = TRUE
WHERE grts_address = 23238;


SELECT grts_address, stratum, activity_group_id, date_start, date_visit
FROM "inbound"."Visits" AS VIS
WHERE VIS.grts_address = 23238 AND activity_group_id = 4;

SELECT grts_address, stratum, activity_group_id, date_start, date_visit, random_point_number
FROM "inbound"."InstallationVisits"
WHERE grts_address = 23238;


SELECT VIS.visit_id, WIA.grts_address, WIA.stratum, WIA.activity_group_id, WIA.date_start, VIS.date_visit, WIA.random_point_number
FROM "inbound"."WellInstallationActivities" AS WIA
LEFT JOIN "inbound"."Visits" AS VIS
ON VIS.visit_id = WIA.visit_id
WHERE WIA.grts_address = 23238;


```

:::{.callout-warning}
... but the INSERT didn't :(

- some columns from `Visits` were missing
- duplicates not removed

... but this is solved now via a better INSERT and a distinct DELETE.
:::

# USAGE

## Adjust the VIEWs: 

### `gw_FieldworkPlanning.sql`

    [!] There was an unnecessary join of WIA...
    
seems to be correct...

```{sql}
--| eval: false
SELECT * FROM "inbound"."Visits" WHERE activity_group_id = 4 AND grts_address = 23238;
SELECT * FROM "outbound"."FieldworkPlanning"
WHERE activity_group_id = 4
AND grts_address = 23238;

```


### `gw_FieldWork.sql`

adjusted to replace WIA by VISIT:

```{sql}
--| eval: false
SELECT grts_address, stratum, date_start, activity_group_id, date_visit
FROM "inbound"."Visits"
WHERE grts_address = 23238
; -- no dups on production; but dups on staging


-- SELECT grts_address, stratum, date_start, activity_group_id, date_visit, VISIT.date_visit, IVIS.date_visit, random_point_number
SELECT *
SELECT visit_id, soilprofile_unclear
FROM ONLY "inbound"."Visits"
NATURAL FULL JOIN "inbound"."InstallationVisits"
-- NATURAL FULL JOIN "inbound"."SamplingVisits"
-- NATURAL FULL JOIN "inbound"."PositioningVisits"
WHERE grts_address = 23238
  AND installationvisit_id IS NOT NULL
;


```

// args... there are empty lines? -> duplicates of other activities...
--> solved!


```
.______________________________.
|    IMPORTANT REMINDER:       |
|    the ONLY is crucual!      |
!______________________________!
```
https://dba.stackexchange.com/questions/94050/query-parent-table-and-get-child-tables-columns/125028#125028
https://stackoverflow.com/questions/40960162/natural-full-outer-join-or-using-if-common-attribute-is-null

I have to really take care from which table the column is taken.
-> best wrap the query.

```{sql}
--| eval: false

SELECT *
FROM "inbound"."FieldWork"
WHERE grts_address = 23238
;

SELECT *
FROM "outbound"."FieldworkPlanning"
WHERE grts_address = 23238
;

```

again, the issue was key linking -> link repeatedly.

# Testing QGIS

Seems to work as expected. All relevant fields update.


# TODO

other daily scripts

?? there are the `is_<activity>` columns... they should be integrated to the GAP table. 


# Cleanup

after everything works,
backup and then
drop WIA/CSA/SPA tables
