---
title: "Overview MNM Groundwater Installations"
subtitle: ""
date: "2025-11-28"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---

# Task

Requested are:

- het aantal koppels dat tot en met 28/11 is geïnstalleerd, in totaal en per maatwerkgebied
- idem voor het aantal locaties waar de loceval is uitgevoerd
- [de totale geplande aantallen in de drie meetnetten: een update dus van onderstaande tabel obv de actuele steekproeven (POC 0.14)] -> @FV


```{r date-filter}
report_date <- as.Date("2025-11-28")

```

# Preparation

load libraries...

```{r libraries}

# libraries
source("MNMLibraryCollection.R")
# load_poc_common_libraries()
load_database_interaction_libraries()

source("MNMDatabaseConnection.R")
source("MNMDatabaseToolbox.R")

```


connect to the server...

```{r connect-databases}

config_filepath <- file.path("./inbopostgis_server.conf")

locevaldb_mirror <- glue::glue("loceval")
mnmgwdb_mirror <- glue::glue("mnmgwdb")

locevaldb <- connect_mnm_database(
  config_filepath,
  database_mirror = locevaldb_mirror,
  user = "monkey",
  password = NA
)

mnmgwdb <- connect_mnm_database(
  config_filepath,
  database_mirror = mnmgwdb_mirror,
  user = "monkey",
  password = NA
)
```


load POC info:

```{r load-rdata}
load_poc_common_libraries()
load_poc_rdata(reload = FALSE, to_env = globalenv())

domains %>%
  sf::st_drop_geometry() %>% 
  knitr::kable(format = "markdown")
```


# Number of Location Evaluations

## counting

```{r loceval-count}

all_locevals <- locevaldb$query_table("Locations") %>%
  left_join(
    locevaldb$query_table("Visits"),
    by = join_by(location_id),
    relationship = "one-to-many",
    suffix = c("_loc", "")
  ) %>% 
  inner_join(
    locevaldb$query_table("GroupedActivities") %>%
      filter(activity_group == "LOCEVALTERR") %>%
      distinct(activity_group_id, activity_group),
    by = join_by(activity_group_id)
  ) %>%
  left_join(
    locevaldb$query_table("SampleUnits"),
    by = join_by(sampleunit_id),
    relationship = "many-to-one",
    suffix = c("", "_su")
  ) %>% 
  filter(visit_done, date_visit <= report_date) %>%
  sf::st_set_geometry("wkb_geometry") %>% 
  select(
    grts_address,
    type,
    type_assessed,
    date_visit,
    is_replaced,
    type_is_absent,
    wkb_geometry
  )

all_locevals %>%
  sf::st_drop_geometry() %>%
  count(is_replaced, type_is_absent) %>% 
  janitor::adorn_totals() %>% 
  knitr::kable(format = "markdown")

```



```{r view-on-map}
mapview::mapview(
  domains,
  zcol = "domain",
  alpha.region = 0.1
) +
mapview::mapview(
  all_locevals,
  zcol = "type_is_absent"
)
```

## localizing

:::{.callout-warning}
Note: In the table below, "Vlaams Gewest" is the TOTAL, it includes the locevals in the SBZs.
:::

```{r intersect-domains}

locevals_per_region <- sf::st_join(
    all_locevals,
    domains,
    join = sf::st_intersects
  ) 

locevals_per_region %>%
  sf::st_drop_geometry() %>%
  count(domain_name_nl, type_is_absent) %>% 
  tidyr::pivot_wider(
    values_from = n,
    names_from = type_is_absent
  ) %>%
  setNames(c("domain", "type confirmed", "type absent")) %>% 
  janitor::adorn_totals(where = "col") %>% 
  knitr::kable(format = "markdown")

```


# Number of Well Placements

## counting

```{r gw-count}

all_gwdb <- mnmgwdb$query_table("Locations") %>%
  left_join(
    mnmgwdb$query_table("Visits"),
    by = join_by(location_id),
    relationship = "one-to-many",
    suffix = c("_loc", "")
  ) %>% 
  inner_join(
    mnmgwdb$query_table("GroupedActivities") %>%
      filter(activity_group == "GWINSTPIEZWELL") %>%
      distinct(activity_group_id, activity_group),
    by = join_by(activity_group_id)
  ) %>%
  left_join(
    mnmgwdb$query_table("SampleLocations"),
    by = join_by(samplelocation_id),
    relationship = "many-to-one",
    suffix = c("", "_sl")
  ) %>% 
  filter(visit_done, date_visit <= report_date) %>%
  sf::st_set_geometry("wkb_geometry") %>% 
  select(
    grts_address,
    stratum,
    date_visit,
    issues,
    archive_version_id,
    archive_version_id_sl,
    notes,
    wkb_geometry
  ) %>%
  mutate(archived = coalesce(archive_version_id_sl, archive_version_id))

all_gwdb %>%
  sf::st_drop_geometry() %>%
  count(archived, issues) %>% 
  janitor::adorn_totals() %>% 
  knitr::kable(format = "markdown")

```



```{r view-placements-on-map}

mapview::mapview(
  domains,
  zcol = "domain",
  alpha.region = 0.1
) +
mapview::mapview(
  all_gwdb,
  zcol = "issues"
)

```



## localizing


:::{.callout-warning}
Reminder: in the table below, "Flanders" also incorporates all the other subsets of data. 
It is the total number of placements.
Do not draw totals per column!
:::

```{r intersect-gw-domains}

installations_per_region <- sf::st_join(
    all_gwdb,
    domains,
    join = sf::st_intersects
  ) 

installations_per_region %>%
  sf::st_drop_geometry() %>%
  count(domain, issues) %>% 
  tidyr::pivot_wider(
    values_from = n,
    names_from = issues
  ) %>%
  setNames(c("domain", "installed", "issues encountered")) %>% 
  janitor::adorn_totals(where = "col") %>% 
  knitr::kable(format = "markdown")

```



## issues

What kind of issues?

```{r show-issues}

all_gwdb %>% 
  sf::st_drop_geometry() %>%
  filter(issues) %>%
  knitr::kable(format = "markdown")

```
