---
title: "Aquatic Habitat Types: Observation Well Placement"
subtitle: "part II: streams"
date: "2025-05-20"
format:
  html:
    toc: true
    html-math-method: katex
    code-fold: false
    embed-resources: true
knitr:
  opts_chunk:
    echo: true
---



```{r libraries}

void <- suppressPackageStartupMessages

conflictRules("n2khab", exclude = c("read_schemes", "read_scheme_types"))
library("stringr")     |> void() # string ragging
library("dplyr")       |> void() # our favorite data wrangling toolbox
library("tidyr")       |> void() # data preparation and rearrangement
library("googledrive") |> void() # google drive data to/fro
library("inbospatial") |> void() # convenience functions for wfs and other queries
library("sf")          |> void() # spatial feature processing
library("terra")       |> void() # spatial raster data
# library("qgisprocess") |> void() # interface to the procedures of our favorite GIS software
library("mapview")     |> void() # show spatial features on a map
library("n2khab")      |> void() # n2khab data and common functions
library("n2khabmon")   |> void() # monitoring schemes for natura2000 habitats

# print sample from sf objects
kableprint <- function(df, show_rows = 5) {
  knitr::kable(df[sample(seq_len(nrow(df)), show_rows), ])
}

mapviewOptions(fgb = FALSE) # https://stackoverflow.com/a/65485896

source(here::here("..", "R", "import_aquatic_positioning.R"))

```


# data

## Assembling Aquatic Habitat Types

### data consistence

```{r datasource-consistency}
confirm_n2khab_data_consistency()
```


### Streams

Temporary approach to generate `segm_3260` (i.e. it will miss a part and some may be false positives)
(unit ID defined by `unit_id`)

```{r load-streams}
# read_watercourse_100mseg(element = "lines")[habstream, ] %>%
#   mapview()
# read_watercourse_100mseg(element = "points")[habstream, ] %>% 
#   mapview()
# read_habitatstreams() %>%
#   mapview()

# habitat 3260 from
#     Biologische Waarderingskaart en Natura 2000 Habitatkaart
#     https://doi.org/10.21436/inbor.96375305
# ... are the streams
habstream <- read_habitatstreams()

# for those streams, we use the 100m line segments
# applying spatial supsetting (intersect!) with sf_x[sf_y, ]
#   not well documented in https://r-spatial.github.io/sf/reference/sf.html
#   -> geocomputation with R https://r.geocompx.org/spatial-operations#spatial-subsetting
#   habstream <- read_habitatstreams()
#   seg_all <- read_watercourse_100mseg(element = "lines")
#   seg_reference <- seg_all[habstream, , op = sf::st_intersects]
#   seg_test <- seg_all[lengths(sf::st_intersects(seg_all, habstream, sparse = TRUE)) > 0, ]
#   identical(seg_reference, seg_test)
segm_3260 <-
  read_watercourse_100mseg(element = "lines")[habstream, ] %>%
  unite(unit_id, vhag_code, rank) # tidyr::unite string concatenation

kableprint(segm_3260) # unique identifier for line segments

```

## load the sample


### google authentification

Currently, the latest version of the sample is distributed via an `.RData` file on the google drive.

```{r google-auth}
google_drive_init()
```



### load/restore sample data

Download the sample data (unless it is already there).

```{r sample-data-download}
# latest (20250506):
#   target_sample_filepath <- file.path("./data", "objects_for_aq_piezometers_panfl_pan5.RData")
#   googledrive::as_id("1Z93w-C3XRQ8756W3835JPfxggGEstjKR"),


force_reload_sample <- FALSE
target_sample_filepath <- file.path("./data", "objects_for_aq_piezometers_panfl_pan5.RData")

if (force_reload_sample || !file.exists(target_sample_filepath)) {
  download_poc_rdata_file(target_sample_filepath)
}

# load the data into a new environment
env_extradata <- load_rdata_environment()
```

(adjusted to read full POC `.RData`, [see here](https://github.com/inbo/n2khab-mne-design/blob/7a08ab9d36669d3a5b64d12b8bc35ff7c7a6a5d1/100_design_common/010_prototyping_sampling_and_revisit_design/helper_scripts/support_dcp_and_fieldwork.R))


restore sample data structure
Below object can be used to filter the foregoing geospatial objects, taking
into account that: rows with ...

- `sample_support_code == watersurface` relate to the IDs in `wsh_pol`
- `sample_support_code == watercourse_segment` relate to the IDs in `segm_3260`
- `sample_support_code == spring` relate to the IDs in `habspring_units_aquatic`

```{r sample-data-join}

stratum_units_grts_stream_gw_spsamples_spares <-
  # units per stratum:
  get("stratum_units_non_cell_n2khab", envir = env_extradata) %>%
  # joining GRTS address per unit. A few non-unique GRTS addresses exist, hence
  # 'many-to-one'. See further.
  inner_join(
    get("units_non_cell_n2khab_grts", envir = env_extradata),
    join_by(sample_support_code, unit_id),
    relationship = "many-to-one",
    unmatched = "error"
  ) %>%
  filter(
    # other 'non-cell' types exist so these must be dropped:
    sample_support_code %in% c(
      "watercourse_segment"
    )
  ) %>%
  rename(grts_address_final = grts_address) %>%
  # join with samples ('sample_status' defines whether location is 'in the
  # sample' or is a 'spare unit' (spare units = a bunch of 'next' GRTS addresses
  # in the available GRTS series for a stratum))
  inner_join(
    get(
      "scheme_moco_ps_stratum_sppost_spsamples_spares_sf",
      envir = env_extradata
    ) %>%
      st_drop_geometry() %>% # geom will be used below
      # only use the samples of groundwater schemes
      filter(str_detect(scheme, "^GW")) %>%
      rename(grts_address_drawn = grts_address) %>%
      # collapse module combos and schemes; hereby select the 'prior'
      # sample_status ("in_sample") across module combos and schemes:
      summarize(
        sample_status = sample_status %>% droplevels() %>% levels() %>%  first(),
        .by = c(
          stratum,
          grts_address_drawn,
          grts_address_final
        )
      ) %>%
      mutate(sample_status = factor(sample_status)),
    join_by(stratum, grts_address_final),
    # A few non-unique GRTS addresses exist, hence 'many-to-one'. We will apply
    # a quick-fix below to meet the requirement of 'one unit sampled per GRTS
    # address', but at least the selection will need further alignment with the
    # (likewise) MHQ solution (to be continued).
    relationship = "many-to-one",
    unmatched = "drop"
  ) %>%
  arrange(sample_support_code, stratum, grts_address_drawn, unit_id) %>%
  # for now, de-duplicate units with the same GRTS address by selecting the 1st
  slice(1, .by = c(stratum, sample_support_code, grts_address_final)) %>%
  select(-grts_address_drawn)


# grts address and stratum of all units which are in the target category
# (i.e. "watersurface", "watercourse_segment", "non-terrestrial spring")
kableprint(stratum_units_grts_stream_gw_spsamples_spares)

```


::: {.callout-caution}
REMINDER:
we de-duplicated units with the same GRTS address by selecting the 1st.
:::


# Positioning Locations on Streams

We have other types of water bodies.

```{r streams-and-springs}
stratum_units_grts_stream_gw_spsamples_spares %>%
  count(sample_support_code) %>%
  # sf::st_drop_geometry() %>%
  knitr::kable()
```

## stream test data

```{r stream-testing}
#| eval: true
# stratum_units_grts_stream_gw_spsamples_spares %>% 


stream_test_data <- 
  segm_3260 %>% 
    filter(
      stringr::str_detect(unit_id, "^9574_"),
      unit_id > "9574_218778"
    ) %>%
  right_join(
    stratum_units_grts_stream_gw_spsamples_spares,
    by = join_by(unit_id),
    relationship = "one-to-many",
    unmatched = "drop"
  ) %>% 
  filter(sample_support_code == "watercourse_segment") %>%
  arrange(unit_id)

location_code <- "9574_218821"
test_location <- stream_test_data %>%
  filter(unit_id == location_code)

mapview(stream_test_data)
```


```{r test-stream-plot-dhmv}

xy <- as.data.frame(
    sf::st_coordinates(stream_test_data)
  ) %>%
  rename_with(tolower)

margin <- 256 # m
flow_cellsize <- 32 # m
bbox <- sf::st_bbox(
   c(xmin = min(xy["x"]) - margin,
     xmax = max(xy["x"]) + margin,
     ymin = min(xy["y"]) - margin,
     ymax = max(xy["y"]) + margin
     ),
   crs = sf::st_crs(31370)
)
test_raster <- inbospatial::get_coverage_wcs(
  wcs = "dhmv",
  bbox = bbox,
  layername = "DHMVII_DTM_1m",
  version = "2.0.1",
  wcs_crs = "EPSG:31370",
  resolution = 1
)

# plot map
plot(test_raster, col = gray.colors(256)
     # ylab = sprintf("cluster %i (%s)", cluster_idx, regions)
     )
points(xy[["x"]], xy[["y"]], pch = 21, col = "black")
points(xy[["x"]], xy[["y"]], pch = 16, col = "yellow")
# title(sprintf("cluster %i", cluster_idx))


```

```{r stream-dhmv}

test_buffer <- test_location %>%
  sf::st_buffer(margin) 
sub_raster <- terra::crop(test_raster, sf::st_bbox(test_buffer))

flowdir <- calculate_flow_direction(
    test_location,
    flow_range = 96, flow_cellsize = 16,
    save_plot_filepath = here::here("figures", sprintf("%s.png", location_code)))

x <- sf::st_coordinates(test_location)[1,"X"][[1]]
y <- sf::st_coordinates(test_location)[1,"Y"][[1]]
plot(sub_raster, col = gray.colors(256))
points(x, y, pch = 16, col = "yellow")
arrows(
  x, y,
  x + 100*flowdir[1], y + 100*flowdir[2],
  col = "darkgray",
  length = 0.1
)

```

In this special case, flow direction might be useful for the stream data point;
However, it is not clear whether/how this will generalizes. 



## ARCHIVE: stream data preview

- lines or points, and where to get them - that is the question!

```{r lines-or-points}
#| eval: false

stream_testpoints <- read_watercourse_100mseg(element = "points") %>% 
  filter(vhag_code == 9574)
stream_testlines <- read_watercourse_100mseg(element = "lines") %>% 
  filter(vhag_code == 9574)

mapview(stream_testpoints, col.regions = "brown") +
    mapview(stream_testlines, col.regions = "steelblue")

```

Indeed, `read_watercourse_100mseg(element = "lines")` seems to be more accurate.


## stream flow maths (I): points

Streams flow from source to sea, 
and the 100m segments are a severe simplification.

Back to the raw data:

```{r stream-raw-data}
# mapview(habstream)
stream_points <- read_watercourse_100mseg(element = "points")
stream_lines <- read_watercourse_100mseg(element = "lines") 

test_stream_points <- stream_points %>%
  filter(vhag_code == 9574)
test_stream_lines <- stream_lines %>%
  filter(vhag_code == 9574)

mapview(test_stream_points, col.regions = "brown") +
    mapview(test_stream_lines, col.regions = "steelblue")

```

Rank: goes in "upstream" direction (water source: highest rank)

- <https://github.com/inbo/n2khab/blob/main/R/read_watercourses.R>
- <https://github.com/inbo/n2khab-preprocessing/blob/main/src/generate_watercourse_100mseg/10_generate_watercourse_100mseg.Rmd>


Maths refresher:

- <https://www.cs.toronto.edu/~mangas/teaching/320/slides/CSC320L04.pdf>
- <https://math.libretexts.org/@go/page/589>
- possibly Taylor series
- possibly arc-length-parametrization


We require:

- flow direction
- tangent
- normal
- curve forward/backward 
  - (projection onto normal)
  - "How much of the normal we must add to the tangent to approximate the tangent at t+dt".



```{r stream-curve-retrieval}
## for testing:
# vhag <- 9574
# segment_rank <- 218821

# extract a single stream from the 100m watercourse segments
get_pointstream_curve <- function(vhag, segment_rank) {

  # stream_points <- read_watercourse_100mseg(element = "points")


  # filter the points of interest
  target_stream_points <- stream_points %>%
    filter(vhag_code == as.numeric(vhag))

  # join them as a curve
  stream_curve <- as.data.frame(
    cbind(target_stream_points$rank, sf::st_coordinates(target_stream_points))
  )
  names(stream_curve) <- c("rank", "x", "y")

  # sort by "rank", i.e. point number
  stream_curve$rank <- stream_curve$rank - segment_rank
  stream_curve <- stream_curve %>% arrange(rank)

  return(stream_curve)
}

# test plot
test_curve <- get_pointstream_curve(vhag = 9574, segment_rank = 218821)
plot_pointstream_curve(test_curve)

```



```{r stream-tangents}

second_derivative <- get_pointstream_tangent(
  test_curve,
  normed = FALSE,
  append = FALSE,
  second = TRUE
)

kableprint(second_derivative)

```


```{r stream-normal}
kableprint(
  get_pointstream_normal(
    test_curve,
    normed = FALSE,
    append = FALSE
  )
)


```


```{r stream-curvature}

# get curvature or curvature direction for a line segment
# optionally smoothed
# direction is coded as curvature sign (-1: left turn, +1: right turn) but with 0: NA
get_curvature_direction <- function(stream_curve, direction = TRUE, smooth_range = NA) {

  # for the dot product
  stopifnot("geometry" = require("geometry"))

  # certainly calculate tangents
  stream_curve <- get_pointstream_normal(
    stream_curve,
    normed = TRUE,
    append = TRUE
  )

  # numeric difference vector
  dx <- diff(stream_curve$x)
  dy <- diff(stream_curve$y)

  # normalize differentials
  l <- Euclid(dx, dy)
  dx <- dx / l
  dy <- dy / l

  # there are zero-length segments
  dx[is.na(dx)] <- 0
  dy[is.na(dy)] <- 0

  # tangents and normals
  tx <- stream_curve$tx[seq_along(dx)]
  ty <- stream_curve$ty[seq_along(dy)]
  nx <- stream_curve$nx[seq_along(dx)]
  ny <- stream_curve$ny[seq_along(dy)]

  # connection vector between tangent and difference vector
  ux <- dx - tx
  uy <- dy - ty

  # scalar of the connection vector onto the normal
  curvatures <- c(sapply(
    seq_along(l),
    FUN = function(t) dotproduct(c(ux[t], uy[t]), c(nx[t], ny[t]))
  ), NA)
  curvatures[is.na(curvatures)] <- 0

  # optional: smoothing by Gaussian-weighted average
  if (!is.na(smooth_range)) {
    unsmoothed_curvatures <- curvatures
    # curvatures <- smoother::smth.gaussian(curvatures, alpha = smooth_range)
    curvatures <- smoother::smth(curvatures, method = "sma", window = smooth_range)

    # keep unsmoothed values for smoothing-na's
    curvatures[is.na(curvatures)] <- unsmoothed_curvatures[is.na(curvatures)]
    
  }
  
  # either return the direction...
  if (direction) {
    # (-1: left turn, 0: NA, +1: right turn)
    dirn <- (2*as.numeric(curvatures < 0)) - 1
    dirn[is.na(dirn)] <- 0
    return(dirn)
  }

  # ... or the curvature
  return(curvatures)
    
}

get_curvature_direction(
  test_curve,
  direction = TRUE
)

```


```{r stream-all-curve-measures}

get_all_curve_measures <- function(
    stream_curve,
    normed = TRUE,
    smooth_range = NA
    ) {

  # numeric difference
  stream_curve$dx <- c(diff(stream_curve$x), NA)
  stream_curve$dy <- c(diff(stream_curve$y), NA)

  # there are zero-length segments
  stream_curve$dx[is.na(stream_curve$dx)] <- 0
  stream_curve$dy[is.na(stream_curve$dy)] <- 0

  # tangent
  stream_curve <- get_pointstream_tangent(
    stream_curve,
    normed = normed,
    append = TRUE,
    second = FALSE
  )
  
  # normal
  stream_curve <- get_pointstream_normal(
    stream_curve,
    normed = normed,
    append = TRUE
  )

  # curvature and curvature direction
  stream_curve$curv <- get_curvature_direction(stream_curve, direction = FALSE, smooth_range = NA)
  stream_curve$dirn <- get_curvature_direction(stream_curve, direction = TRUE, smooth_range = NA)
  stream_curve$curv_smth <- get_curvature_direction(stream_curve, direction = FALSE, smooth_range = smooth_range)
  stream_curve$dirn_smth <- get_curvature_direction(stream_curve, direction = TRUE, smooth_range = smooth_range)

  # head(stream_curve)
  return(stream_curve)

}


test_curve <- get_all_curve_measures(
  test_curve,
  normed = TRUE,
  smooth_range = 5
)

knitr::kable(head(test_curve))

# tangent_norm <- function(sc) sqrt((sc$tx**2) + (sc$ty**2))
# print(tangent_norm(stream_tangent))


```



```{r plot-stream-direction-flow}

plot_pointstream_flowdirection <- function(
    stream_curve,
    scale = 64
  ) {

  x <- stream_curve$x
  y <- stream_curve$y
  tx <- stream_curve$tx * scale
  ty <- stream_curve$ty * scale
  tx2 <- stream_curve$tx2 * scale
  ty2 <- stream_curve$ty2 * scale
  nx <- stream_curve$nx * scale
  ny <- stream_curve$ny * scale
  curv <- stream_curve$curv
  curv_smth <- stream_curve$curv_smth
  dirn <- stream_curve$dirn
  dirn_smth <- stream_curve$dirn_smth
  nx <- nx * dirn_smth
  ny <- ny * dirn_smth
  nz <- !as.logical(as.integer(nx == 0) * as.integer(ny == 0))
  # col <- as.integer(dirn)+1
  color <- as.integer(dirn_smth[nz])+3
  
  
  plot(x, y)
  graphics::arrows(x, y, x+tx, y+ty, col = "darkgray", length = 0.1)
  # graphics::arrows(x, y, x+nx, y+ny, col = "lightblue", length = 0.1)
  # graphics::arrows(x-tx2, y-ty2, x+tx2, y+ty2, col = "lightblue", length = 0.1)
  graphics::arrows(
    x[nz], y[nz],
    x[nz] + nx[nz], y[nz] + ny[nz],
    col = color, length = 0.1
  )
}

plot_pointstream_flowdirection(test_curve)

```

Summary: we calculated

- the tangent (i.e. flow direction)
- the curvature (optionally smoothed)
- the direction (i.e. side, optionally smoothed)


:::{.callout-warning}
**The above was a calculation for points at 100m intervals.**
We need a more fine-grained stream sampling.
:::


## stream flow maths (II): lines

### conceptual

The `lines` stream data source has a finer resolution.
For reasons, I need to point out the ambiguity of the term **line**:

- in [geometry](https://en.wikipedia.org/wiki/Line_(geometry)): "a straight line, usually abbreviated line, is an infinitely long object with no width, depth, or curvature". Actually, we want [line segments](https://en.wikipedia.org/wiki/Line_segment).
- In [ggplot](https://ggplot2.tidyverse.org/reference/geom_path.html), "`geom_line()` connects [observations] in order of the variable on the x axis", ...
- ... whereas [`graphics::lines()`](https://www.rdocumentation.org/packages/graphics/versions/3.6.2/topics/lines) intuitively connects them in order of appearance: try `plot(c(0, 2, 1, 3), c(0, 1, 2, 3))` â® `lines(c(0, 2, 1, 3), c(0, 1, 2, 3))` (series of line segments).
- Finally, `read_watercourse_100mseg(element = "lines")` gives multiple line segments per row, which in fact is terminologically closest to school intuition.


Here I will adapt the point functions from above for stream lines.

### resampling

```{r test-resampling}
# stream_lines <- read_watercourse_100mseg(element = "lines")
  
stopifnot("pspline" = require("pspline"))

# filter the points of interest
target_stream_points <- stream_lines %>%
  filter(vhag_code == as.numeric(9574))

resample_m = 1
test <- target_stream_points[1, ]
original <- sf::st_coordinates(test)
resampled <- sf::st_coordinates(
  sf::st_line_sample(test, density = 1/resample_m)
)
x <- original[,1]
x0 <- x[1]
x <- x - x0
y <- original[,2]
y0 <- x[1]
y <- y - y0

adx <- abs(diff(x))
ady <- abs(diff(y))
dt <- sqrt(adx^2 + ady^2)
t <- c(0, cumsum(dt))
t <- t / max(t)
s <- seq(0, max(t), length.out = as.integer(round(max(cumsum(dt))))+1)

spline_x <- predict(sm.spline(t, x), s, 0)
spline_y <- predict(sm.spline(t, y), s, 0)
plot(s, spline_x, type = "l")
points(t, x, type = "o", col = "red")

spline_x <- spline_x + x0
spline_y <- spline_y + y0
  
par(pty = "s")
plot(x+x0, y+y0, type = "o", col = "black", asp = 1)
lines(spline_x, spline_y, type = "o", col = "blue")
lines(resampled, type = "o", col = "red")

```


We'll manually resample with splines (blue curve).
(As implemented in auxiliary R files.)


### retrieve lines


```{r linestream-curve}
# vhag <- 9574

# extract a single stream from the 100m watercourse segments
get_linestream_curve <- function(vhag, segment_rank = 0, resample_m = NA) {

  # stream_lines <- read_watercourse_100mseg(element = "lines")
  # message(vhag)
  # message(segment_rank)
    
  # filter the points of interest
  target_stream_points <- stream_lines %>%
    filter(vhag_code == as.numeric(vhag))

  # resample the streams
  if (!is.na(resample_m)) {
    target_stream_points <- dplyr::bind_rows(lapply(
      seq_len(nrow(target_stream_points)),
      FUN = function(i) {resample_linestream(
        target_stream_points[i,],
        resample_m = 1
        )}
    ))
  }

  # there are duplicates:
  # the last point of one segment matches the first point of the consecutive segment
  rank <- target_stream_points$rank
  coords <- data.frame(sf::st_coordinates(target_stream_points))
  coords$exclude <- FALSE
  # tail(head(coords, 32), 16)
  for (i in seq_len(nrow(coords)-1)) {
    this <- coords[i,]
    conseq <- coords[i+1,]
    coords[i, "exclude"] <- (this$X == conseq$X) &&
      (this$Y == conseq$Y) &&
      ((this$L1+1) == conseq$L1)
  }
  coords <- coords[!coords$exclude, c("X", "Y", "L1")]

  coords$sequence <- seq_len(nrow(coords))

  # join them as a curve
  linestream_curve <- as.data.frame(
      cbind(rank, seq_along(rank))
    ) %>%
    setNames(c("rank", "L1")) %>% 
    left_join(coords, join_by(L1))
  names(linestream_curve) <- c("rank", "lseq", "x", "y", "sequence")

  # sort by "rank", i.e. point number
  linestream_curve$rank <- linestream_curve$rank - segment_rank
  linestream_curve <- linestream_curve %>% arrange(rank, sequence)

  ref_rank <- linestream_curve %>%
    filter(rank == 0) %>%
    slice(1) %>%
    pull(sequence)
  if (length(ref_rank) > 0) {
    linestream_curve$sequence <- linestream_curve$sequence - ref_rank 
  }

  return(linestream_curve)
}

```


### Plotting Issues

```{r get-linecurve-testing}
# test plot
test_curve <- get_linestream_curve(vhag = 9574, segment_rank = 218821, resample_m = 1) %>%
    filter(rank > 20)

# WRONG!
test_curve %>%
  ggplot(aes(x = x, y = y)) +
    geom_line() +
    geom_point(aes(color = rank)) +
    coord_fixed(ratio = 1)

head(test_curve)
```


```{r get-linecurve-plotting}

# WORKS!
plot(test_curve$x, test_curve$y, asp = 1) +
  lines(test_curve$x, test_curve$y)

# CORRECTED:
test_curve %>%
  ggplot(aes(x = x, y = y)) +
    geom_path() +
    geom_point(aes(color = rank)) +
    coord_fixed(ratio = 1)

```

Order of points is ~~horribly wrong~~ totally correct.

:::{.callout-warning}
The problem was in ggplot (use `geom_path()` instead of `geom_line()`).

:::

### ARCHIVE: correct line point order

For the archives: my desperate and futile attempts to get the correct line point order on gg-plotting.


```{r test-pointorder-correction}
#| eval: false

test_curve <- get_linestream_curve(vhag = 9574, segment_rank = 218821) %>%
    filter(rank > 20, rank < 26)
head(test_curve, 16)

corrected_curve <- correct_curvepoint_order(test_curve) %>%
  arrange(streampoint_order)

# cbind(test_curve$lseq)

test_curve %>%
  ggplot(aes(x, y)) +
    geom_point() +
    geom_line(color = "orange") +
    geom_path(aes(corrected_curve$x, corrected_curve$y), color = "darkgreen") +
    coord_fixed(ratio = 1)


```

The good news is that my solution mathes the VHAG default in the test case.


### linestream calculation testing

```{r test-single-segment}
# head(test_curve)

# linestream_curve <- test_curve
test_curve <- get_linestream_curve(
    vhag = 9574,
    segment_rank = 218821,
    resample_m = 10
  ) %>% 
  filter(rank > 20)

if (FALSE) plot(test_curve$x, test_curve$y, asp = 1, type = "o", cex = 0.5)

# tangent
test_curve <- get_linestream_tangent(
  test_curve,
  normed = TRUE,
  append = TRUE
)

if (FALSE) {
  plot(test_curve$x, test_curve$y, asp = 1, type = "l", cex = 0.5)
  arrows(
    test_curve$x,
    test_curve$y,
    test_curve$x+test_curve$tx,
    test_curve$y+test_curve$ty,
    col = "darkgray",
    length = 0.1
  )
  # looks a bit like ivy roots
}


test_curve <- get_linestream_normal(
  test_curve,
  normed = TRUE,
  append = TRUE
)


if (FALSE) {
  plot(test_curve$x, test_curve$y, asp = 1, type = "l", cex = 0.5)
  arrows(
    test_curve$x,
    test_curve$y,
    test_curve$x+test_curve$nx,
    test_curve$y+test_curve$ny,
    col = "darkgray",
    length = 0.05
  )
}


test_curve$curv <- get_linestream_curvature_direction(test_curve, direction = FALSE, smooth_range = 5)
test_curve$dirn <- get_linestream_curvature_direction(test_curve, direction = TRUE, smooth_range = 5)

head(test_curve, 24)
plot_linestream_flowdirection(test_curve)

```


### linestream batch processing

```{r linestream-all-curve-measures}

test_curve <- get_linestream_curve(
  vhag = 9574,
  segment_rank = 218821,
  resample_m = 1
)

curve <- get_all_linestream_measures(
  test_curve,
  normed = TRUE,
  smooth_range = 2*pi
)

segment <- curve %>%
  filter(rank %in% c(-1,0)) %>% 
  filter(sequence > -20, sequence < 20) #%>%
  # select(-rank) %>% 
  # mutate(unit_id = unit_id)
knitr::kable(head(segment))

unit_point <- segment %>%
  filter(sequence == 0)

plot_linestream_flowdirection(segment) +
  points(unit_point$x, unit_point$y, type = "o", cex = 5)

```



```{r stream-data-assembly}
# vhag <- 9574
# segment_rank <- 218821
# unit_id <- "9574_218821"
#
# unit_id <- "47203_84627"
# unit_id <- "33011_111886" # less than 5 obs
# unit_id <- "47203_84627"


get_linestream_curve_properties <- function(unit_id, smooth_range = 5, resample_m = NA) {

  # message(unit_id)

  vhag <- stringr::str_split(unit_id, "_")[[1]][1]
  segment_rank <- as.numeric(stringr::str_split(unit_id, "_")[[1]][2])

  # extract the curve  
  # curve <- get_pointstream_curve(vhag = vhag, segment_rank = segment_rank)
  linestream_curve <- get_linestream_curve(
      vhag = vhag,
      segment_rank = segment_rank,
      resample_m = resample_m
    ) %>%
    filter(rank >= -3, rank <= 2)
  # print(linestream_curve)

  linestream_curve <- get_all_linestream_measures(
    linestream_curve,
    normed = TRUE,
    smooth_range = smooth_range
  )

  segment <- linestream_curve %>%
    filter(sequence == 0) %>%
    select(-rank) %>% 
    mutate(unit_id = unit_id)

  return(segment)
    
}

```


```{r stream-batch}
#| eval: true

stream_list <- stratum_units_grts_stream_gw_spsamples_spares %>%
  filter(sample_support_code == "watercourse_segment") %>%
  pull(unit_id)

# # debugging
# for (uid in stream_list) {
#   message(uid)
#   get_stream_curve_properties(uid)
# }

# # more debugging
# for (uid in stream_list){
#   # print(uid) # unit_id <- uid
#   get_linestream_curve_properties(uid, smooth_range = 1)
# }

# get_linestream_curve_properties("9512_238546")

stream_data <- bind_rows(lapply(
  stream_list,
  FUN = function(uid) get_linestream_curve_properties(uid, 5, 10)
))
kableprint(stream_data)


# get_linestream_curve_properties("8501_224807")
# get_linestream_curve_properties("8576_98821")
# head(get_linestream_curve(8501, segment_rank = 224807))
# head(get_linestream_curve(8576, segment_rank = 98821))
# head(get_linestream_curve(vhag = 9574, segment_rank = 218821))
# 
```



Strategy to continue (TODO):

- [X] Per sample point: go into `direction * normal`.
- [X] Mark target area aligned towards upstream.
- [X] Consider also incorporating slope; at least check consistency.


## stream determine target area

With the info aggregated by `get_stream_curve_properties`, we can decide on an alternative placement area.

```{r test-target-vectors}

for (uid in seq(781, 852, 5)) {
  unit_id <- sprintf("9574_218%03.0f", uid)
  save_plot_filepath <- here::here("figures", "direction_vectors", sprintf("%s.png", unit_id))

  # get stream info
  point_info <- get_linestream_curve_properties(unit_id, smooth_range = 5, resample_m = 10)

  # reference vectors
  segment_point <- point_info[c("x", "y")]

  # normal, to the right in the direction of flow
  normal_unit_vector <- normalize_vector(point_info[c("nx", "ny")])

  # tangent and difference vectors
  diff_unit_vector <- normalize_vector(point_info[c("dx", "dy")])
  tangent_unit_vector <- normalize_vector(point_info[c("tx", "ty")])

    
  # compare curvature and elevation-slope flow
  curvature <- point_info[["curv_smth"]]
  if(is.na(curvature)) curvature <- point_info[["curv"]]
 

  # check the strenght of the slope in the area
  flow_vector <- calculate_flow_direction(
    sf::st_as_sf(segment_point, coords = c("x", "y"), crs = 31370),
    flow_range = 96,
    flow_cellsize = 16,
    save_plot_filepath = here::here("figures", sprintf("%s.png", unit_id))
  )

  # check whether flow is in direction of the normal, or not
  flow_direction_scalar <- dotproduct(flow_vector, normal_unit_vector)

  flow_sign <- sign(flow_direction_scalar)
  flow_direction_magnitude <- abs(flow_direction_scalar)
  # flow_magnitude <- sqrt(sum(flow_vector^2))

  # curvature in normal direction -> go opposite direction
  curv_sign <- sign(curvature) 
  curv_magnitude <- abs(curvature)

  # normally, we go in direction of flow.
  total_sign <- -flow_sign
  curv_weight <- 4
  if (flow_direction_magnitude < curv_weight*curv_magnitude) {
    total_sign <- -curv_sign
  }

  # print(unit_id)
  # print(vectorize(tangent_unit_vector))
  # print(vectorize(normal_unit_vector))
  # print(vectorize(flow_vector))
  # print(curvature)

  png(save_plot_filepath,
    width = 120,
    height = 120,
    units = "mm",
    res = 300
  )

  par(pty = "s")
  plot(x = c(0), y = c(0), type = "o", asp = 1)
  plot_arrow_from_center(tangent_unit_vector, col = "darkgray", length = 0.1)
  plot_arrow_from_center(curv_weight*curvature * normal_unit_vector, col = "orange", length = 0.1)
  plot_arrow_from_center(flow_vector, col = "darkblue", length = 0.1)
  plot_arrow_from_center(total_sign * normal_unit_vector, col = "green", length = 0.1)

  dev.off()

}

```


```{r stream-target-area}
get_linestream_target_area <- function(unit_id, offset_m = 2, side_m = 24) {

  # unit_id <- "9574_218821"
  # unit_id <- "9574_218796"
  # unit_id <- "9574_218786" # straight downhill
  # unit_id <- sprintf("9574_218%03.0f", idx)

  # get stream info
  point_info <- get_linestream_curve_properties(unit_id, smooth_range = 5, resample_m = 10)

  # reference vectors
  segment_point <- point_info[c("x", "y")]

  # normal, to the right in the direction of flow
  normal_unit_vector <- normalize_vector(point_info[c("nx", "ny")])

  # tangent and difference vectors
  diff_unit_vector <- normalize_vector(point_info[c("dx", "dy")])
  tangent_unit_vector <- normalize_vector(point_info[c("tx", "ty")])

    
  # compare curvature and elevation-slope flow
  curvature <- point_info[["curv_smth"]]
  if(is.na(curvature)) curvature <- point_info[["curv"]]
 

  # check the strenght of the slope in the area
  flow_vector <- calculate_flow_direction(
    sf::st_as_sf(segment_point, coords = c("x", "y"), crs = 31370),
    flow_range = 96,
    flow_cellsize = 16,
    save_plot_filepath = here::here("figures", sprintf("%s.png", unit_id))
  )

  # check whether flow is in direction of the normal, or not
  flow_direction_scalar <- dotproduct(flow_vector, normal_unit_vector)

  flow_sign <- sign(flow_direction_scalar)
  flow_direction_magnitude <- abs(flow_direction_scalar)
  # flow_magnitude <- sqrt(sum(flow_vector^2))

  # curvature in normal direction -> go opposite direction
  curv_sign <- sign(curvature) 
  curv_magnitude <- abs(curvature)

  # normally, we go in direction of flow.
  total_sign <- -flow_sign
  curv_weight <- 4
  if (flow_direction_magnitude < curv_weight*curv_magnitude) {
    total_sign <- -curv_sign
  }

  # go around the square
  direction_vector <- tangent_unit_vector
  tpoints <- segment_point + total_sign * offset_m * normal_unit_vector
  tpoints <- bind_rows(tpoints, tpoints[1, ] - side_m * direction_vector)
  tpoints <- bind_rows(tpoints, tpoints[2, ] + total_sign * side_m * normal_unit_vector)
  tpoints <- bind_rows(tpoints, tpoints[3, ] + side_m * direction_vector)
  tpoints <- bind_rows(tpoints, tpoints[4, ] - total_sign * side_m * normal_unit_vector) # back to start

  target <- tpoints %>% sf::st_as_sf(coords = c("x", "y"), crs = 31370)

  target <- st_combine(target) %>% st_cast("POLYGON", warn = FALSE)
  return(sf::st_sf(data.frame(unit_id = unit_id, geom=target)))
} # /get_linestream_target_area


```


```{r stream-test-curvature-vs-flow}

# TODO try unit_id <- "9574_218856"
# TODO crashing unit_id <- "9574_218829", 837, ...
sample_unit_id <- "9574_218821"
test_targets <- get_linestream_target_area(sample_unit_id, offset_m = 2, side_m = 24)

curvs <- NA
flows <- NA
for (i in seq(771, 852, 5)) {
  unit_id <- sprintf("9574_218%03.0f", i)
  # message(unit_id)
  test_targets <- bind_rows(
    test_targets,
    get_linestream_target_area(unit_id, offset_m = 2, side_m = 24)
    )

  # flow and curvature
  scale <- 64
  point_info <- get_linestream_curve_properties(unit_id, smooth_range = 5, resample_m = 10)
  segment_point <- point_info[c("x", "y")]

  # normal, in the direction of curvature
  curvature <- point_info[["curv_smth"]]
  if(is.na(curvature)) curvature <- point_info[["curv"]]
  normal_curvature <- 8*scale * curvature * point_info[c("nx", "ny")]
  if (any(is.na(curvs))) {
    curvs <- create_sf_vector(segment_point, normal_curvature, unit_id)
  } else {
    curvs <- bind_rows(curvs, create_sf_vector(segment_point, normal_curvature, unit_id))
  }

  # check the strenght of the slope in the area
  flow_vector <- scale * calculate_flow_direction(
    sf::st_as_sf(segment_point, coords = c("x", "y"), crs = 31370),
    flow_range = 96,
    flow_cellsize = 16,
    save_plot_filepath = here::here("figures", sprintf("%s.png", unit_id))
  )

  if (any(is.na(flows))) {
    flows <- create_sf_vector(segment_point, flow_vector, unit_id)
  } else {
    flows <- bind_rows(flows, create_sf_vector(segment_point, flow_vector, unit_id))
  }
  
}

test_curve <- sf::st_as_sf(
  get_linestream_curve(vhag = 9574, segment_rank = 218821, resample_m = 25),
  coords = c("x", "y"),
  crs = 31370
  ) %>%
  filter(rank >= -52, rank < 36) %>% 
  mutate(selected = ((rank - 770) %% 5) == 0)

m1 <- mapview(test_curve, zcol = "selected")
test_targets$label <- "placement target area"
m2 <- mapview(test_targets, col.regions = "red", zcol = "label")

flows$label <- "flow direction"
m3 <- mapview(flows, color = "darkblue", zcol = "label")
curvs$label <- "curvature direction"
m4 <- mapview(curvs, color = "orange", zcol = "label")
m1+m2+m3+m4

```


## Summary: Streams

- Curvature is calculated with linestring points (i.e. more accurate).
- Target is placed depending on (i) curvature and (ii) elevation/slope.
- Usually, those seem consistent.
- Elevation has to overrule curvature; then, the target direction is taken as the mean of curvature and flow.
- Target area is aligned upstream from segment point.

